% Quelle der Übersetzung: Schneefl0cke https://www.fanfiktion.de/s/60044849000ccc541aef297e/102/
\chapter{Tests}

\section{4. Juni 1992}

% \lettrine{D}{aphne} Greengrass was in the Slytherin common room, writing a letter to her Lady Mother (who was surprisingly intransigent about power-sharing, despite not even \emph{being} in Hogwarts to exercise control) when she saw Draco Malfoy stagger in through the portrait door carrying what must have been a dozen books, Vincent and Gregory behind him each carrying a dozen more. The Auror who’d accompanied Malfoy stuck his head in briefly, then withdrew to who-knew-where.
\lettrine{D}{aphne} Greengrass befand sich im Slytherin-Gemeinschaftsraum und schrieb einen Brief an ihre Herrin Mutter (die erstaunlich unnachgiebig war, was die Teilung der Macht anging, obwohl sie nicht einmal in Hogwarts war, um die Kontrolle auszuüben), als sie Draco Malfoy durch die Porträttür taumeln sah, der wohl ein Dutzend Bücher trug, Vincent und Gregory hinter ihm, jeder mit einem weiteren Dutzend. Der Auror, der Malfoy begleitet hatte, steckte kurz den Kopf herein und zog sich dann nach wer-weiß-wohin zurück.

% Draco looked around, then seemed to be struck by a bright idea as he staggered toward her, Vincent and Gregory following after.
Draco sah sich um, dann schien er eine glänzende Idee zu haben, denn er taumelte auf sie zu, Vincent und Gregory folgten ihm.

% “Can you help me read these?” said Draco, sounding slightly out of breath as he approached.
„Kannst du mir helfen, die zu lesen?“, sagte Draco und klang leicht außer Atem, als er sich näherte.

% “What.” Lessons were over, only the exams were left now, and since when did \emph{Malfoys} ask \emph{Greengrasses} for help with their homework?
„Was?“ Der Unterricht war vorbei, jetzt standen nur noch die Prüfungen an, und seit wann baten \emph{Malfoys} \emph{Greengrasses} um Hilfe bei ihren Hausaufgaben?

% “These,” Draco Malfoy said importantly, “are all the library books Miss~Granger borrowed between April 1st and April 16th. I thought I’d go through them in case there are any Clues there, only then I thought, maybe \emph{you} should help because you knew Miss~Granger better.”
„Das“, sagte Draco Malfoy wichtig, „sind alle Bibliotheksbücher, die Miss~Granger zwischen dem 1. und 16. April ausgeliehen hat. Ich dachte, ich schaue sie durch, falls es dort irgendwelche Hinweise gibt, nur dachte ich dann, vielleicht solltest du helfen, weil du Miss~Granger besser kennst.“

% Daphne stared at the books. “The General read all that in \emph{two weeks?}” A twinge of pain went through her heart, but she suppressed it.
Daphne starrte auf die Bücher.
„Der General hat das alles in zwei Wochen gelesen?“ Ein schmerzhafter Stich durchfuhr ihr Herz, aber sie unterdrückte ihn.

% “Well, I don’t know if Miss~Granger finished them all,” Draco said. He held up a cautioning finger. “In fact, we don’t know if she read any of them, or if she really borrowed them, I mean, all we’ve \emph{observed} is that the library ledger says she checked them out—”
„Nun, ich weiß nicht, ob Miss~Granger sie alle gelesen hat“, sagte Draco. Er hielt einen mahnenden Finger hoch. „Tatsächlich wissen wir nicht, ob sie eines davon gelesen hat, oder ob sie es wirklich ausgeliehen hat, ich meine, alles, was wir beobachtet haben, ist, dass im Bibliotheksbuch steht, dass sie es ausgeliehen hat—“

% Daphne suppressed a groan. Malfoy had been talking like this for weeks. There were some people who clearly were not meant to be involved with mysterious murders because it did \emph{strange things to their minds}. “Mr~Malfoy, I couldn’t read all these if I spent my whole summer doing nothing else.”
Daphne unterdrückte ein Stöhnen. Malfoy redete schon seit Wochen so. Es gab einige Leute, die eindeutig nicht dazu bestimmt waren, mit mysteriösen Morden zu tun zu haben, denn es machte seltsame Dinge mit ihrem Verstand.
„Mr~Malfoy, ich könnte das alles nicht lesen, wenn ich den ganzen Sommer nichts anderes machen würde.“

% “Then just skim through them, please?” Draco said. “Especially if there’s, you know, mysterious words scribbled in her handwriting, or a bookmark left inside, or—”
„Dann überfliege sie bitte einfach? Vor allem, wenn da, du weißt schon, geheimnisvolle Worte in ihrer Handschrift gekritzelt sind, oder ein Lesezeichen drin steckt, oder—“

% “I’ve seen those plays too, Mr~Malfoy.” Daphne rolled her eyes. “Don’t we have \emph{Aurors} now for—”
„Ich habe diese Stücke auch schon gesehen, Mr~Malfoy.“ Daphne rollte mit den Augen. „Haben wir jetzt nicht \emph{Auroren} für—“

% “\emph{We’re doomed!}” shrieked Millicent Bulstrode, as she burst up from the lower chambers into the Slytherin common room.
„\emph{Wir sind dem Untergang geweiht!}“, kreischte Millicent Bulstrode, als sie aus den unteren Räumen in den Slytherin-Gemeinschaftsraum stürmte.

% People paused to look at her.
Die Leute hielten inne und sahen sie an.

% “\emph{It’s Professor Quirrell!}”
„\emph{Es ist Professor Quirrell!}“

% A sudden air of attentiveness, as of long-standing disputes about to be settled. “Well, finally,” someone said, as Millicent tried to catch her breath. “He’s only got, what, ten days left to go bad?”
Eine plötzliche Aufmerksamkeit, als ob ein langjähriger Streit geschlichtet werden sollte.
„Na, endlich“, sagte jemand, während Millicent versuchte, zu Atem zu kommen. „Er hatte ja nur noch, was, zehn Tage, um gefeuert zu werden?“

% “Eleven days,” said the seventh-year who was running the betting pool.
„Elf Tage“, sagte der Siebtklässler, der das Wettbüro leitete.

% “\emph{He’s suddenly got a little better and he’s going to summon the first-years for our Defence exam! By surprise! In fifty minutes!}”
„\emph{Es geht ihm plötzlich etwas besser, und er wird die Erstklässler für unsere Verteidigungsprüfungen holen! Überraschend! In fünfzig Minuten!}“

% “A Defence exam?” Pansy said blankly. “But Professor Quirrell doesn’t give exams.”
„Eine Verteidigungsprüfung?“ sagte Pansy verständnislos. „Aber Professor Quirrell hält keine Prüfungen.“

% “The \emph{Ministry} Defence exam!” shrieked Millicent.
„Die Verteidigungsprüfung des \emph{Ministeriums}!“, kreischte Millicent.

% “But Professor Quirrell doesn’t teach anything from the Ministry curriculum,” objected Pansy.
„Aber Professor Quirrell unterrichtet doch gar nichts aus dem Lehrplan des Ministeriums“, wandte Pansy ein.

% Daphne was already fleeing to her room, racing for the first-year Defence textbook that she hadn’t touched since September and screaming curses inside her mind.
Daphne war bereits in ihr Zimmer geflüchtet, rannte zu dem Verteidigungslehrbuch für das erste Jahr, das sie seit September nicht mehr angerührt hatte, und schrie in Gedanken Flüche.

\later

% One desk behind her, someone was crying, their soft sobs providing a background chant of despair for the classroom. Daphne looked back, expecting to see a Hufflepuff and hoping it wasn’t Hannah, and was surprised at first (though not on further reflection) to see it was a Ravenclaw.
Ein Pult hinter ihr weinte jemand, dessen leises Schluchzen einen Hintergrundgesang der Verzweiflung für das Klassenzimmer darstellte. Daphne schaute zurück, in der Erwartung, einen Hufflepuff zu sehen und in der Hoffnung, dass es nicht Hannah war, und war im ersten Moment überrascht (wenn auch nicht bei näherem Nachdenken) zu sehen, dass es eine Ravenclaw war.

% Before them were set the exam parchments, turned over, waiting for the bell.
Vor ihnen lagen die Prüfungspergamente, umgedreht, und sie warteten auf die Glocke.

% Fifty minutes hadn’t been nearly enough preparation time, but it was something, and Daphne was now feeling ashamed that she hadn’t thought to send messengers to warn the Hufflepuff, Ravenclaw, and Gryffindor Houses. They’d started giving House Points again just three days ago, at the beginning of June, but the Auxiliary Protective Special Committee still ought to promote House unity.
Fünfzig Minuten waren nicht annähernd genug Vorbereitungszeit gewesen, aber es war zumindest etwas, und Daphne schämte sich jetzt, dass sie nicht daran gedacht hatte, Boten zu schicken, um die Häuser Hufflepuff, Ravenclaw und Gryffindor zu warnen. Sie hatten erst vor drei Tagen, Anfang Juni, wieder angefangen, Hauspunkte zu vergeben, aber das Hilfsschutz-Sonderkomitee sollte immer noch die Einheit der Häuser fördern.

% Another Ravenclaw, sitting four desks to her left, also started to cry. That was Katherine Tung of Dragon Army, if she recalled correctly, whom she’d once seen take on three Sunshine Soldiers simultaneously without a flinch.
Eine andere Ravenclaw, die vier Tische links von ihr saß, begann ebenfalls zu weinen. Das war Katherine Tung von der Drachen-Armee, wenn sie sich richtig erinnerte, die sie einmal gesehen hatte, wie sie es mit drei Sonnenschein Soldaten gleichzeitig aufgenommen hatte, ohne mit der Wimper zu zucken.

% Daphne had calmed down after the first couple of minutes of frantic reading. It was just a test, not a \emph{murder} or anything; and if almost all the first-year students turned in mostly blank parchments then it stood to reason that nobody would be shamed. But Daphne could understand, if not exactly sympathize, that Ravenclaws and Hufflepuffs might not see it that way.
Daphne hatte sich nach den ersten paar Minuten des hektischen Lesens wieder beruhigt. Es war nur ein Test, kein \emph{Mord} oder so etwas; und wenn fast alle Erstklässler überwiegend leere Pergamente abgaben, dann lag es auf der Hand, dass sich niemand schämen würde. Aber Daphne konnte verstehen, wenn auch nicht gerade mitfühlen, dass Ravenclaws und Hufflepuffs das vielleicht nicht so sahen.

% “He’s evil,” another Ravenclaw witch said in a shaking voice. “One hundred percent pure Dark Wizard to the bone. The Dark Lord Grindelwald wouldn’t do this, not to children, he’s worse than You-Know-Who.”
„Er ist böse“, sagte eine andere Ravenclaw-Hexe mit zitternder Stimme. „Ein hundertprozentiger, reiner dunkler Zauberer bis auf die Knochen. Der Dunkle Lord Grindelwald würde so etwas nicht tun, nicht mit Kindern, er ist schlimmer als Du-weißt-schon-wer.“

% Daphne looked reflexively at where Professor Quirrell was sitting, slumped to one side but his eyes alert; and she thought she saw the Defence Professor smile for one tiny instant. No, that had to be her imagination, there was no way the Defence Professor could have heard that.
Daphne schaute reflexartig zu der Stelle, wo Professor Quirrell saß, zur Seite gesackt, aber mit wachen Augen; und sie glaubte, den Verteidigungsprofessor für einen winzigen Augenblick lächeln zu sehen. Nein, das musste sie sich einbilden, das konnte der Verteidigungsprofessor auf keinen Fall gehört haben.

% The bell rang.
\emph{Die Glocke läutete.}

% Daphne flipped the parchment over.
Daphne klappte das Pergament um.

% The top was stamped with the seals for the Ministry, the Hogwarts Board of Governors, and the Department of Magical Education, and runes to detect cheating. Below that was a line for her to write her name, and a list of exam rules with a picture of Lindsay Gagnon, the Director of the Department of Magical Education, shaking an admonishing finger at everyone.
Oben waren die Siegel des Ministeriums, des Obersten Rates von Hogwarts und der Abteilung für magische Erziehung sowie Runen zur Erkennung von Betrug aufgedruckt. Darunter befand sich eine Zeile, in die sie ihren Namen schreiben konnte, und eine Liste der Prüfungsregeln mit einem Bild von Lindsay Gagnon, der Direktorin der Abteilung für magische Erziehung, die jedem einen mahnenden Finger entgegenstreckte.

% Halfway down the page was the first exam question.
Auf der Hälfte der Seite stand die erste Prüfungsfrage. Sie lautete:
%
% It was, \emph{Why is it important for children to stay away from strange creatures?}
„\emph{Warum ist es für Kinder wichtig, sich von fremden Wesen fernzuhalten?}“

% There was a stunned pause.
Es gab eine verblüffte Pause.

% One student began laughing, she thought it was from the Gryffindor section of the class. Professor Quirrell made no motion to censor it, and the laughter spread.
Eine Schülerin begann zu lachen, sie dachte, es sei aus dem Gryffindor-Teil der Klasse. Professor Quirrell machte keine Anstalten, es zu unterbinden, und das Lachen breitete sich aus.

% Nobody spoke aloud, but the students looked around at each other, exchanging glances as the laughter died down, and then as if by some unspoken agreement they all looked at Professor Quirrell, who was smiling down at them benevolently.
Niemand sprach laut, aber die Schüler sahen sich um, tauschten Blicke aus, als das Lachen abebbte, und dann sahen sie alle wie durch eine unausgesprochene Übereinkunft zu Professor Quirrell, der wohlwollend auf sie herablächelte.

% Daphne bent over her exam, wearing a defiant evil smile that would have done proud to either Godric Gryffindor or Grindelwald; and she wrote down, \emph{Because my Stunning Hex, my Most Ancient Blade, and my Patronus Charm won’t work against everything.}
Daphne beugte sich über ihre Prüfung, mit einem trotzigen, bösen Lächeln, das sowohl Godric Gryffindor als auch Grindelwald zur Ehre gereicht hätte; und sie schrieb auf:
\emph{Weil mein Betäubungszauber, meine Uralte Klinge und mein Patronus nicht gegen alles wirken.}

\later

% Harry Potter turned over the last page of his Defence exam.
Harry Potter blätterte die letzte Seite seiner Verteidigungsprüfung um.

% Even Harry had needed to quash a small bit of nervousness, some tiny remnant of his childhood, upon reading the first real question (‘How can you make a Shrieking Eel be silent?’). Professor Quirrell’s lessons had spent roughly zero time on the surprising yet useless trivia that some idiot had imagined a ‘Defence class’ should look like. In principle, Harry could have used his Time-Turner to read through the first-year Defence book after being notified of the surprise exam; but that might have unfairly skewed the grading curve for others. After staring at the question for a couple of seconds, Harry had written down ‘Quieting Charm’, and included the casting directions in case the Ministry marker didn’t believe that Harry knew it.
Selbst Harry hatte ein kleines bisschen Nervosität unterdrücken müssen, ein winziges Überbleibsel seiner Kindheit, als er die erste richtige Frage las
(‚Wie kann man einen Schreienden Aal zum Schweigen bringen?‘)
Professor Quirrells Unterricht hatte so gut wie keine Zeit auf die überraschenden, aber nutzlosen Belanglosigkeiten verwendet, die sich irgendein Idiot bei einem ‚Verteidigungskurs‘ vorgestellt hatte. Im Prinzip hätte Harry seinen Zeitumkehrer benutzen können, um das Erstklässler-Verteidigungsbuch durchzulesen, nachdem er von der Überraschungsprüfung erfahren hatte; aber das hätte die Benotungskurve für die anderen unfairerweise verzerrt.
Nachdem er ein paar Sekunden lang auf die Frage gestarrt hatte, schrieb Harry „Stillezauber“ auf und fügte die Zauberanweisungen hinzu, falls der Prüfer des Ministeriums nicht glaubte, dass Harry ihn kannte.

% Once Harry had decided to just answer all the questions \emph{correctly}, the exam had gone by very quickly. The most realistic answer to more than half the questions was ‘Stunning Hex’, and many of the other questions had optimal solutions along the lines of ‘Turn around and walk in the opposite direction’ or ‘Throw away the cheese and buy a new pair of shoes.’
Nachdem Harry beschlossen hatte, einfach alle Fragen richtig zu beantworten, war die Prüfung sehr schnell vorbei gegangen. Die realistischste Antwort auf mehr als die Hälfte der Fragen war ‚Betäubungszauber‘, und viele der anderen Fragen hatten optimale Lösungen nach dem Muster ‚Dreh dich um und gehe in die entgegengesetzte Richtung‘ oder ‚Wirf den Käse weg und kaufe ein neues Paar Schuhe.‘

% The last question on the test was “What would you do if you suspected there might be a Bogeysnake underneath your bed?” The Ministry-approved answer, Harry could in fact recall from his read-through of the textbook at the start of the year, was \emph{Tell your parents.} The problem with this had occurred to Harry right away, which was why Harry had remembered it.
Die letzte Frage des Tests lautete:
„Was würdest du tun, wenn du vermutest, dass sich unter deinem Bett eine Kraytschlange befindet?“ Die vom Ministerium zugelassene Antwort, an die sich Harry noch aus der Lektüre des Lehrbuchs zu Beginn des Jahres erinnern konnte, lautete: \emph{Sag es deinen Eltern.}
Das Problem dabei war Harry sofort aufgefallen, deshalb hatte er sich auch daran erinnert.

% After some pondering, Harry wrote down:
Nach einigem Grübeln schrieb Harry auf:

% \emph{Dear Ministry marker: I’m afraid the real answer to that is a secret, but rest assured that a Bogeysnake would present no more trouble to me than a mountain troll, a Dementor, or You-Know-Who. Please inform your superiors that I find your standard answer prejudicial to Muggle-borns, and that I expect this failing will be corrected at once without any need for my direct intervention.}
\begin{writtenNote}
\letterAddress{Sehr geehrter Prüfer des Ministeriums,}
Ich fürchte, die wirkliche Antwort darauf ist ein Geheimnis, aber seien Sie versichert, dass eine Kraytschlange mir nicht mehr Ärger bereiten würde als ein Bergtroll, ein Dementor oder Du-weißt-schon-wer. Bitte teilen Sie Ihren Vorgesetzten mit, dass ich Ihre Standardantwort gegenüber Muggelgeborenen als unangemessen empfinde, und dass ich erwarte, dass dieser Fehler sofort korrigiert wird, ohne dass mein direktes Eingreifen erforderlich ist.
% \emph{Sincerely, the Boy-Who-Lived.}
\letterClosing[Mit freundlichen Grüßen,]{der Junge-der-überlebte}
\end{writtenNote}

% Harry signed the last parchment with a broad flourish, turned it over into his stack, put down his quill, and sat up.
Harry unterschrieb das letzte Pergament mit einem breiten Schwung, legte es in seinen Stapel, legte seinen Federkiel nieder und setzte sich auf.

% Looking around, Harry saw that Professor Quirrell seemed to be looking in his rough direction, though the Defence Professor’s head had nodded to one side. The other students were still writing. Some of them were silently crying, but they were still writing. \emph{Continuing to fight} was also a lesson Professor Quirrell had taught.
Als er sich umschaute, sah Harry, dass Professor Quirrell in seine ungefähre Richtung zu schauen schien, obwohl der Kopf des Verteidigungsprofessors zur Seite genickt hatte.
Die anderen Schüler waren immer noch am Schreiben. Einige von ihnen weinten leise, aber sie schrieben immer noch. \emph{Weiter zu kämpfen} war auch eine Lektion, die Professor Quirrell erteilt hatte.

% Interminably later, the official exam time was up. A seventh-year student went from desk to desk, collecting the exams in Professor Quirrell’s place.
Wenig später war die offizielle Prüfungszeit um. Ein Siebtklässler ging von Pult zu Pult und sammelte an Professor Quirrells Stelle die Klausuren ein.

% The last exam parchment was collected, and Professor Quirrell sat up straight.
Das letzte Prüfungspergament wurde eingesammelt, und Professor Quirrell setzte sich aufrecht hin.

% “My young students,” he said softly. The seventh-year student had her wand trained on the Defence Professor’s mouth, so that they all heard his voice seeming to come from right beside them. “I know…that probably seemed very fearsome to some of you…it is a different kind of fear from facing the enemy’s wand…you must conquer it separately. So I…shall tell you this now. It is the custom of Hogwarts…that grades are given in the second week of June. But for my case…they can make an exception, I think.” The Defence Professor smiled his familiar dry smile, tinged now as though by a suppressed grimace. “I know you are worried…that you were not prepared for this exam…that my lessons have not covered this material…and I quite forgot to mention…that it was approaching…though you should have known…it would come in time. But I have just now magically checked…the answers you have given on that…terribly, terribly important exam…though of course only the Ministry grade is official…and assigned your grades for the year taking the results into account…and magically written them down on these parchments,” Professor Quirrell tapped a stack of parchments on the side of his desk, “which will now be handed out…an incredible spell…is it not?”
„Meine jungen Schüler“, sagte er leise.
Die Schülerin im siebten Jahr hatte ihren Zauberstab auf den Mund des Verteidigungsprofessors gerichtet, so dass sie alle seine Stimme hörten, die von direkt neben ihnen zu kommen schien.
„Ich weiß… das erschien einigen von euch wahrscheinlich sehr furchteinflößend… es ist eine andere Art von Angst, als sich dem Zauberstab des Feindes zu stellen… ihr müsst sie selbst besiegen. Deshalb… werde ich euch jetzt Folgendes sagen. Es ist Brauch in Hogwarts, dass die Noten in der zweiten Juniwoche vergeben werden. Aber für meinen Fall… kann man eine Ausnahme machen, denke ich.“
Der Verteidigungsprofessor lächelte sein vertrautes trockenes Lächeln, das jetzt wie von einer unterdrückten Grimasse aus Schmerzen entsellt war.
„Ich weiß, dass Sie sich Sorgen machen… dass Sie nicht auf diese Prüfung vorbereitet waren… dass mein Unterricht diesen Stoff nicht behandelt hat… und ich habe ganz vergessen zu erwähnen… dass sie bevorsteht… obwohl Sie hätten wissen müssen… dass sie rechtzeitig kommen würde. Aber ich habe soeben auf magische Weise… die Antworten überprüft, die ihr bei dieser… furchtbar, furchtbar wichtigen Abschlussprüfung gegeben habt… obwohl natürlich nur die Note des Ministeriums offiziell ist… und eure Jahresnoten unter Berücksichtigung der Ergebnisse zugewiesen… und auf magische Weise eure vollen Noten auf diese Pergamente geschrieben wie ich Sie vergeben würde“,
Professor Quirrell tippte auf einen Stapel Pergamente auf der Seite seines Schreibtisches,
„die jetzt ausgeteilt werden… ein unglaublicher Zauber… nicht wahr?“

% A few students on the Ravenclaw side were looking indignant, but for the most part the students just looked relieved, and some Slytherins were chuckling. Harry would have laughed too, if not for the pain of watching Professor Quirrell gasp out the words.
Ein paar Schüler auf der Ravenclaw-Seite schauten entrüstet, aber zum größten Teil sahen die Schüler einfach nur erleichtert aus, und einige Slytherins kicherten. Harry hätte auch gelacht, wenn es nicht so weh getan hätte, Professor Quirrell dabei zuzusehen, wie er die Worte ausstieß.

% The seventh-year student standing beside Professor Quirrell pointed her wand and spoke an incantation in magical pseudo-Latin. The parchments rose up and started to drift through the air, separating in mid-flow to drift toward each student.
Die Schülerin im siebten Jahr, die neben Professor Quirrell stand, zeigte ihren Zauberstab und sprach eine Beschwörungsformel in magischem Pseudolatein.
Die Pergamente erhoben sich und begannen durch die Luft zu schweben, trennten sich in der Mitte der Halle, um zu jedem Schüler zu schweben.

% Harry waited until his parchment had arrived on his desk, and then unfolded it.
Harry wartete, bis sein Pergament auf seinem Schreibtisch angekommen war, und entfaltete es dann.

% The parchment said EE+, which stood for Exceeds Expectations. It was the second-highest grade letter, the highest being Outstanding.
Auf dem Pergament stand \emph{EE+}, was für \emph{Erwartungen übertroffen} stand. Es war der zweithöchste Notenbuchstabe, der höchste war \emph{Ohnegleichen}.

% In another world, a distant vanished world, a little boy named Harry would have shouted with indignation about receiving only the second-highest grade. This Harry sat quietly and thought. Professor Quirrell was making some point, and it wasn’t as though the exact grade letter mattered in any other way. Was Professor Quirrell saying that Harry had done relatively well, but not lived up to his full potential? Or was the grade meant to be read literally, that Harry had in fact exceeded the Defence Professor’s expectations?
In einer anderen Welt, einer fernen, verschwundenen Welt, hätte ein kleiner Junge namens Harry vor Empörung darüber geschrien, dass er nur die zweithöchste Note bekommen hatte. Dieser Harry saß still da und dachte nach. Professor Quirrell wollte damit irgendetwas sagen, und es war nicht so, dass der genaue Notenbuchstabe in irgendeiner Weise von Bedeutung war.
Wollte Professor Quirrell damit sagen, dass Harry zwar relativ gut abgeschnitten, aber nicht sein volles Potenzial ausgeschöpft hatte? Oder war die Note wörtlich zu lesen, dass Harry tatsächlich die Erwartungen des Verteidigungsprofessors übertroffen hatte?

% “All of you…pass,” Professor Quirrell said, as the students all looked at their final grades, as sighs of relief rose from desks and Lavender Brown raised her parchment in a clenched fist held high with triumph. “Every student in first-year Battle Magic has passed…except for one.”
„Ihr habt alle… bestanden“, sagte Professor Quirrell, als alle Schüler auf ihre Abschlussnoten blickten, während Seufzer der Erleichterung von den Tischen aufstiegen und Lavender Brown ihr Pergament in einer geballten, triumphierend hochgehaltenen Faust erhob.
„Jeder Schüler im ersten Jahr Kampfmagie hat bestanden…bis auf einen.“

% A number of students looked up in sudden terror.
Eine Reihe von Schülern blickte plötzlich erschrocken auf.

% Harry sat there silently. He had seen the point immediately, and even if it was a wrong point, he knew Professor Quirrell would never, ever be talked out of making it.
Harry saß schweigend da. Er hatte den Punkt sofort erkannt, und selbst wenn es ein falscher Punkt war, wusste er, dass Professor Quirrell sich niemals, niemals davon abbringen lassen würde, ihn zu machen.

% “All of you in this room…have received grades of at least Acceptable. Neville Longbottom…who took this test in the Longbottom home…received a grade of Outstanding. But the other student who is not here…has had a Dreadful grade entered on her record…for failing the only important test…that was given her this year. I would have marked her even lower…but that would have been in poor taste.”
„Jeder von euch in diesem Raum… hat mindestens die Note Annehmbar erhalten. Neville Longbottom… der diesen Test im Hause Longbottom abgelegt hat… hat ein Ohnegleichen erhalten. Aber die andere Schülerin, die nicht anwesend ist, hat die Note ‚Schrecklich‘ in ihre Akte eingetragen bekommen, weil sie bei der einzigen wichtigen Prüfung, die sie in diesem Jahr abgelegt hat, durchgefallen ist. Ich hätte sie noch schlechter benotet… aber das wäre geschmacklos gewesen.“

% The room was very quiet, though a number of students were staring angrily at the Professor.
Im Raum war es sehr still, obwohl einige Schüler den Professor wütend anstarrten.

% “You may think that a grade of Dreadful…is not fair. That Miss~Granger was faced with a test…for which her lessons…had not prepared her. That she was not told…that the exam was coming on that day.”
„Sie werden vielleicht denken, dass eine Note von Schrecklich… nicht fair ist. Dass Miss~Granger mit einem Test konfrontiert wurde… auf den ihr Unterricht… sie nicht vorbereitet hatte. Dass ihr nicht gesagt wurde… dass die Prüfung an diesem Tag stattfinden würde.“

% The Defence Professor drew in a shaking breath.
Der Verteidigungsprofessor holte zitternd Luft.

% “Such is realism,” said Professor Quirrell. “The only important test…may come at any time…be better prepared for it…than she was. As for the rest of you…those who have received Exceeds Expectations or above…have received my letters of recommendation…to certain organizations beyond Britain’s shores…where your training might be completed. They will contact you…when you are old enough…if you still appear worthy…and if you have not failed an important test. And remember…from this day…you must train yourselves…you cannot rely…on future Defence professors. Your first year of Battle Magic is over…you are dismissed.”
„So ist der Realismus“, sagte Professor Quirrell. „Die einzige wichtige Prüfung… kann jederzeit kommen… seid besser darauf vorbereitet… als sie es war. Was den Rest von euch angeht… diejenigen, die \emph{Erwartungen übertroffen} oder besser abgeschnitten haben… habe ich Empfehlungsschreiben geschrieben… an bestimmte Organisationen jenseits der britischen Küste… wo eure Ausbildung vervollständigt werden könnte. Man wird sich mit euch in Verbindung setzen, wenn ihr alt genug seid, wenn ihr noch würdig erscheint und wenn ihr nicht bei einem wichtigen Test durchgefallen seid. Und denkt daran…von diesem Tag an…müsst Ihr Euch selbst ausbilden…Ihr könnt Euch nicht…auf zukünftige Verteidigungsprofessoren verlassen. Euer erstes Jahr in Kampfmagie ist vorbei… ihr seid entlassen.“

% Professor Quirrell sat back with his eyes closed, seeming to ignore the excited babble that broke out around him.
Professor Quirrell lehnte sich mit geschlossenen Augen zurück und schien das aufgeregte Geplapper, das um ihn herum ausbrach, zu ignorieren.

% In time most of the students had departed, and one remained, staying a prescribed distance from the Defence Professor.
Mit der Zeit hatten sich die meisten Schüler entfernt, einer blieb zurück und hielt einen vorgeschriebenen Abstand zum Verteidigungsprofessor.

% The Defence Professor opened his eyes.
Der Verteidigungsprofessor öffnete seine Augen.

% Harry raised the parchment with its \emph{EE+}, still silent.
Harry hob das Pergament mit seinem \emph{EE+}, immer noch schweigend.

% The Defence Professor smiled, and it went all the way to those tired eyes.
Der Verteidigungsprofessor lächelte, und es ging bis in die müden Augen.

% “It is the same grade…that I received in my own first year.”
„Es ist die gleiche Note…die ich in meinem eigenen ersten Jahr erhalten habe.“

% “Th, th, th,” Harry couldn’t make the words \emph{thank you} come out, they were stuck in his suddenly closed throat, the Defence Professor tilting his head and giving him an inquiring stare, so Harry just bowed jerkily and then left the room.
„Da… dan…“,
Harry brachte das Wort „\emph{Danke}“ nicht heraus, sie blieben in seiner plötzlich zugeschnürten Kehle stecken.
Der Verteidigungsprofessor neigte den Kopf und warf ihm einen fragenden Blick zu, also verbeugte sich Harry nur ruckartig und verließ dann den Raum.

% Nine days yet remained.
Noch neun Tage.

%  LocalWords:  aphne Tung Bogeysnake EE
