% Quelle der Übersetzung: DieFuechsin https://www.fanfiktion.de/s/5c793dfe000a402030774dc7/18/
% \chapter{Self Centeredness}
\chapter{Self Selbstzentriertheit}

That’s not \emph{true}!

% \lettrine{P}{adma} Patil had finished her dinner a little late, getting on toward seven-thirty, and was now striding quickly out of the Great Hall on her way to the Ravenclaw dorm and the study rooms. Gossiping was fun and destroying Granger’s reputation was more fun, but it could distract from schoolwork. She’d put off a six-inch essay on \emph{lomillialor} wood due in next morning’s Herbology class, and she needed to finish it tonight.
\lettrine{P}{adma} Patil hatte ihr Abendessen etwas später beendet, so gegen 19.30~Uhr und verließ nun schnell die Große Halle auf dem Weg zum Ravenclaw-Schlafsaal und zu den Studienräumen. Klatsch und Tratsch machten Spaß und die Zerstörung von Grangers Ruf machte sogar noch mehr Spaß, aber es konnte von den Schulaufgaben ablenken. Sie hatte einen 15 cm langen Aufsatz über \emph{Lomillialor}-Holz, der am nächsten Morgen in der Kräuterkundeklasse fällig war, aufgeschoben, und sie musste ihn heute Abend fertig stellen.

% It was while she was passing through a long, twisting, narrow stone corridor that the whisper came, sounding like it was coming from right behind her.
Als sie durch einen langen, gewundenen, engen Steinkorridor ging, kam das Flüstern, das sich anhörte, als käme es von direkt hinter ihr.

„\emph{Padma Patil…}“

% She spun around quick as lightning, her wand already snatched up from a pocket of her robes and leaping into her hands, if Harry Potter thought he could sneak up on and scare \emph{her} that easily—
Sie drehte sich blitzschnell, ihr Zauberstab kam bereits aus einer Tasche ihres Gewandes und sprang ihr in die Hände, wenn Harry Potter dachte, er könne sich so leicht anschleichen und \emph{sie} erschrecken—

% There was no-one there.
Es war niemand da.

% Instantly Padma spun around and looked in the other direction, if it had been a Ventriloquism Charm—
Sofort drehte sich Padma um und schaute in die andere Richtung, ob es ein Bauchrednerzauber gewesen war—

% There was no-one there, either.
Es war auch dort niemand.

% The whispering sigh came again, soft and dangerous with a slight hissing undertone.
Der flüsternde Seufzer kam wieder, sanft und gefährlich mit einem leicht zischenden Unterton.

% “\emph{Padma Patil, Slytherin girl…}”
„\emph{Padma Patil, Slytherin-Mädchen…}“

% “Harry Potter, Slytherin boy,” she said out loud.
„Harry Potter, Slytherin-Junge,“ sagte sie laut.

% She’d fought Potter and his Chaos Legion a dozen times over, and she \emph{knew} that this was Harry Potter doing this somehow…
Sie hatte ein Dutzend Mal gegen Potter und seine Chaos-Legion gekämpft, und sie \emph{wusste}, dass es Harry Potter war, der dies irgendwie tat…

% …even though the Ventriloquism Charm was only line-of-sight, and in the winding corridor, she could easily see all the way to the nearest twist both forward and backward, and there was no-one there…
…obwohl der Zauber für Bauchreden nur in Sichtweite möglich war, und in dem gewundenen Korridor konnte sie leicht bis zur nächsten Wendung vorwärts und rückwärts sehen, und es war niemand da…

% …it didn’t matter. She knew her enemy.
…es war egal. Sie kannte ihren Feind.

% There was a whispering chuckle, now coming from beside her, and she spun around and pointed her wand at the whisper and shouted “\emph{Luminos!}”
Da war ein flüsterndes Glucksen, das jetzt von neben ihr kam, und sie drehte sich um und zeigte mit ihrem Zauberstab auf das Flüstern und rief „\emph{Luminos!}“

% The red bolt of light shot out and struck the wall, which lit with a crimson glow that soon faded.
Der rote Lichtblitz schoss heraus und traf die Wand, die mit einem purpurroten Schein leuchtete, der bald verblasste.

% She hadn’t really expected it to work. Harry Potter couldn’t \emph{possibly} be invisible, not really invisible, that was magic most \emph{grown-ups} couldn’t do, and she’d never believed nine-tenths of the stories about him.
Sie hatte nicht wirklich erwartet, dass es funktionieren würde. Harry Potter konnte \emph{unmöglich} unsichtbar sein, nicht wirklich unsichtbar, das war Magie, die die meisten \emph{Erwachsenen} nicht beherrschten, und sie hatte neun Zehntel der Geschichten über ihn nie geglaubt.

% The whispering voice laughed again, now on her other side.
Die flüsternde Stimme lachte wieder, jetzt auf ihrer anderen Seite.

% “Harry Potter stands on the precipice,” whispered the voice, now sounding very close to her ear, “he is wavering, but you, you are already falling, Slytherin girl…”
„Harry Potter steht am Abgrund,“ flüsterte die Stimme, die jetzt sehr nahe an ihrem Ohr klang, „er schwankt, aber du, du fällst schon, Slytherin-Mädchen…“

% “The hat never called out Slytherin for \emph{my} name, Potter!” She backed up against the wall, so she wouldn’t have to watch behind herself, and raised her wand in an attack stance.
„Der Hut hat nie Slytherin für \emph{meinen} Namen ausgerufen, Potter!“ Sie stellte sich mit dem Rücken zur Wand, um nicht hinter sich schauen zu müssen, und erhob ihren Zauberstab in Angriffshaltung.

% Again the soft laugh. “Harry Potter has been in the Ravenclaw common room for the last half-hour, helping Kevin Entwhistle and Michael Corner rehearse Potions recipes. But it matters not. I am here to deliver a warning to you, Padma Patil, and if you choose to ignore it, that is your own affair.”
Wieder das leise Lachen. „Harry Potter war die letzte halbe Stunde im Ravenclaw-Gemeinschaftsraum und half Kevin Entwhistle und Michael Corner, die Rezepte für Zaubertränke zu lernen. Aber das macht nichts. Ich bin hier, um dir eine Warnung zu überbringen, Padma Patil, und wenn Sie sich entscheiden, sie zu ignorieren, ist das Ihre eigene Sache.“

% “Fine,” she said coldly. “Go ahead and warn me, Potter, I’m not afraid of you.”
„Gut,“ sagte sie kalt. „Nur zu, warne mich, Potter, ich habe keine Angst vor dir.“

% “Slytherin was a great House, once,” said the whisper; it sounded sadder, now. “Slytherin was once a House you would have been proud to choose, Padma Patil. But something turned wrong, something turned sour; do you know what went awry in Slytherin House, Padma Patil?”
„Slytherin war einst ein großes Haus,“ sagte das Flüstern; jetzt klang es trauriger. „Slytherin war einst ein Haus, auf das Sie stolz gewesen wären, Padma Patil. Aber etwas ging schief, etwas wurde schlecht; wissen Sie, was in Slytherin House schief ging, Padma Patil?“

% “No, and I don’t care!”
„Nein, und es ist mir egal!“

% “But you should care,” said the whisper, now coming from just behind her head as it almost touched the wall. “For you are still that girl whom the Sorting Hat offered that choice. Do you think that just choosing Ravenclaw means that you are not Pansy Parkinson, and will not ever become Pansy Parkinson, no matter how you conduct yourself otherwise?”
„Aber es sollte Ihnen nicht egal sein,“ sagte das Flüstern, das sich jetzt anhörte, als käme es von direkt hinter ihrem Kopf, wo es fast an die Wand gedrückt war. „Denn Sie sind immer noch das Mädchen, dem der Sprechende Hut diese Wahl bot. Glauben Sie, dass die Wahl von Ravenclaw bedeutet, dass Sie nicht Pansy Parkinson sind und nie Pansy Parkinson werden, egal wie Sie sich sonst verhalten?“

% Despite everything, now, small chills of fear were spreading out from her spine and running over her skin. She’d heard \emph{those} stories about Harry Potter too, that he was a secret Legilimens. But she still stood straight, and she put all the bite she could into her voice when she said, “The Slytherins went Dark to get power, just like \emph{you} did, Potter. And \emph{I} won’t, not ever.”
Trotz allem rann nun ein kleiner Angstschauer ihren Rücken hinunter und machte ihr eine Gänsehaut. Sie hatte auch \emph{diese} Geschichten über Harry Potter gehört, dass er ein heimlicher Legilimentiker sei. Aber sie stand immer noch aufrecht, und sie steckte so viel Biss in ihre Stimme, wie sie konnte, als sie sagte: „Die Slytherins sind in die Dunkelheit gegangen, um Macht zu bekommen, genau wie \emph{du}, Potter. Und \emph{ich} werde es nicht tun, niemals.“

% “But you’ll spread vicious rumours about an innocent girl,” whispered the voice, “even though it will not help you attain any of your own ambitions, and without considering that she has powerful allies who might take offense. That is not the proud Slytherin of the old days, Padma Patil, that is not the pride of Salazar, that is Slytherin gone rotten, Padma Parkinson not Padma Malfoy…”
„Aber Sie werden bösartige Gerüchte über ein unschuldiges Mädchen verbreiten,“ flüsterte die Stimme, „obwohl es Ihnen nicht helfen wird, Ihre eigenen Ambitionen zu verwirklichen, und ohne zu bedenken, dass sie mächtige Verbündete hat, die sich vielleicht beleidigt fühlen. Das ist nicht die stolze Slytherin der alten Tage, Padma Patil, das ist nicht der Stolz von Salazar, das ist Slytherin, die verkommen ist, Padma Parkinson, nicht Padma Malfoy…“

% She was getting more spooked than she ever had been in her life, and the possibility was starting to occur to her that this might \emph{really} be a ghost. She hadn’t ever heard that ghosts could hide themselves like this, but maybe they just didn’t usually do it—not to mention that most ghosts weren’t this \emph{eerie}, they were just dead people after all— “Who \emph{are} you? The Bloody Baron?”
Sie bekam mehr Angst als je zuvor in ihrem Leben, und die Möglichkeit, dass dies \emph{wirklich} ein Geist sein könnte, kam ihr allmählich in den Sinn. Sie hatte noch nie gehört, dass sich Geister so verstecken können, aber vielleicht taten sie es normalerweise nicht—ganz zu schweigen davon, dass die meisten Geister nicht so \emph{unheimlich} waren, sie waren schließlich nur tote Menschen— „Wer \emph{sind} Sie? Der Blutige Baron?“

% “When Harry Potter was bullied and beaten,” the voice whispered, “he commanded all his allies to refrain from vengeance; do you remember that, Padma Patil? For Harry Potter is wavering, but not yet lost; he is struggling, he knows himself to be in peril. But Hermione Granger made no such request of her own allies. Harry Potter is angered with you now, Padma Patil, more angered than he would ever be on his own behalf…and \emph{he} has allies of his own.”
„Als Harry Potter schikaniert und geschlagen wurde,“ flüsterte die Stimme, „befahl er allen seinen Verbündeten, von Rache abzusehen; erinnern Sie sich daran, Padma Patil? Denn Harry Potter schwankt, ist aber noch nicht verloren; er kämpft, er weiß sich in Gefahr. Aber Hermine Granger hat ihre eigenen Verbündeten nicht darum gebeten. Harry Potter ist jetzt wütend auf Sie, Padma Patil, wütender, als er es in seinem eigenen Namen jemals sein würde… und \emph{er} hat seine eigenen Verbündeten.“

% A shudder went through her, she knew that it was visible and she hated herself for it.
Ein Schauder durchzog sie, sie wusste, dass es sichtbar war, und sie hasste sich dafür.

% “Oh, don’t be afraid,” breathed the voice. “I will not hurt you. For you see, Padma Patil, Hermione Granger truly is innocent. \emph{She} does not stand on the precipice, \emph{she} is not falling. She did not ask her allies to refrain from hurting you, because the thought did not even occur to her as a possibility. And Harry Potter knows very well that if he hurt you or caused you to be hurt, for Hermione Granger’s sake, then she would never speak to him again until the Sun burned low and the last star failed in the night sky.” The voice was very sad now. “She truly is a kindly girl, a person such as I could only wish to be…”
„Oh, hab keine Angst,“ atmete die Stimme. „Ich werde Ihnen nicht wehtun. Denn sehen Sie, Padma Patil, Hermine Granger ist wirklich unschuldig. \emph{Sie} steht nicht am Abgrund, \emph{sie} fällt nicht. Sie hat ihre Verbündeten nicht gebeten, es zu unterlassen, Sie zu verletzen, denn der Gedanke kam ihr nicht einmal als Möglichkeit in den Sinn. Und Harry Potter weiß sehr gut, dass, wenn er Sie verletzen würde oder dafür sorgte das Ihnen wehgetan würde, um Hermine Granger willen, sie nie wieder mit ihm sprechen würde, bis die Sonne erlischt und der letzte Stern vom Nachthimmel verschwindet. Die Stimme war jetzt sehr traurig.“ Sie ist wirklich ein nettes Mädchen, ein Mensch, wie ich es mir nur wünschen kann zu sein…"

% “Granger can’t cast the Patronus Charm!” said Padma. “If she was really as nice as she pretends to be—”
„Granger kann keinen Patronus zaubern!“, sagte Padma. „Wenn sie wirklich so nett wäre, wie sie vorgibt,—“

% “Can \emph{you} cast the Patronus Charm, Padma Patil? You dared not even attempt it, you feared what the result would be.”
„Können \emph{Sie} den Patronuszauber wirken, Padma Patil? Sie haben sich nicht einmal getraut, es zu versuchen, Sie haben sich vor dem Ergebnis gefürchtet.“

% “That’s not \emph{true!} I didn’t have time, that was all!”
„Das ist nicht \emph{wahr}! Ich hatte keine Zeit, das war alles!“

% The whisper continued. “But Hermione Granger did try, openly before her friends, and when her magic failed she was surprised and dismayed. For there are secrets to the Patronus Charm that few ever knew, and maybe none now know but I.” A soft, whispering chuckle. “Let it stand that it is no stain on her spirit that halts her light from coming forth. Hermione Granger cannot cast the Patronus Charm for the very same reason that Godric Gryffindor, who raised these halls, never could.”
Das Flüstern ging weiter. „Aber Hermine Granger versuchte es, offen vor ihren Freunden, und als ihre Magie versagte, war sie überrascht und bestürzt. Denn es gibt Geheimnisse des Patronuszaubers, die nur wenige je kannten, und vielleicht weiß jetzt außer mir niemand mehr davon.“ Ein leises, flüsterndes Glucksen. „Lassen Sie es einfach so stehen, dass es kein Makel ihres Geistes ist, der ihr Licht daran hindert, hervorzukommen. Hermine Granger kann den Patronuszauber aus demselben Grund nicht aussprechen, aus dem Godric Gryffindor, der diese Hallen errichtete, es nie konnte.“

% The corridor \emph{was} becoming colder, she was certain of it, as though someone were using the Chilling Charm.
Der Korridor \emph{wurde} kälter, dessen war sie sich sicher, als ob jemand den Kühlenden Zauber einsetzen würde.

% “And Harry Potter is not Hermione Granger’s only ally.” Now there was an undertone of dry amusement in that whisper, it reminded her suddenly and frighteningly of Professor Quirrell. “Filius Flitwick and Minerva McGonagall are quite fond of her, I do believe. Did it occur to you that if those two learned what you were doing to Hermione Granger, they might become less fond of you? They might not intervene openly, perhaps; but they might be a little slower to award you House Points, a little slower to steer opportunities your way—”
„Und Harry Potter ist nicht der einzige Verbündete von Hermine Granger.“ Nun gab es einen Unterton von trockener Belustigung in diesem Flüstern, es erinnerte sie plötzlich und erschreckend an Professor Quirrell. „Filius Flitwick und Minerva McGonagall haben sie, glaube ich, sehr gern. Ist es Ihnen in den Sinn gekommen, dass, wenn die beiden erfahren würden, was Sie Hermine Granger antun, sie Sie vielleicht weniger gern haben würden? Sie werden vielleicht nicht offen eingreifen, aber sie werden vielleicht etwas langsamer sein, um Ihnen Hauspunkte zu geben, und etwas langsamer darin Möglichkeiten in Ihre Richtung zu lenken—“

% “Potter \emph{sneaked} on me?”
„Potter hat mich \emph{angeschwärzt}?“

% A ghostly chuckle, a dry heh-heh-heh. “Do you think those two are stupid, deaf and blind?” In a sadder whisper, “Do you think Hermione Granger is not precious to them, that they will not see her hurting? As they might have been fond of you once, their bright young Padma Patil, but you are throwing it away…”
Ein geisterhaftes Glucksen, ein trockenes He-he-he-heh. „Glauben Sie, die beiden sind dumm, taub und blind?“ In einem traurigeren Flüstern: „Glauben Sie, dass Hermine Granger nicht wertvoll für sie ist, dass sie nicht sehen, wie sie verletzt wird? So wie sie Sie, ihre aufgeweckte junge Padma Patil, vielleicht einmal gemocht haben, aber Sie werfen das weg…“

% Padma’s throat was dry. She hadn’t thought of that, not at all.
Padmas Kehle war trocken. Daran hatte sie nicht gedacht, ganz und gar nicht.

% “I wonder how many people will end up caring for you, Padma Patil, on this path that you now tread. Is it worth that much, just to distance yourself further from your sister? To be the shadow to Parvati’s light? Your deepest fear has always been to fall into harmony with her, \emph{back} into harmony with her I should say; but is it worth hurting an innocent girl, just to make yourself that much more different? Must you be the \emph{evil} twin, Padma Patil, can you not find a different good to pursue?”
"Ich frage mich, wie viele Menschen sich auf diesem Weg, den Sie jetzt beschreiten, für Sie, Padma Patil, einsetzen werden. Ist es so viel wert, nur um sich weiter von Ihrer Schwester zu entfernen? Der Schatten von Parvatis Licht zu sein? Ihre tiefste Angst war immer, mit ihr in Harmonie zu fallen, \emph{zurück} in Harmonie mit ihr, sollte ich sagen; aber ist es das wert, ein unschuldiges Mädchen zu verletzen, nur um sich so viel anders zu machen? Müssen Sie der \emph{böse} Zwilling sein, Padma Patil, können Sie nicht ein anderes Gut finden, dem Sie nacheifern können?

% Her heart was hammering in her chest. She’d, she’d never talked about that with \emph{anyone—}
Ihr Herz hämmerte in ihrer Brust. Sie hatte, sie hatte nie mit \emph{irgendjemandem} darüber geredet—

% “I have always wondered at how students bully each other,” sighed the voice. “How children make life difficult for themselves, how they turn their schools into prisons even with their own hands. Why do human beings make their own lives so unpleasant? I can give you a part of the answer, Padma Patil. It is because people do not stop and think before causing pain, if they do not imagine that they themselves could also be hurt, that they might also suffer from their own misdeeds. But suffer you will, oh, yes, Padma Patil, suffer you will, if you stay on this road. You will suffer the same pain of loneliness, the same pain of others’ fear and distrust, that you now inflict on Hermione Granger. Only for you it will be deserved.”
„Ich habe mich immer gefragt, wie sich Schüler gegenseitig schikanieren,“ seufzte die Stimme. „Wie Kinder sich selbst das Leben schwer machen, wie sie ihre Schulen mit ihren eigenen Händen in Gefängnisse verwandeln. Warum machen sich Menschen ihr eigenes Leben so unangenehm? Ich kann Ihnen einen Teil der Antwort geben, Padma Patil. Es liegt daran, dass Menschen nicht innehalten und nachdenken, bevor sie Schmerzen verursachen, wenn sie sich nicht vorstellen, dass sie selbst auch verletzt werden könnten, dass sie auch unter ihren eigenen Missetaten leiden könnten. Aber leiden werden Sie, oh ja, Padma Patil, leiden werden Sie, wenn Sie auf diesem Weg bleiben. Sie werden den gleichen Schmerz der Einsamkeit erleiden, den gleichen Schmerz der Angst und des Misstrauens anderer, den Sie jetzt Hermine Granger zufügen. Nur für Sie wird er verdient sein.“

% Her wand was shaking in her hand.
Ihr Zauberstab zitterte in ihrer Hand.

% “You did not choose sides when you went to Ravenclaw, girl. You choose your side by the way you live your life, what you do to other people and what you do to yourself. Will you illuminate others’ lives, or darken them? That is the choice between Light and Dark, not any word the Sorting Hat cries out. And the hard part, Padma Patil, is not saying ‘Light’, the hard part is deciding which is which, and admitting it to yourself when you begin down the wrong road.”
„Du hast dich nicht für eine Seite entschieden, als du nach Ravenclaw gingst, Mädchen. Du wählst deine Seite durch die Art und Weise, wie du dein Leben lebst, was du anderen Menschen antust und was du dir selbst antust. Wirst du das Leben anderer erhellen oder verdunkeln? Das ist die Wahl zwischen Licht und Dunkelheit, nicht irgendein Wort, das der Sprechende Hut ausruft. Und das Schwierigste, Padma Patil, ist nicht, 'Licht' zu sagen, das Schwierigste ist, zu entscheiden, was was ist, und es sich einzugestehen, wenn man auf dem falschen Weg beginnt.“

% There was silence. It went on for a time, and Padma realized that she had been dismissed.
Es herrschte Stille. Sie dehnte sich eine Zeitlang aus und Padma wurde klar, dass sie entlassen worden war.

% Padma almost dropped her wand, when she tried to put it back into her pocket. She almost fell, when she took a step forward away from the wall, and turned to go—
Padma ließ ihren Zauberstab fast fallen, als sie versuchte, ihn wieder in ihre Tasche zu stecken. Sie fiel fast hin, als sie einen Schritt von der Wand weg machte und sich umdrehte, um zu gehen—

% “I have not always chosen rightly between Light and Dark,” the whisper said, now loud and harsh directly into her ear. “Do not take my wisdom as a final word, girl, do not fear to question it, for though I have tried I have sometimes failed, oh, yes, I have failed. But you are hurting a true innocent, and you will achieve none of your ambitions by doing so; it is not for any cunning plan. You are inflicting pain purely for the sake of the pleasure it brings you. I have not always chosen rightly between Light and Dark, but that I know is darkness, for certain. You are hurting an innocent girl, and escaping retribution only because she is too kindly to tolerate her allies moving against you. I cannot hurt you for that, so know only that I cannot respect it. You are unworthy of Slytherin; go and do your Herbology homework, Ravenclaw girl!”
„Ich habe nicht immer richtig zwischen Hell und Dunkel gewählt,“ sagte das Flüstern, nun laut und scharf direkt in ihr Ohr. „Nimm meine Weisheit nicht als letztes Wort, Mädchen, fürchte dich nicht, sie in Frage zu stellen, denn obwohl ich es versucht habe, bin ich manchmal gescheitert, oh ja, ich habe versagt. Aber Sie verletzen eine wahre Unschuldige, und Sie werden damit keine Ihrer Ambitionen erreichen, es ist nicht für irgendeinen listigen Plan. Sie fügen Schmerzen zu, nur um des Vergnügens willen, das sie Ihnen bringen. Ich habe mich nicht immer richtig zwischen Licht und Dunkelheit entschieden, aber ich weiß mit Sicherheit, dass das zur Dunkelheit führt. Du tust einem unschuldigen Mädchen weh und entgehst der Vergeltung nur deshalb, weil sie zu freundlich ist, um zu zuzulassen dass ihre Verbündeten gegen dich vorgehen. Ich kann dir daher nicht wehtun, also wisse nur, dass ich das nicht respektieren kann. Du bist Slytherins unwürdig; geh und mach deine Kräuterkundehausaufgaben, Ravenclaw-Mädchen!“

% The final whisper came out in a louder hiss that sounded almost like a snake, and Padma fled, she fled down the corridors as if Lethifolds were chasing her, she ran heedless of the rules about running in the corridors, even when she passed other students who looked at her in surprise, she did not stop, she ran all the way to the Ravenclaw dorms with her pulse pounding in her neck, the door asked her “Why does the Sun shine in the day and not at night?” and it took her three tries before she could make her answer coherent, and then the door came open and she saw—
Das letzte Flüstern kam in einem lauten Zischen heraus, das fast wie eine Schlange klang, und Padma floh, sie floh die Korridore hinunter, als ob Lethifolds sie verfolgten, sie rannte ohne Rücksicht auf die Regeln über Laufen in den Korridoren, selbst als sie an anderen Studenten vorbeikam, die sie überrascht ansahen, hielt sie nicht an, sie rannte den ganzen Weg zum Ravenclaw-Schlafsaal und ihr Blut pulsierte in ihrem Nacken, die Tür fragte sie: „Warum scheint die Sonne am Tag statt in der Nacht?“ Sie brauchte drei Versuche, um eine kohärente Antwort zu geben, dann öffnete sich die Tür und sie sah—

% —a few girls and boys, some young and some old, all staring at her, and in one corner at the pentagonal table, Harry Potter and Michael Corner and Kevin Entwhistle, looking up from their textbooks.
—ein paar Mädchen und Jungen, einige jung und einige alt, die sie alle anstarren, und in einer Ecke am fünfeckigen Tisch Harry Potter und Michael Corner und Kevin Entwhistle, die von ihren Schulbüchern aufblicken.

% “Sweet Merlin!” exclaimed Penelope Clearwater, rising from a couch. “What happened to you, Padma?”
„Bei Merlin!“, rief Penelope Clearwater, die sich von einer Couch erhob. „Was ist denn mit dir passiert, Padma?“

% “I,” she stuttered, “I, I heard—a ghost—”
„Ich,“ stotterte sie, „ich, ich hörte—einen Geist—“

% “It wasn’t the Bloody Baron, was it?” said Clearwater. She drew her wand and a moment later she was holding a cup, and then an \emph{Aguamenti} later the cup was filled with water. “Here, drink this, sit down—”
„Es war doch nicht der Blutige Baron, oder?“, sagte Clearwater. Sie zog ihren Zauberstab und einen Moment später hielt sie einen Becher, und einen \emph{Aguamenti}später war der Becher mit Wasser gefüllt. „Hier, trink das, setz dich hin—“

% Padma was already striding toward the pentagonal table. She looked at Harry Potter, who was looking at her with his own gaze, calm and grave and a little sad.
Padma schritt bereits auf den fünfeckigen Tisch zu. Sie schaute Harry Potter an, der sie mit seinem eigenen Blick, ruhig und ernst und ein wenig traurig, ansah.

% “\emph{You} did this!” Padma said. “How—you—how dare you!”
„\emph{Du} hast das getan!“ sagte Padma. „Wie—du—wie kannst du es wagen!“

% There was a sudden hush in the Ravenclaw dorm.
Im Wohnheim von Ravenclaw herrschte plötzlich Stille.

% Harry just looked at her.
Harry sah sie nur an.

% And said, “Is there anything I can help you with?”
Und sagte: „Kann ich dir irgendwie helfen?“

% “Don’t deny it,” Padma said, her voice shaking, “\emph{you} set that ghost on me, it \emph{said}—”
„Leugne es nicht,“ sagte Padma, ihre Stimme zitterte, „\emph{Du} hast den Geist auf mich gehetzt, er \emph{sagte}…“

% “I mean it,” Harry said. “Can I help you with anything? Get you some food, or go fetch a soda for you, or help you with your homework, or anything like that?”
„Ich meine es ernst,“ sagte Harry. „Kann ich dir bei irgendetwas helfen? Dir etwas zu essen besorgen, oder dir eine Limonade holen, oder dir bei den Hausaufgaben helfen, oder etwas in der Art?“

% Everyone was staring at the two of them.
Alle starrten die beiden an.

% “Why?” Padma said. She couldn’t think of anything else to say, she didn’t understand.
„Warum?“, fragte Padma. Es fiel ihr nichts anderes ein, sie verstand nichts.

% “Because some of us are standing on the precipice,” Harry said. “And the difference is what you do for other people. Will you let me help you with something, Padma, please?”
„Weil einige von uns am Abgrund stehen,“ sagte Harry. „Und der Unterschied ist, was man für andere Menschen tut. Lässt du mich dir bitte bei etwas helfen, Padma?“

% She stared at him, and knew, in that moment, that he’d had his own warning, same as her.
Sie starrte ihn an und wusste in diesem Moment, dass er seine eigene Warnung bekommen hatte, genau wie sie.

% “I…” she said. “I’ve got to write six inches on \emph{lomillialor}—”
„Ich…,“ sagte sie. „Ich muss 15 Zentimeter über \emph{Lomillialor}schreiben…“

% “Let me run up to my dorm and get my Herbology stuff,” Harry said. He rose from the pentagonal table, looked at Entwhistle and Corner. “Sorry, guys, I’ll see you later.”
„Lass mich in meinen Schlafsaal gehen und meine Kräuterkundesachen holen,“ sagte Harry. Er erhob sich vom fünfeckigen Tisch, schaute auf Entwhistle und Corner. „Tut mir leid, Leute, wir sehen uns später.“

% They didn’t say anything, just stared, along with everyone else in the dorm room, as Harry Potter walked over to the stairs.
Sie sagten nichts, starrten nur, wie alle anderen im Schlafsaal, als Harry Potter zur Treppe hinüberging.

% And just as he started up, he said, “And no-one’s to pester her with questions unless \emph{she} wants to talk about it, I hope everyone’s \emph{got that?}”
Und gerade als er sie betrat, sagte er: „Und niemand beöästigt sie mit Fragen, es sei denn, \emph{sie} will darüber reden, ich hoffe, das haben alle \emph{verstanden}?“

% “Got it,” said most of the first-years and some of the older students, a few of them sounding quite scared.
„Haben wir,“ sagten die meisten der Erstklässler und einige der älteren Schüler, einige von ihnen klangen ziemlich verängstigt.

\later

% And she talked about a lot of things with Harry Potter besides \emph{lomillialor} wood—even her fear of falling back into harmony with Parvati, which she’d never talked about with \emph{anyone} before, but then Harry’s ghostly ally already knew. And Harry had reached into his pouch and pulled out some \emph{odd} books, loaning them to her on condition of complete secrecy, saying that if she could comprehend those books it would change the pattern of her thinking enough that she’d never fall into harmony with Parvati again…
Und sie sprach mit Harry Potter über vieles andere als \emph{Lomillialor-Holz}—sogar über ihre Angst, mit Parvati wieder in Harmonie zu verfallen, über die sie noch nie mit \emph{jemandem} gesprochen hatte, aber Harrys geisterhafter Verbündete wusste ja schon Bescheid. Und Harry hatte in seinen Beutel gegriffen und einige \emph{seltsame} Bücher herausgenommen, die er ihr unter der Bedingung völliger Geheimhaltung geliehen hatte, und sagte, wenn sie diese Bücher verstehen würde, würde das ihre Denkweise so verändern, dass sie nie wieder mit Parvati in Einklang fallen würde…

% At nine o’clock, when Harry said he had to go, the essay was only half done.
Um neun Uhr, als Harry sagte, er müsse gehen, war der Aufsatz erst halb fertig.

% And when Harry paused, and looked at her on the way out, and said that \emph{he} thought she was worthy of Slytherin, it made her feel good for a whole minute before she realized what had just been said to her and who had said it.
Und als Harry eine Pause machte und sie auf dem Weg nach draußen ansah und sagte, dass \emph{er} dachte, sie sei Slytherin würdig, gab ihr das eine ganze Minute lang ein gutes Gefühl, bevor sie begriff, was ihr gerade gesagt worden war und wer es gesagt hatte.

\later

% When Padma got down to breakfast, that morning, she saw Mandy see her and whisper something to the girl sitting beside her at the Ravenclaw table.
Als Padma an diesem Morgen zum Frühstück kam, sah sie, dass Mandy sie ansah und dem Mädchen, das neben ihr am Ravenclaw-Tisch saß, etwas zuflüsterte.

% She saw that girl get up from the bench and walk toward her.
Sie sah, wie das Mädchen von der Bank aufstand und auf sie zuging.

% Last night Padma had been glad that girl slept in the other dorm; but now that she thought about it, this was worse, now she had to do it in front of \emph{everyone}.
Gestern Abend war Padma froh gewesen, dass das Mädchen im anderen Schlafsaal untergebracht war; aber jetzt, wo sie darüber nachdachte, war es noch schlimmer, jetzt musste sie es vor \emph{allen Leuten} tun.

% But even though Padma was sweating, she knew what she had to do.
Aber obwohl Padma schwitzte, wusste sie, was sie zu tun hatte.

% The girl came closer—
Das Mädchen kam näher—

% “I’m sorry.”
„Es tut mir leid.“

% “What?” said Padma. That was \emph{her} line.
„Was?“, sagte Padma. Das war \emph{ihr} Satz.

% “I’m sorry,” repeated Hermione Granger. Her voice was loud so that everyone could hear. “I…I didn’t ask Harry to do that, and I was angry with him when I found out, and I made him promise not to do it again to \emph{anyone}, and I’m not talking to him for a week…I’m really, \emph{really} sorry, Miss~Patil.”
„Es tut mir leid,“ wiederholte Hermine Granger. Ihre Stimme war laut, so dass jeder sie hören konnte. „Ich… ich habe Harry nicht darum gebeten, und ich war wütend auf ihn, als ich es herausfand, und ich ließ ihn versprechen, es \emph{niemandem} mehr anzutun, und ich werde eine Woche lang nicht mit ihm sprechen… Es tut mir wirklich, \emph{wirklich} leid, Miss~Patil.“

% Hermione Granger’s back was stiff, her face was stiff, you could see the sweat on her face.
Hermine Grangers Rücken war steif, ihr Gesicht war steif, man konnte den Schweiß auf ihrem Gesicht sehen.

% “Um,” said Padma. Her own thoughts were pretty much scrambled, now…
„Ähm,“ sagte Padma. Ihre eigenen Gedanken waren ziemlich durcheinander, jetzt…

% Padma’s gaze flicked to the Ravenclaw table, where one boy was watching them with tight eyes and his hands clenched in his lap.
Padmas Blick flitzte zum Ravenclaw-Tisch, wo ein Junge sie mit im Schoß geballten Händen gespannt ~beobachtete.

% \latersection{Earlier}

\latersection{Vorher}

% “I told you to be \emph{nicer!}” shrieked Hermione.
„Ich habe dir gesagt, du sollst \emph{netter} sein!“ schrie Hermine.

% Harry was starting to sweat. He’d never actually heard Hermione scream at him before, and it was quite loud in the empty classroom.
Harry begann zu schwitzen. Er hatte noch nie zuvor wirklich gehört, wie Hermine ihn anschrie, und es war ziemlich laut in dem leeren Klassenzimmer.

% “I—but—but I \emph{was} nice!” Harry protested. “I practically \emph{redeemed} her, Padma was going down the wrong path and I turned her off it! I probably changed her whole life to be happier! Besides, you should’ve heard the \emph{original} version of what Professor Quirrell suggested I do—” at which point Harry realized what he was saying and closed his mouth a second too late.
„Ich—aber—aber ich \emph{war} nett!“ Harry protestierte. „Ich habe sie praktisch \emph{erlöst}, Padma war auf dem falschen Weg, und ich habe sie davon abgehalten! Ich habe wahrscheinlich ihr ganzes Leben verändert, so dass sie glücklicher sein wird! Außerdem hättest du die \emph{Originalversion} dessen hören sollen, was Professor Quirrell mir vorschlug—“ an diesem Punkt erkannte Harry, was er sagte, und schloss seinen Mund eine Sekunde zu spät.

% Hermione clutched at her chestnut curls, a gesture Harry hadn’t seen from her before. “What’d \emph{he} say to do? \emph{Kill} her?”
Hermine klammerte sich an ihre Kastanienlocken, eine Geste, die Harry noch nie von ihr gesehen hatte. „Was hat \emph{er} gesagt, was du tun sollst? Sie \emph{umbringen}?“

% The Defence Professor had suggested that Harry identify all the key influential students inside and outside his year and try to gain control of the entire Hogwarts rumour mill, remarking that this was a generally useful and amusing challenge for any true Slytherin attending Hogwarts.
Der Verteidigungsprofessor hatte vorgeschlagen, dass Harry alle wichtigen einflussreichen Studenten innerhalb und außerhalb seines Jahrgangs identifizieren und versuchen sollte, die Kontrolle über die gesamte Hogwarts-Gerüchteküche zu erlangen. Er bemerkte, dass dies eine allgemein nützliche und amüsante Herausforderung für jeden echten Slytherin sei, der nach Hogwarts kommt.

% “Nothing like \emph{that,}” Harry said quickly, “he just said in a general way that I should get influence over the people spreading rumours, and \emph{I} decided that the \emph{nice} version of that would be to just inform Padma directly about the meaning of what she was doing, and the possible consequences of her actions, instead of trying to threaten her or anything like that—”
„Nichts \emph{dergleichen},“ sagte Harry schnell, „er sagte nur ganz allgemein, dass ich Einfluss auf die Leute bekommen sollte, die Gerüchte verbreiten, und \emph{ich} beschloss, dass die \emph{nette} Version davon darin bestünde, Padma einfach direkt über die Bedeutung dessen, was sie tat, und die möglichen Konsequenzen ihrer Handlungen zu informieren, anstatt zu versuchen, sie zu bedrohen oder etwas derartiges—“

% “\emph{You call that not threatening someone?}” Hermione’s hands were pulling at her hair now.
„\emph{Das nennst du jemanden nicht bedrohen?}“ Hermines Hände zogen jetzt an ihren Haaren.

% “Um…” Harry said. “I guess she might’ve felt a \emph{little} threatened, but Hermione, people will do whatever they think they can get away with, they don’t care about how much it hurts other people if it doesn’t hurt themselves, if Padma thinks there’s \emph{no} consequences to spreading lies about you then of \emph{course} she’ll just go on doing it—”
„Ähm…“ sagte Harry. „Ich schätze, sie hat sich vielleicht ein \emph{wenig} bedroht gefühlt, aber Hermine, die Leute werden alles tun, womit sie glauben durchkommen zu können, es ist ihnen egal, wie sehr es andere Menschen verletzt, wenn es ihnen selbst nicht weh tut, wenn Padma denkt, dass es \emph{keine} Konsequenzen hat, Lügen über dich zu verbreiten, dann wird sie es \emph{natürlich} einfach weiter tun—“

% “And you think there’s going to be no consequences to what \emph{you} did?”
„Und du glaubst, dass es keine Konsequenzen für das gibt, was du getan hast?“

% Harry got a sudden sick feeling to his stomach.
Harry bekam plötzlich ein mulmiges Gefühl im Magen.

% Hermione had the angriest look on her that he’d ever seen. “What do you think the other students think of you now, Harry? Of \emph{me?} If Harry doesn’t like the way you talk about Hermione, you’ll get ghosts set on you, is that what you want them to think?”
Hermine hatte den wütendsten Blick aufgesetzt, den er je gesehen hatte. „Was denkst du, was die anderen Schüler jetzt von dir denken, Harry? Von \emph{mir}? Wenn Harry nicht mag, wie du über Hermine sprichst, werden die Geister auf dich losgehen, willst du, dass sie das denken?“

% Harry opened his mouth and no words came out, he just…hadn’t thought about it that way, actually…
Harry öffnete den Mund und es kamen keine Worte heraus, er hatte nur… so hatte er eigentlich nicht darüber nachgedacht…

% Hermione reached down to grab her books from the table where she’d slammed them. “I’m not talking to you for a week, and I’ll \emph{tell} everyone I’m not talking to you for a week, and I’ll tell them \emph{why}, and \emph{maybe} that’ll undo some of what you just did. And after that week, I’ll—I’ll decide then what to do, I guess—”
Hermine griff nach unten, um ihre Bücher vom Tisch zu holen, wo sie sie zugeschlagen hatte. „Ich rede eine Woche lang nicht mit dir, und ich werde allen \emph{sagen}, dass ich eine Woche lang nicht mit dir rede, und ich werde ihnen sagen, \emph{warum}, und \emph{vielleicht} macht das einiges von dem rückgängig, was du gerade getan hast. Und nach dieser Woche werde ich—ich werde dann entscheiden, was zu tun ist, denke ich—“

% “\emph{Hermione!}” Harry’s own voice rose to a shriek of desperation. “\emph{I was trying to help!}”
„\emph{Hermine!}“ Harrys eigene Stimme erhob sich zu einem Schrei der Verzweiflung. „\emph{Ich habe versucht zu helfen!}“

% The girl turned back and looked at him as she opened the classroom door.
Das Mädchen drehte sich um und sah ihn an, als es die Tür zum Klassenzimmer öffnete.

% “Harry,” she said, and her voice trembled a little beneath the anger, “Professor Quirrell is sucking you into the darkness, he really is, I mean it, Harry.”
„Harry,“ sagte sie, und ihre Stimme zitterte ein wenig unter der Wut: „Professor Quirrell saugt dich in die Dunkelheit, das tut er wirklich, ich meine es ernst, Harry“.

% “This…wasn’t him, this wasn’t what he said to do, this was just \emph{me}—”
„Das… war er nicht, das war nicht das, was er mir geraten hat zu tun, das war nur \emph{ich}—“

% Hermione’s voice was almost a whisper now. “Someday you’re going to go out to lunch with him, and it will be your dark side that comes back, or maybe even you won’t come back at all.”
Hermines Stimme war nun fast ein Flüstern. „Eines Tages wirst du mit ihm essen gehen, und es wird deine dunkle Seite sein, die zurückkommt, oder vielleicht kommst du auch gar nicht mehr zurück“.

% “I promise you,” Harry said, “that I \emph{will} come back from lunch.”
„Ich verspreche dir,“ sagte Harry, „dass ich vom Mittagessen zurückkommen \emph{werde}.“

% He wasn’t even thinking as he said it.
Er dachte nicht einmal nach, als er es sagte.

% And Hermione just turned around and strode out and slammed the door behind her.
Und Hermine drehte sich einfach um, ging hinaus und knallte die Tür hinter sich zu.

% \emph{Way to invoke the laws of dramatic irony, moron,} observed Harry’s Internal Critic. \emph{Now you’re going to die this Saturday, your last words will be ‘I’m sorry, Hermione’, and she’ll always regret that the last thing she did was slam the door—}
\emph{Das} \emph{is} \emph{mal `ne Art, sich auf die Gesetze der dramatischen Ironie zu berufen, Idiot,} stellte Harrys Interner Kritiker fest. \emph{Jetzt wirst du an diesem Samstag sterben, deine letzten Worte werden sein: „Es tut mir leid, Hermine,“ und sie wird immer bedauern, dass das letzte was sie tat war die Tür zuzuschlagen—}

% \emph{Oh, shut up.}
\emph{Ach, halt die Klappe.}

\later

% When Padma sat down with Hermione for breakfast, and said in a voice loud enough for others to hear that the ghost had just told her things that were important for her to hear, and Harry Potter had been right to do it, there were some people who were less frightened afterwards, and some who were frightened more.
Als Padma sich zum Frühstück mit Hermine hinsetzte und mit einer Stimme sagte, die laut genug war, dass andere es hören konnten, dass der Geist ihr nur Dinge gesagt hatte, die für sie wichtig waren, und Harry Potter Recht gehabt hatte, es zu tun, gab es einige Leute, die danach weniger Angst hatten, und einige, die mehr Angst hatten.

% And afterwards people \emph{did} say fewer nasty things about Hermione, at least in the first year, at least in public where Harry Potter might hear about it.
Und danach \emph{sagten} die Leute weniger böse Dinge über Hermine, zumindest im ersten Jahr, zumindest in der Öffentlichkeit, wo Harry Potter davon hören könnte.

% When Professor Flitwick asked Harry if he was responsible for what had happened to Padma, and Harry said yes, Professor Flitwick told him that he was to serve two days’ detention. Even if it had only been a ghost and Padma hadn’t been hurt, still, that wasn’t acceptable behaviour for a Ravenclaw student. Harry nodded and said that he understood why the Professor had to do that, and wouldn’t protest; but considering that it \emph{did} seem to have turned Padma around, did Professor Flitwick really think, off the record, that he’d done the wrong thing? And Professor Flitwick paused, seeming to actually think about it, and then said to Harry, in a solemnly squeaky voice, that he needed to learn how to relate to other students the normal way.
Als Professor Flitwick Harry fragte, ob er für das, was Padma passiert war, verantwortlich sei, und Harry ja sagte, sagte Professor Flitwick ihm, dass er zwei Tage Nachsitzen müsse. Selbst wenn es nur ein Geist gewesen war und Padma nicht verletzt worden war, war das für einen Ravenclaw-Schüler dennoch kein akzeptables Verhalten gewesen. Harry nickte und sagte, dass er verstünde, warum der Professor das tun musste, und dass er nicht protestieren würde; aber wenn man bedachte, dass es Padma anscheinend zum Guten bekehrt \emph{hatte}, dachte Professor Flitwick dann wirklich, inoffiziell, dass er das Falsche getan hatte? Und Professor Flitwick hielt inne, schien tatsächlich darüber nachzudenken, und sagte dann mit feierlicher, quietschender Stimme zu Harry, dass er lernen müsse, wie er mit anderen Studenten auf normale Weise umzugehen habe.

% And Harry couldn’t help but think that this was advice that Professor Quirrell would never give him.
Und Harry konnte nicht anders, als zu denken, dass dies ein Rat war, den Professor Quirrell ihm niemals geben würde.

% Harry couldn’t help but think that if he’d done it Professor Quirrell’s way, the normal \emph{Slytherin} way, a mixture of positive and negative incentives to bring Padma and the other rumour-mongers under his explicit control, then Padma wouldn’t have talked about it, and Hermione would have never found out…
Harry konnte nicht umhin, zu denken, dass, wenn er es auf Professor Quirrells Art und Weise getan hätte, auf die normale Art und Weise \emph{Slytherins}, eine Mischung aus positiven und negativen Anreizen, um Padma und die anderen Gerüchtemacher unter seine ausdrückliche Kontrolle zu bringen, dann hätte Padma nicht darüber gesprochen und Hermine hätte es nie herausgefunden…

% …in which case Padma wouldn’t have been redeemed, she would have stayed on the wrong path, and she herself would have suffered from that eventually. It wasn’t as if Harry had \emph{lied} to Padma in any way, when he was Time-Turned and invisible and using the Ventriloquism Charm.
…in welchem Falle Padma nicht erlöst worden wäre, sie wäre auf dem falschen Weg geblieben, und sie selbst hätte letztendlich darunter gelitten. Es war nicht so, dass Harry Padma in irgendeiner Weise \emph{belogen} hatte, als er zeitumgekehrt und unsichtbar war und den Bauchrednerzauber benutzte.

% Harry still wasn’t sure whether he’d done the right thing, or \emph{a} right thing, and Hermione hadn’t relented on not talking to him—though she was talking a lot with Padma. It hurt more than Harry had expected, going back to studying by himself; like his brain had already started to forget its long-honed skill of being alone.
Harry war sich immer noch nicht sicher, ob er das Richtige getan hatte, oder \emph{eine} richtige Sache, und Hermine hatte nicht nachgegeben, nicht mit ihm zu sprechen—obwohl sie viel mit Padma sprach. Es tat mehr weh, als Harry erwartet hatte, wieder alleine zu lernen; als hätte sein Gehirn bereits begonnen, seine lang erprobte Fähigkeit des Alleinseins zu vergessen.

% The days until Saturday’s lunch with Professor Quirrell seemed to go by very, very slowly.
Die Tage bis zum Mittagessen mit Professor Quirrell am Samstag schienen sehr, sehr langsam zu vergehen.

%  LocalWords:  adma lomillialor
