% Quelle der Übersetzung: DieFuechsin https://www.fanfiktion.de/s/5c793dfe000a402030774dc7/38/
% \partchapter{Self Actualization}{V}
\partchapter{Selbstverwirklichung}{V}

% \lettrine{E}{ven} if you had been the Deputy Headmistress for three decades, and a Transfiguration Professor before that, it was rare that you saw Albus Dumbledore completely wrong-footed.
\lettrine{S}{elbst} nachdem man drei Jahrzehnte lang stellvertretende Schulleiterin und davor Professorin für Verwandlung gewesen war, war es selten Albus Dumbledore komplett unvorbereitet zu erwischen.

% “…Susan Bones, Lavender Brown, and Daphne Greengrass,” Minerva finished. “I should also note, Albus, that Miss~Granger’s account of your seemingly unsupportive attitude—I believe her phrase was ‘he said I should be happy to be just a sidekick’—has generated a good deal of \emph{interest} among the older girls. Several of whom came to me to ask if Miss~Granger’s accusations were true, since Miss~Granger had said that I was there.”
„…Susan Bones, Lavender Brown und Daphne Greengrass“, beendete Minerva ihre Aufzählung. „Ich sollte auch anmerken, Albus, dass Miss~Grangers Bericht über dein scheinbar nicht sehr hilfreiches Verhalten—ich glaube, ihre Formulierung war „\emph{er sagte, ich solle froh sein, nur eine Gehilfin zu sein}“—eine Menge \emph{Interesse} bei den älteren Mädchen geweckt hat. Mehrere von ihnen kamen zu mir, um zu fragen, ob Miss~Grangers Anschuldigungen stimmten, da sie gesagt hatte ich wäre dabei gewesen.“

% The old wizard leaned back in his huge chair, still gazing at her, his eyes looking rather abstracted beneath the half-moon glasses.
Der alte Zauberer lehnte sich in seinem riesigen Stuhl zurück und starrte sie immer noch an, wobei seine Augen unter der Halbmondbrille etwas abwesend wirkten.

% “It placed me in something of a dilemma, Albus,” said Professor McGonagall. Her face stayed quite neutral, she made sure of that. “I now know that you did not truly mean to discourage the girl. Quite the opposite, in fact. But you and Severus have often told me that to keep a secret I must give no sign that differs from the reaction of someone truly ignorant. Thus I had no choice but to confirm that Miss~Granger’s account was accurate, and feign the appropriate degree of worry, with a slight overtone of offense. After all, had I \emph{not} known you were deliberately manipulating Miss~Granger, I might have been rather put out.”
„Das hat mich etwas in die Bredouille gebracht, Albus“, sagte Professor McGonagall. Ihr Gesicht blieb ganz neutral, dafür sorgte sie. „Ich weiß jetzt, dass du nicht wirklich die Absicht hattest, das Mädchen zu entmutigen. Ganz im Gegenteil. Aber du und Severus habt mir oft gesagt, dass ich, um ein Geheimnis zu wahren, kein Zeichen geben darf, das sich von der Reaktion eines wirklich Unwissenden unterscheidet. So blieb mir nichts anderes übrig, als zu bestätigen, dass Miss~Grangers Schilderung korrekt war, und den angemessenen Grad von Besorgnis vorzutäuschen, mit einem leichten Unterton von Verärgerung. Hätte ich nämlich \emph{nicht} verstanden, dass du Miss~Granger absichtlich manipulierst, wäre ich vielleicht ziemlich empört gewesen.“

% “I…see,” the old wizard said slowly. His hands toyed absently with his silver beard, small quick gestures.
„Ich…verstehe“, sagte der alte Zauberer langsam. Seine Hände spielten abwesend mit seinem silbernen Bart, kleine schnelle Gesten.

% “Thankfully,” Professor McGonagall continued, “so far Professors Sinistra and Vector are the only two faculty members to don Miss~Granger’s buttons.”
„Zum Glück“, fuhr Professor McGonagall fort, „sind die Professoren Sinistra und Vector bisher die einzigen beiden Fakultätsmitglieder, die Miss~Grangers Anstecker tragen.“

% “Buttons?” repeated the old wizard.
„Anstecker?“, wiederholte der alte Zauberer.

% Minerva drew forth a small silver disc bearing the initials \SPHEW, laid it on Albus’s desk, and gave it a brief tap with her finger.
Minerva zog eine kleine silberne Scheibe mit der Abkürzung \SPHEW hervor, legte sie auf Albus‘ Schreibtisch und tippte sie kurz mit dem Finger an.

% And the voices of Hermione Granger, Padma Patil, Parvati Patil, Lavender Brown, Susan Bones, Hannah Abbott, Daphne Greengrass, and Tracey Davis cried out in unison, “\emph{We won’t settle for second best, it’s time to give a witch a quest!}”
Und die Stimmen von Hermine Granger, Padma Patil, Parvati Patil, Lavender Brown, Susan Bones, Hannah Abbott, Daphne Greengrass und Tracey Davis riefen unisono: „Wir bleiben nicht Zweitbeste! Es ist Zeit! Gebt Hexen eine Queste.“

% “Miss~Granger is selling them for two Sickles, and tells me that she has so far sold fifty of them. I believe that Nymphadora Tonks, in seventh-year Hufflepuff, is enchanting them for her. To conclude my report,” Professor McGonagall said briskly, “our eight newly minted heroines have asked permission to conduct a protest outside the entrance to your office.”
„Miss~Granger verkauft sie für zwei Sickel und erzählt mir, dass sie bisher fünfzig davon verkauft hat. Ich glaube, dass Nymphadora Tonks aus dem siebten Schuljahr in Hufflepuff sie für sie verzaubert. Um meinen Bericht abzuschließen“, sagte Professor McGonagall zügig, „unsere acht frisch gebackenen Heldinnen haben um Erlaubnis gebeten, vor dem Eingang Ihres Büros eine Protestaktion durchzuführen.“

% “I hope,” Albus said, frowning, “you explained to them that—”
„Ich hoffe“, sagte Albus und runzelte die Stirn, „Du hast ihnen erklärt, dass—“

% “I explained to them that Wednesday at 7\pm would be fine,” said Minerva. She took back the button from the Headmaster’s desk, favoured Albus with a honeyed smile, and turned to the door.
„Ich habe ihnen erklärt, dass Mittwoch um 19~Uhr in Ordnung wäre“, sagte Minerva. Sie nahm den Knopf vom Schreibtisch des Schulleiters zurück, schenkte Albus ein honigsüßes Lächeln und wandte sich der Tür zu.

% “Minerva?” said the old wizard from behind her. “\emph{Minerva!}”
„Minerva?“, fragte der alte Zauberer hinter ihr. „\emph{Minerva!}“

% The oaken door shut solidly behind her.
Die Eichentür schloss sich fest hinter ihr.

\later

% There wasn’t a lot of room between the brief stone walls that demarcated the vestibule to the Headmaster’s office, so although a lot of people had wanted to watch the protest, not many had been allowed to come. Just Professor Sinistra and Professor Vector, who were wearing the buttons, and the prefects Penelope Clearwater and Rose Brown and Jacqueline Preece, who were wearing the buttons. Behind \emph{them}, Professor McGonagall and Professor Sprout and Professor Flitwick, who weren’t wearing the buttons, scrutinizing the whole affair. Harry Potter and the Head Boy of Hogwarts were there, and the boy prefects Percy Weasley and Oliver Beatson, all wearing the buttons to show Solidarity. And of course the eight founding members of \SPHEW, forming a picket line next to the gargoyles with their signs. Hermione’s own sign, attached to a solid wooden handle which seemed to weigh heavier and heavier in her hands as the seconds passed, said NOBODY’S SIDEKICK.
Zwischen den engen Steinmauern, die den Vorraum zum Büro des Schulleiters abgrenzten, war nicht viel Platz, und obwohl viele Leute dem Protest zuschauen wollten, hatten nur wenige einen Platz bekommen. Nur Professor Sinistra und Professor Vector, die die Anstecker trugen, und die Vertrauensschüler Penelope Clearwater und Rose Brown und Jacqueline Preece, die die Anstecker trugen. \emph{Dahinter} Professor McGonagall und Professor Sprout und Professor Flitwick, die die Anstecker nicht trugen und die ganze Angelegenheit begutachteten. Harry Potter und der Schulsprecher von Hogwarts waren da, und die Vertrauensschüler Percy Weasley und Oliver Beatson, die alle die Anstecker trugen, um Solidarität zu zeigen. Und natürlich die acht Gründungsmitglieder von \SPHEW, die mit ihren Schildern eine Streikpostenkette neben den Wasserspeiern bildeten. Auf Hermines eigenem Schild, das an einem massiven Holzgriff befestigt war, der in ihren Händen immer schwerer zu werden schien, je mehr Sekunden vergingen, stand NIEMANDES GEHILFIN.

% And Professor Quirrell, who was leaning with his back against the far stone wall and watching with unreadable eyes. The Defence Professor had acquired one of her buttons, though she’d never sold one to him; and he wasn’t wearing it, but idly tossing it with one hand.
Und Professor Quirrell, der mit dem Rücken an der entfernten Steinwand lehnte und mit undurchdringlicher Miene zusah. Der Verteidigungsprofessor hatte einen ihrer Anstecker bekommen, obwohl sie ihm nie einen verkauft hatte; und er trug ihn nicht, sondern warf ihn müßig mit einer Hand hin und her.

% This whole idea had seemed like a much better idea four days ago, when the fires of her indignation had been burning fresh and hot, and she’d been facing the prospect of doing it all four days \emph{later} instead of \emph{right now.}
Diese ganze Idee war ihr vor vier Tagen viel besser vorgekommen, als die Feuer ihrer Empörung noch frisch und heiß gebrannt hatten und sie mit der Aussicht konfrontiert gewesen war, das alles vier Tage \emph{später} zu tun, statt \emph{jetzt}.

% But she had to carry on, because that was what heroes did, they carried on, and also because it had seemed infinitely too awful to tell everyone she was calling it off. Hermione wondered how much heroism had gone on for reasons like that. Most books didn’t \emph{say} “And then they refused to give up, no matter how sensible it would have been, because that would’ve been too embarrassing”; but a great deal of history made a lot more sense that way.
Aber sie musste weitermachen, denn das war es, was Helden taten, sie machten weiter, und auch, weil es unendlich peinlich gewesen wäre, es jetzt noch abzusagen. Hermine fragte sich, wie viel Heldentum nur aus solchen Gründen in die Geschichtsbücher eingegangen war. In den meisten Büchern \emph{stand} nicht: „Und dann weigerten sie sich aufzugeben, egal wie vernünftig es gewesen wäre, denn das wäre zu peinlich gewesen“; aber ein großer Teil der Weltgeschichte ergab auf diese Weise viel mehr Sinn.

% At 7:15\pm, Professor McGonagall had told her, Headmaster Dumbledore would come down and talk to them for a couple of minutes. Professor McGonagall had said not to be frightened—the Headmaster was a good person deep down, and they’d properly obtained the school’s authorization for the protest.
Um 19:15~Uhr, hatte Professor McGonagall ihr gesagt, würde Schulleiter Dumbledore herunterkommen und ein paar Minuten mit ihnen sprechen. Professor McGonagall hatte gesagt, dass sie keine Angst haben sollten—der Schulleiter war tief im Inneren ein guter Mensch, und sie hatten die Genehmigung der Schule für den Protest ordnungsgemäß erhalten.

% But Hermione was very very aware that even if she was doing it with signed permission, she was still Defying Authority.
Aber Hermine war sich dennoch sehr bewusst, dass sie, auch wenn sie es mit unterschriebener Erlaubnis tat, immer noch die Autoritätspersonen herausforderte.

% After she’d decided to be a hero, Hermione had done the obvious thing, and gone to the Hogwarts library and taken out books on how to be a hero. Then she’d returned those books back to their shelves, because it’d been patently obvious that none of the authors had been actual heroes themselves. Instead she’d just read five times over, until she’d memorized every word, the thirty inches by Godric Gryffindor that was all his autobiography and his life’s advice. (Or the English translation, anyway; she couldn’t read Latin yet.) Godric Gryffindor’s autobiography had been a lot more \emph{compressed} than the books Hermione was used to reading, he used \emph{one sentence} to say things that should’ve taken thirty inches just by themselves, and then there was \emph{another} sentence after that…
Nachdem sie beschlossen hatte, eine Heldin zu sein, hatte Hermine das Offensichtliche getan und war in die Hogwarts-Bibliothek gegangen, um sich Bücher darüber auszuleihen, wie man ein Held wird. Dann hatte sie die Bücher wieder in die Regale zurückgestellt, weil es offensichtlich war, dass keiner der Autoren selbst ein Held gewesen war. Stattdessen hatte sie einfach fünfmal hintereinander (bis sie jedes Wort auswendig kannte) die dreißig Zoll Pergamentrolle von Godric Gryffindor gelesen, die seine gesamte Autobiografie und seine Lebensratschläge waren. (Oder zumindest die englische Übersetzung; Latein konnte sie noch nicht lesen.) Godric Gryffindors Autobiografie war viel \emph{komprimierter} als die Bücher, die Hermine zu lesen gewohnt war, er benutzte \emph{einen Satz}, um Dinge zu sagen, die allein schon dreißig Zoll hätten einnehmen müssen, und dann kam noch ein \emph{weiterer} Satz danach…

% But it was clear from what she’d read that, while Defying Authority wasn’t the \emph{point} of being a hero, you couldn’t be a hero if you were too scared to do it. And Hermione Granger knew by now how others saw her, and she knew what other people thought she couldn’t do.
Aber nach dem, was sie gelesen hatte, war klar, dass es zwar \emph{nicht} darum ging, Autoritäten \emph{aus Prinzip} zu trotzen, aber man kein Held sein konnte, wenn man zu viel Angst hatte, es zu tun. Und Hermine Granger wusste inzwischen, wie andere sie sahen, und auch, was sie \emph{ihr} nicht zutrauten.

% Hermione hefted her picket sign a little higher and concentrated on breathing slowly and rhythmically instead of hyperventilating until she fell over.
Hermine hievte ihr Demonstrationsschild ein wenig höher und konzentrierte sich darauf, langsam und rhythmisch zu atmen, anstatt zu hyperventilieren, bis sie umkippte.

% “\emph{Really?}” said Miss~Preece in a tone of undisguised fascination. “They couldn’t \emph{vote?}”
„\emph{Wirklich?}“, sagte Miss~Preece in einem Ton unverhohlener Faszination. „Sie durften nicht \emph{wählen}?“

% “Indeed,” said Professor Sinistra. (The Astronomy Professor’s hair was still dark, and her dark face only slightly lined; Hermione \emph{would} have guessed her age at around seventy, except—) “I quite remember my mother’s rejoicing when they announced the Qualification of Women Act, although she did not actually qualify.” (Which meant that Professor Sinistra had been around her Muggle family in 1918.) “And that wasn’t the worst of it. Why, just a few centuries earlier—”
„In der Tat“, sagte Professor Sinistra. (Das Haar der Astronomieprofessorin war immer noch dunkel und ihr dunkles Gesicht nur leicht faltig; Hermine \emph{hätte} ihr Alter auf etwa siebzig geschätzt, allerdings—) „Ich kann mich noch gut an den Jubel meiner Mutter erinnern, als der Qualification of Women Act beschlossen wurde, obwohl es gar nicht für sie galt.“ (Was bedeutete, dass Professor Sinistra 1918 bei ihrer Muggelfamilie gelebt hatte.) „Und das war nicht das Schlimmste daran. Denn nur ein paar Jahrhunderte früher—“

% Thirty seconds later all the non-Muggle-borns, male and female both, were staring at Professor Sinistra with utterly shocked expressions. Hannah had dropped her sign.
Dreißig Sekunden später starrten alle Nicht-Muggelstämmigen, sowohl männliche als auch weibliche, Professor Sinistra mit völlig schockierten Mienen an. Hannah hatte ihr Schild fallen gelassen.

% “And \emph{that} wasn’t the worst of it either, not by half,” finished Professor Sinistra. “But you see where this sort of thing could potentially lead.”
„Und \emph{das} war auch nicht das Schlimmste, bei weitem nicht“, beendete Professor Sinistra. „Aber Sie sehen, wohin so etwas potenziell führen kann.“

% “Merlin preserve us,” said Penelope Clearwater in a strangled voice. “You mean \emph{that’s} how men would treat us if we didn’t have wands to defend ourselves?”
„Merlin bewahre uns“, sagte Penelope Clearwater mit erstickter Stimme. „Sie meinen, \emph{so} würden uns Männer behandeln, wenn wir keine Zauberstäbe hätten, um uns zu verteidigen?“

% “\emph{Hey!}” said one of the boy prefects. “\emph{That’s} not—”
„\emph{Hey!}“, sagte einer der jungen Vertrauensschüler. „\emph{Das ist} nicht—“

% There was a short, sardonic laugh from the direction of Professor Quirrell. When Hermione turned her head to look she saw that the Defence Professor was still idly toying with the button, not bothering to glance up at the rest of them, as he said, “Such is human nature, Miss~Clearwater. Rest assured that \emph{you} would be no kinder, if witches had wands and men lacked them.”
Ein kurzes, sardonisches Lachen ertönte aus der Richtung von Professor Quirrell. Als Hermine den Kopf drehte, um nachzusehen, sah sie, dass der Verteidigungsprofessor immer noch müßig mit dem Anstecker herumspielte. Er machte sich nicht die Mühe, zu ihnen aufzublicken, als er antwortete: „So ist die menschliche Natur, Miss~Clearwater. Seien Sie versichert, dass \emph{Sie} nicht freundlicher wären, wenn Hexen Zauberstäbe hätten und Männer nicht.“

% “I hardly think so!” snapped Professor Sinistra.
„Das glaube ich kaum!“, entgegnete Professor Sinistra brüskiert.

% A cold chuckle. “I suspect it happens more often than any dare suggest, in the proudest pureblood families. Some lonely witch spies a handsome Muggle; and thinks how very easy it would be, to slip the man a love potion, and by him be adored alone and utterly. And since she knows he can offer her no resistance, why, it is only natural for her to take from him whatever she pleases—”
Ein kaltes Lachen. „Ich vermute, es kommt selbst in den stolzesten Reinblüterfamilien öfter vor, als man zu glauben wagt. Irgendeine einsame Hexe erspäht einen gutaussehenden Muggel; und denkt, wie leicht es wäre, dem Mann einen Liebestrank unterzuschieben, und von ihm angebetet zu werden. Und da sie weiß, dass er ihr keinen Widerstand leisten kann, ist es nur natürlich, dass sie sich von ihm nimmt, was immer sie will—“

% “\emph{Professor Quirrell!}” said Professor McGonagall sharply.
„\emph{Professor Quirrell!}“, sagte Professor McGonagall scharf.

% “I’m sorry,” Professor Quirrell said mildly, his eyes still looking down on the button in his hand, “are we all still pretending it doesn’t happen? My apologies, then.”
„Es tut mir leid“, sagte Professor Quirrell milde, seine Augen immer noch auf den Anstecker in seiner Hand gerichtet, „tun wir alle immer noch so, als ob sowas nicht passiert? Dann entschuldige ich mich.“

% Professor Sinistra snapped, “And I suppose that wizards don’t—”
Professor Sinistra schnappte: „Und ich nehme an, dass Zauberer nie—“

% “There are \emph{children} present, Professors!” Again Professor McGonagall.
„Es sind \emph{Kinder} anwesend, Ich bitte Sie!“ Wieder Professor McGonagall.

% “Some do,” Professor Quirrell said equably, as though discussing the weather. “Although personally, I don’t.”
„Manche schon“, sagte Professor Quirrell gleichmütig, als würde er über das Wetter diskutieren. „Ich persönlich nicht“

% There was a bit of silence, for a time. Hermione put up her sign again—it had slipped down to her shoulder while she was listening. She’d never thought of that, not even a little, and now she was trying \emph{not} to think of it, and her stomach was feeling a bit queasy. She looked in Harry Potter’s direction, not quite knowing why she did; and she saw that Harry’s face was perfectly still. A chill ran down her spine before she looked away, not quite fast enough to miss the small nod that Harry gave her, as though they were agreeing on something.
Eine Zeit lang herrschte Schweigen. Hermine hob ihr Schild wieder hoch—es war bis auf Schulterhöhe heruntergerutscht, während sie zuhörte. Daran hatte sie nie gedacht, nicht einmal ein bisschen, und jetzt versuchte sie, \emph{nicht} daran zu denken, und ihr Magen fühlte sich etwas mulmig an. Sie schaute in Harry Potters Richtung, ohne recht zu wissen, warum sie es tat; und sie sah, dass Harrys Gesicht vollkommen ruhig war. Ein Schauer lief ihr über den Rücken, bevor sie wegschaute, nicht schnell genug um das kleine Nicken zu verpassen, das Harry ihr schenkte, als ob sie sich über etwas einig wären.

% “To be fair,” Professor Sinistra said after a while, “since I received my Hogwarts letter I can’t recall encountering any prejudice on account of being a woman, or coloured. No, now it is all for being a Muggle-born. I believe Miss~Granger said that it was \emph{just} with heroes that she found a problem, so far?”
„Um fair zu sein“, sagte Professor Sinistra nach einer Weile, „seit ich meinen Hogwarts-Brief erhalten habe, kann ich mich nicht daran erinnern, auf irgendwelche Vorurteile wegen meiner Hautfarbe oder meinem Geschlecht gestoßen zu sein. Nein, hier geht es nur darum, dass ich Muggelstämmige bin. Ich glaube, Miss~Granger hat gesagt, dass sie bisher \emph{nur} bei Helden ein Problem bemerkt hat.“

% It took Hermione a moment to recognize that she’d been asked the question, and then she said “Yes,” in a tone that squeaked a little. This whole thing had blown up a bit larger than she’d imagined when she’d started it.
Hermine brauchte einen Moment, um zu erkennen, dass ihr eine Frage gestellt worden war, und dann brachte sie ein „Ja“ zu Stande, wobei ihre Stimme ein wenig quietschte. Diese ganze Sache hatte sich ein bisschen mehr aufgebläht, als sie sich zu Beginn vorgestellt hatte.

% “What exactly did you check, Miss~Granger?” said Professor Vector. She looked older than Professor Sinistra, her hair starting to grey a little; Hermione hadn’t ever come close to Professor Vector in person until the Arithmancy Professor had asked her for a button.
„Was genau haben Sie überprüft, Miss~Granger?“, fragte Professor Vector. Sie sah älter aus als Professor Sinistra, ihr Haar begann, schon ein wenig zu ergrauen; Hermine hat mit Professor Vector noch nie ein Wort gewechselt, bis die Arithmantik-Professorin sie nach einem Anstecker gefragt hatte.

% “Um,” Hermione said, her voice a little high, “I checked the history books and there’s been as many woman Ministers of Magic as men. Then I looked at Supreme Mugwumps and there were a few more wizards than witches but not many. But if you look at people like famous Dark Wizard hunters, or people who’ve stopped invasions of Dark creatures, or people who’ve overthrown Dark Lords—”
„Ähm“, sagte Hermine, ihre Stimme ein wenig hoch, „ich habe in den Geschichtsbüchern nachgeschaut und es hat genauso viele weibliche Zaubereiminister gegeben wie männliche. Dann habe ich mir die Oberstern Mugwumps der Internationale Vereinigung von Zauberern angesehen und da gab es ein paar mehr Zauberer als Hexen, aber nicht viele. Aber wenn man sich Leute wie berühmte Jäger von dunklen Zauberern ansieht, oder Leute, die Invasionen von dunklen Kreaturen aufgehalten haben, oder Leute, die böse Herrscher gestürzt haben—“

% “And the Dark Wizards themselves, of course,” said Professor Quirrell. \emph{Now} the Defence Professor had looked up. “You may add that to your list, Miss~Granger. Among all the suspected Death Eaters we know of only two sorceresses, Bellatrix Black and Alecto Carrow. And I dare say that most wizards would be hard-pressed to name a single Dark Lady besides Baba Yaga.”
„Und natürlich die Dunklen Zauberer selbst“, sagte Professor Quirrell. \emph{Jetzt} schaut der Verteidigungsprofessor auf. „Sie können das zu Ihrer Liste hinzufügen, Miss~Granger. Von allen mutmaßlichen Todessern wissen wir nur von zwei Magierinnen, Bellatrix Black und Alecto Carrow. Und ich wage zu behaupten, dass die meisten Zauberer sich schwer tun würden, eine einzige Dunkle Herrscherin außer Baba Yaga zu nennen.“

% Hermione just stared at him.
Hermine starrte ihn nur an.

% He couldn’t \emph{possibly} be—
Das \emph{konnte} doch nicht—

% “Professor Quirrell,” said Professor Vector, “what exactly are you implying?”
„Professor Quirrell“, sagte Professor Vector, „was genau wollen Sie damit andeuten?“

% The Defence Professor raised the button so that the golden-lettered \SPHEW faced them, and said, “Heroes,” then turned the button to show its silver backside and said, “Dark Wizards. They are similar career paths followed by similar people, and one can hardly ask why young witches are turning away from one course without considering its reflection.”
Der Verteidigungsprofessor hob den Anstecker so an, dass der goldene Schriftzug \SPHEW zu lesen war, und sagte: „Helden“, dann drehte er den Anstecker um, sodass er seine silberne Rückseite zeigte, und sagte: „Dunkle Zauberer. Es sind ähnliche Karrierewege, die von ähnlichen Menschen beschritten werden, und man kann sich kaum fragen, warum sich junge Hexen von dem einen Weg abwenden, ohne sein Spiegelbild in Betracht zu ziehen.“

% “Oh, \emph{now} I see!” said Tracey Davis, speaking up so suddenly that Hermione gave a small start. “You’re joining our protest because you’re worried that not enough girls are becoming Dark Witches!” Then Tracey giggled, which Hermione couldn’t have managed at this point if you paid her a million pounds sterling.
„Oh, \emph{jetzt} kapier ich’s!“, sagte Tracey Davis und meldete sich so plötzlich zu Wort, dass Hermine einen kleinen Schreck bekam. „Sie schließen sich unserem Protest an, weil Sie sich Sorgen machen, dass nicht genug Mädchen zu Dunklen Magierinnen werden!“ Dann kicherte Tracey, was Hermine zu diesem Zeitpunkt nicht einmal geschafft hätte, wenn man ihr eine Million englische Pfund bezahlt hätte.

% There was a half-smile on Professor Quirrell’s face as he replied, “Not really, Miss~Davis. In truth I do not care about that sort of thing in the slightest. But it is futile to count the witches among Ministers of Magic and other such ordinary folk leading ordinary existences, when Grindelwald and Dumbledore and He-Who-Must-Not-Be-Named were all men.” The Defence Professor’s fingers idly spun the button, turning it over and over. “Then again, only a very few folk ever do anything interesting with their lives. What does it matter to you if \emph{they} are mostly witches or mostly wizards, so long as \emph{you} are not among them? And I suspect you will not be among them, Miss~Davis; for although you are ambitious, you have no ambition.”
Es lag ein halbes Lächeln auf Professor Quirrells Gesicht, als er antwortete: „Nicht wirklich, Miss~Davis. In Wahrheit interessiert mich diese Art von Dingen nicht im Geringsten. Aber es ist müßig, die Hexen unter den Zaubereiministern und anderen gewöhnlichen Leuten zu zählen, die ein gewöhnliches Leben führen, wo doch Grindelwald und Dumbledore und Er-dessen-Name-nicht-genannt-werden-darf alles Männer waren.“ Die Finger des Verteidigungsprofessors drehten den Anstecker untätig hin und her. „Andererseits machen nur die wenigsten Leute etwas Interessantes aus ihrem Leben. Was macht es für Sie aus, ob es überwiegend Hexen oder überwiegend Zauberer sind, solange Sie nicht zu ihnen gehören? Und ich vermute, Sie werden nicht zu ihnen gehören, Miss~Davis; denn obwohl Sie ehrgeizig sind, haben Sie keine Ambitionen.“

% “\emph{That’s not true!}” said Tracey indignantly. “And what’s it mean?”
„\emph{Das ist nicht wahr!}“, sagte Tracey entrüstet. „Und was soll das heißen?“

% Professor Quirrell straightened from where he had been leaning against the wall. “You were Sorted into Slytherin, Miss~Davis, and I expect that you will grasp at any opportunity for advancement which falls into your hands. But there is no great ambition that you are driven to accomplish, and you will not \emph{make} your opportunities. At best you will grasp your way upward into Minister of Magic, or some other high position of unimportance, never breaking the bounds of your existence.”
Professor Quirrell richtete sich von dort auf, wo er an der Wand gelehnt hatte. „Sie wurden nach Slytherin sortiert, Miss~Davis, und ich denke, dass Sie jede Gelegenheit zum Aufstieg ergreifen werden, die Ihnen in die Hände fällt. Aber sie haben kein großes Ziel, das Sie antreibt, und Sie werden jene Gelegenheiten nicht \emph{erschaffen}. Bestenfalls werden Sie sich bis zum Zaubereiminister oder einer anderen hohen, unbedeutenden Position empor hangeln, ohne jemals die Grenzen Ihrer Existenz zu überschreiten.“

% Then Professor Quirrell’s gaze shifted away from Tracey, he was looking at \emph{her}, the pale blue eyes staring at her with an awful intensity— “Tell me, Miss~Granger. Do \emph{you} have an ambition?”
Dann wandte sich Professor Quirrells Blick von Tracey ab, er sah \emph{sie} an, die blassblauen Augen starrten sie mit einer furchtbaren Intensität an— „Sagen Sie mir, Miss~Granger. Haben \emph{Sie} ein Ziel?“

% “Professor—” squeaked the high stern voice of Professor Flitwick, and then her Head of House’s voice cut off, and from the side of her vision Hermione saw that Harry had laid his hand on Professor Flitwick’s shoulder and was shaking his head, face looking very adult.
„Professor—“, quietschte die hohe, strenge Stimme von Professor Flitwick, und dann brach die Stimme ihres Hauslehrers ab, und aus dem Augenwinkel sah Hermine, dass Harry seine Hand auf Professor Flitwicks Schulter gelegt hatte und mit ernstem Gesichtsausdruck den Kopf schüttelte.

% Hermione felt like a deer caught in headlights.
Hermine fühlte sich wie ein Reh, das im Scheinwerferlicht stand.

% “What drove you to break your bounds, Miss~Granger?” said the Defence Professor, still gazing directly at her. “Why is getting good marks in class no longer enough? Is it true greatness that you seek? Does some aspect of the world dissatisfy you, that you must remake according to your will? Or is this all merely a child’s game to you? I will be quite disappointed if this is only about rivalling Harry Potter.”
„Was hat Sie dazu getrieben, Ihre Grenzen zu überschreiten, Miss~Granger?“, fragte der Verteidigungsprofessor und blickte sie immer noch direkt an. „Warum reicht es nicht mehr aus, gute Noten im Unterricht zu bekommen? Ist es wahre Größe, die Sie suchen? Sind Sie mit irgendeinem Aspekt der Welt unzufrieden, den Sie nach Ihrem Willen umgestalten müssen? Oder ist das alles nur ein Spiel für Sie? Ich wäre sehr enttäuscht, wenn es nur darum ginge, Harry Potter Konkurrenz zu machen.“

% “I—” said Hermione, her voice so high-pitched it made a sort of peeping sound, but then she couldn’t think of what else to say.
„Ich—“, sagte Hermine, aber ihre Stimme war so hoch, dass sie nur eine Art Piepsen von sich gab, aber dann fiel ihr nicht ein, was sie noch sagen sollte.

% “You may take a moment to think, if you like,” said Professor Quirrell. “Pretend it is a homework essay, six inches due Thursday. I hear you are quite eloquent in them.”
„Sie können sich einen Moment Zeit zum Nachdenken nehmen, wenn Sie möchten“, sagte Professor Quirrell. „Stellen Sie sich vor, es ist ein Aufsatz, sechs Zoll, Abgabe am Donnerstag. Ich habe gehört, dass Sie darin recht eloquent sind.“

% Everyone was looking at her.
Alle sahen sie an.

% “I—” said Hermione. “I don’t agree with one single thing you just said, anywhere.”
„Ich—“, sagte Hermine. „Ich stimme Ihnen, bei dem was Sie gerade gesagt haben, in keinster Weise zu, nirgendwo.“

% “Well spoken,” came Professor McGonagall’s crisp voice.
„Gut gesagt“, kam Professor McGonagalls klare Stimme.

% Professor Quirrell’s gaze did not waver. “That is not six inches, Miss~Granger. \emph{Something} drives you to defy the Headmaster’s verdict and gather followers about yourself. Perhaps it is something you prefer not to speak aloud?”
Professor Quirrells Blick wankte nicht. „Das sind keine sechs Zoll, Miss~Granger. \emph{Irgendetwas} treibt Sie dazu, sich dem Urteil des Schulleiters zu widersetzen und Anhänger um sich zu scharen. Vielleicht ist es etwas, das Sie lieber nicht laut aussprechen wollen?“

% Hermione knew the correct answer wouldn’t impress Professor Quirrell, but it was the correct answer, so she said it. “I don’t think you need ambition to be a hero,” Hermione said. Her voice wavered but it didn’t crack. “I think you just have to do what’s right. And they’re not my followers, we’re friends.”
Hermine wusste, dass die richtige Antwort Professor Quirrell nicht beeindrucken würde, aber es war die richtige Antwort, also sagte sie sie trotzdem. „Ich glaube nicht, dass man Ehrgeiz oder ein Ziel braucht, um ein Held zu sein“, sagte Hermine. Ihre Stimme schwankte, aber sie brach nicht. „Ich glaube, man muss nur das Richtige tun. Und sie sind nicht meine Gefolgsleute, wir sind Freunde.“

% Professor Quirrell leaned back against the wall again. The half-smile had faded from his face. “Most folk tell themselves they are doing right, Miss~Granger. They do not thereby rise above the ordinary.”
Professor Quirrell lehnte sich wieder an die Wand. Das angedeutete Lächeln war aus seinem Gesicht verschwunden. „Die meisten Leute reden sich ein, dass sie das Richtige tun, Miss~Granger. Dabei erheben sie sich nicht über das Gewöhnliche.“

% Hermione took a couple of deep breaths, trying to be brave. “It’s not \emph{about} being not ordinary,” she said as stoutly as she could. “But I think if someone just tries to do what’s right, over and over again, and they’re not too lazy to do all the work it takes, and they think about what they’re doing, and they’re brave enough to do it even when they’re scared—” Hermione paused for an instant, her eyes darting to Tracey and Daphne, “—and they cleverly plan how to do it—and they don’t just do what other people do—then I think someone like that would already get into enough trouble.”
Hermine holte ein paar Mal tief Luft und versuchte, tapfer zu sein. „Es \emph{geht nicht darum}, nicht gewöhnlich zu sein“, sagte sie so tapfer, wie sie konnte. „Aber ich denke, wenn jemand einfach nur versucht, das Richtige zu tun, immer und immer wieder, und sie nicht zu faul sind, sich die ganze Arbeit zu machen, die dazu nötig ist, und sie darüber nachdenken, was sie tun, und mutig genug ist, es zu tun, auch wenn sie Angst haben—“ Hermine hielt für einen Moment inne, ihre Augen huschten zu Tracey und Daphne, „—und sie klug planen, wie sie vorgehen werden—und sie nicht nur einfach das machen, was andere Leute machen—dann denke ich, dass so jemand schon genug Ärger bekommen würde.“

% Some of the girls and boys chuckled, as did Professor McGonagall, who looked wry and proud at the same time.
Einige der Mädchen und Jungen kicherten, ebenso wie Professor McGonagall, die amüsiert und stolz zugleich aussah.

% “You may be right about that,” said the Defence Professor, his eyes half-lidded. He tossed Hermione the button, and she caught it without thinking. “My donation to your cause, Miss~Granger. I understand that they are worth two Sickles.”
„Da mögen Sie recht haben“, sagte der Verteidigungsprofessor mit halb geschlossenen Augen. Er warf Hermine den Anstecker zu, und sie fing ihn auf, ohne nachzudenken. „Meine Spende für Ihre Sache, Miss~Granger. Ich glaube, dass die zwei Sickel wert sind.“

% The Defence Professor turned and walked away without another word.
Der Verteidigungsprofessor drehte sich um und ging ohne ein weiteres Wort davon.

% “I thought I was going to faint!” gasped Hannah after his footsteps had faded, and she heard some of the other girls letting out their breath or putting down their signs for a moment.
„Ich dachte, ich werde ohnmächtig!“, keuchte Hannah, nachdem seine Schritte verklungen waren, und sie hörte, wie einige der anderen Mädchen den angehaltenen Atem ausstießen oder ihre Schilder für einen Moment ablegten.

% “I do \emph{too} have an ambition!” said Tracey, who seemed to be almost on the verge of tears. “I’m—I’m—I’ll figure out what it is by tomorrow, but I have one, I’m sure!”
„Ich habe \emph{auch} ein Ziel!“, sagte Tracey, die fast am Rande der Tränen zu sein schien. „Ich—ich—ich werde bis morgen herausfinden, was es ist, aber ich habe eins, da bin ich mir sicher!“

% “If you really can’t think of anything,” Daphne said, giving Tracey a comforting pat on the shoulder, “just go with the oldie but goodie and try to take over the world.”
„Wenn dir wirklich nichts einfällt“, sagte Daphne und gab Tracey einen tröstenden Klaps auf die Schulter, „nimm einfach den Klassiker und versuche, die Welt zu erobern.“

% “Hey!” said Susan sharply. “You’re supposed to be heroes now! That means you have to be \emph{good!}”
„Hey!“, sagte Susan scharf. „Ihr sollt doch jetzt Helden sein! Das heißt, ihr müsst \emph{gut} sein!“

% “No, it’s all right,” said Lavender, “I’m pretty sure General Chaos wants to take over the world and \emph{he’s} sort of a good guy.”
„Nein, das ist schon in Ordnung“, sagte Lavender, „ich bin mir ziemlich sicher, dass General Chaos die Welt übernehmen will und \emph{er} ist schon irgendwie einer der Guten.“

% More conversation was going on behind the picket line. “My goodness,” said Penelope Clearwater. “I think that’s the most \emph{overtly} evil Defence Professor we’ve ever had.”
Hinter den Demonstrantinnen wurde weiter diskutiert. „Meine Güte“, sagte Penelope Clearwater. „Ich glaube, das ist der \emph{am} \emph{Offensichtlichsten} böse Verteidigungsprofessor, den wir je hatten.“

% Professor McGonagall coughed warningly, and the Head Boy said, “You weren’t around for Professor Barney,” which made several people twitch.
Professor McGonagall hustete warnend, und der Schulsprecher sagte: „Du hast Professor Barney nicht erlebt“, was mehrere Anwesende zusammenzucken ließ.

% “Professor Quirrell just \emph{talks} like that,” said Harry Potter, though he sounded less certain than before. “I mean, think about it, he doesn’t \emph{do} anything like what Professor Snape does—”
„Professor Quirrell \emph{redet} einfach so“, sagte Harry Potter, obwohl er weniger sicher klang als zuvor. „Ich meine, überlegt doch mal, im Gegensatz zu Professor Snape \emph{handelt} er nicht so—“

% “Mr~Potter,” squeaked Professor Flitwick, voice polite and face stern, “why did you ask me to stay silent?”
„Mr~Potter“, quietschte Professor Flitwick, mit höflicher Stimme und strenger Miene, „warum haben Sie mich gebeten, nichts zu sagen?“

% “Professor Quirrell was testing Hermione to see if he wanted to be her mysterious old wizard,” Harry said. “Which totally would not have worked out in any way, shape, or form, but she had to answer for herself.”
„Professor Quirrell hat Hermine getestet, um zu sehen, ob er ihr \emph{mysteriöser alter Zauberer} sein will“, sagte Harry. „Was auf keinen Fall geklappt hätte, aber sie musste schon für sich selbst antworten.“

% Hermione blinked.
Hermine blinzelte.

% Then Hermione blinked again, as she realized that it was Professor Quirrell who was Harry Potter’s mysterious old wizard, and not Dumbledore at all, and that \emph{really wasn’t a good sign—}
Dann blinzelte Hermine noch einmal, als ihr klar wurde, dass es Professor Quirrell war, der Harry Potters mysteriöser alter Zauberer war, und gar nicht Dumbledore, und das \emph{war wirklich kein gutes Zeichen}—

% A rumbling noise filled the small stone vestibule, and Hermione, her nerves already on edge, spun rapidly around, almost dropping her protest sign as her other hand darted toward her wand.
Ein rumpelndes Geräusch erfüllte den kleinen steinernen Vorraum, und Hermine, die bereits mit den Nerven am Ende war, wirbelte schnell herum und ließ fast ihr Protestschild fallen, während ihre andere Hand zu ihrem Zauberstab wanderte.

% The gargoyles were stepping aside, the Flowing Stone rumbling like rock as it moved like flesh. The huge ugly figures waited only briefly, dead grey eyes staring out in silent vigil. Then the great gargoyles folded their wings back into place and stepped back into their former positions, the Flowing Stone not changing its outward appearance at all as it returned from flexibility to motionlessness, and the brief gap in the stone of Hogwarts was solid once more.
Die Wasserspeier traten zur Seite, der Fließende Stein rumpelte wie Fels, während er sich wie ein Wesen aus Fleisch und Blut bewegte. Die riesigen hässlichen Gestalten warteten nur kurz, totengraue Augen starrten in stummer Wachsamkeit geradeaus. Dann klappten die großen Wasserspeier ihre Flügel wieder ein und traten in ihre frühere Position zurück, der Fließende Stein veränderte sein Äußeres nicht im Geringsten, als er von Flexibilität zu Bewegungslosigkeit zurückkehrte, und die kurzzeitige Lücke im Stein von Hogwarts war wieder geschlossen.

% And before them all, wearing robes of bright purple that probably only looked hideous if you were Muggle-born, stood the towering form of Albus Percival Wulfric Brian Dumbledore, the Headmaster of Hogwarts, the Chief Warlock of the Wizengamot, the Supreme Mugwump of the International Confederation of Wizards, the vanquisher of the Dark Lord Grindelwald and protector of Britain, the rediscoverer of the fabled Twelve Uses of Dragon’s Blood, the most powerful wizard alive; and he was looking at \emph{her}, Hermione Jean Granger, General of the recently expanded Sunshine Regiment, who was getting the best grades in the first year of Hogwarts classes, and who had declared herself a heroine.
Und vor ihnen allen, in leuchtend violetten Umhängen, die wahrscheinlich nur für Muggelstämmige furchtbar aussahen, stand die hoch aufragende Gestalt von Albus Percival Wulfric Brian Dumbledore, dem Schulleiter von Hogwarts, dem Großmeister des Zaubergamots, dem Oberstern Mugwump der Internationalen Konföderation der Zauberer, dem Bezwinger des Dunklen Lords Grindelwald und Beschützer Großbritanniens, der Wiederentdecker der sagenumwobenen Zwölf Gebräuche von Drachenblut, der mächtigste lebende Zauberer; und er sah \emph{sie} an, Hermine Jean Granger, Generalin des kürzlich erweiterten Sonnenschein-Regiments, die im ersten Jahr der Hogwarts-Klassen die besten Noten bekam und sich selbst zur Heldin erklärt hatte.

% Even her \emph{name} was shorter than his.
Sogar ihr \emph{Name} war kürzer als seiner.

% The Headmaster smiled benevolently at her, his wrinkle-lined eyes twinkling cheerfully beneath their half-circles of glass, and said, “Hello, Miss~Granger.”
Der Schulleiter lächelte sie wohlwollend an, seine faltigen Augen funkelten fröhlich unter ihren Halbkreisen aus Glas, und sagte: „Hallo, Miss~Granger.“

% The odd thing was that it wasn’t nearly as scary as talking to Professor Quirrell. “Hello, Headmaster Dumbledore,” Hermione said with only a slight quaver in her voice.
Das Seltsame war, dass es nicht annähernd so beängstigend war wie das Gespräch mit Professor Quirrell. „Hallo, Schulleiter Dumbledore“, sagte Hermine mit nur einem leichten Zittern in der Stimme.

% “Miss~Granger,” said Dumbledore, now looking more serious, “I think you and I may have had a bit of a misunderstanding. I did not mean to imply that you could not, or should not be a hero. I certainly did not mean to imply that witches in general should not be heroes. Only that you were…a bit young, to be thinking of such things.”
„Miss~Granger“, sagte Dumbledore, nun mit ernsterem Blick, „ich glaube, wir beide haben ein kleines Missverständnis gehabt. Ich wollte nicht andeuten, dass Sie keine Heldin sein können oder sollten. Ich wollte im Besonderen auch nicht andeuten, dass Hexen im Allgemeinen keine Helden sein sollten. Nur, dass Sie…ein bisschen jung bist, um an solche Dinge zu denken.“

% Hermione, unable to help herself, glanced at Professor McGonagall and saw that Professor McGonagall was giving her an encouraging smile—or she was giving the two of them \emph{some} kind of smile, anyway—so Hermione looked back at the Headmaster and said, the small quaver in her voice a little larger now, “Since you became Headmaster forty years ago, there’ve been eleven students to graduate Hogwarts who became heroes, I mean people like Lupe Cazaril and so on, and \emph{ten} of those were boys. Cimorene Linderwall was the only witch.”
Hermine, die sich nicht darin hindern konnte, blickte zu Professor McGonagall hinüber und sah, dass Professor McGonagall ihr ein aufmunterndes Lächeln schenkte—oder sie schenkte den beiden \emph{irgendeine} Art Lächeln—also blickte Hermine wieder zum Schulleiter und sagte, nun mit etwas mehr Zittern in ihrer Stimme: „Seit Sie vor vierzig Jahren Schulleiter wurden, gab es elf Hogwarts-Absolventen, die zu Helden wurden. Ich meine damit Leute wie Lupe Cazaril und so weiter, und \emph{zehn} davon waren Jungs. Cimorene Linderwall war die einzige Hexe.“

% “Hm,” said the Headmaster. There was a thoughtful expression on his face; he at least \emph{seemed} to be thinking about it. “Miss~Granger, I have never been one for tallying such numbers. Often it is too much easier to count than to understand. Many good people have come out of Hogwarts, witches and wizards both; those famed as heroes are only one kind of good person, and perhaps not the highest. You did not include Alice Longbottom or Lily Potter in your reckoning…But leave that aside. Tell me, Miss~Granger, did you tally how many heroes came out of Hogwarts in the forty years before me? For in that time I can recall only three now called heroes; and among those three, no witches at all.”
„Hm“, sagte der Schulleiter. Es lag ein nachdenklicher Ausdruck auf seinem Gesicht; er schien zumindest darüber nachzudenken. „Miss~Granger, ich war noch nie einer, der sich viel von solchen Zahlen leiten ließ. Oft ist es viel zu einfach, zu zählen, als zu verstehen. Aus Hogwarts sind viele gute Menschen hervorgegangen, sowohl Hexen als auch Zauberer; Und die, die als Helden gefeiert werden, sind nur eine bestimmte Art von guten Menschen, und vielleicht nicht die beste. Sie haben zum Beispiel Alice Longbottom oder Lily Potter nicht in Ihre Rechnung einbezogen…Aber lassen wir das beiseite. Sagen Sie mir, Miss~Granger, haben Sie gezählt, wie viele Helden Hogwarts in den 40 Jahren vor mir hervorgebracht hat? Denn in dieser Zeit kann ich mich nur an drei erinnern, die heute Helden genannt werden; und unter diesen drei nicht eine Hexe.“

% “I’m not trying to say it’s \emph{just} you!” Hermione said. “Only I think maybe a \emph{lot} of people, like the Headmasters before you too, maybe even your whole society and everything, might be discouraging girls.”
„Ich will damit nicht sagen, dass es \emph{nur} an Ihnen liegt!“ sagte Hermine. „Ich denke nur, dass vielleicht \emph{viele} Leute, so wie die Schulleiter vor Ihnen, und vielleicht sogar eure ganze Gesellschaft und alles, Mädchen entmutigen.“

% The old wizard sighed. His half-glasses eyes looked only at her, as though they were the only two people present. “Miss~Granger, it might be possible to discourage witches from becoming Charms Mistresses, or Quidditch players, or even Aurors. But not heroes. If someone is meant to be a hero then a hero they will be. They will walk through fire and swim through ice. Dementors will not stop them, nor the deaths of friends, and not discouragement either.”
Der alte Zauberer seufzte. Seine hellblauen Augen hinter den halbmondförmigen Gläsern sahen nur sie ruhig an, als wären sie die einzigen beiden anwesenden Menschen. „Miss~Granger, man kann vielleicht Hexen davon abhalten, Zauberkunstlehrerin zu werden, oder Quidditch-Spielerin oder sogar Aurorin. Bei Helden ist das anders. Wenn jemand dazu bestimmt ist, ein Held zu sein, dann wird er ein Held sein. Sie werden durch Feuer gehen und durch Eis schwimmen. Dementoren werden sie nicht aufhalten, auch nicht der Tod von Freunden, und auch nicht Entmutigung.“

% “Well,” Hermione said, and paused, struggling with the words. “Well, I mean…what if that’s not \emph{actually} true? I mean, to \emph{me} it seems that if you want more witches to be heroes, you ought to teach them heroing.”
„Nun“, sagte Hermine und hielt inne, um nach Worten zu ringen. „Nun, aber…~aber was ist, wenn das \emph{in Wirklichkeit} gar nicht stimmt? \emph{Mir} scheint, dass wenn man will, dass mehr Hexen Helden werden, sollte man ihnen Heldentum beibringen.“

% “Many boys and girls are heroes in their dreams,” Dumbledore said quietly. He did not look at any of the other girls, only at her. “Fewer in the waking world. Many have stood their ground and faced the darkness when it comes for them. Fewer come for the darkness and force it to face them. It is a hard life, sometimes lonely, often short. I have told none to refuse that calling, but neither would I wish to increase their number.”
„Viele Jungen und Mädchen sind Helden in ihren Träumen“, sagte Dumbledore leise. Er sah keines der anderen Mädchen an, nur sie. „In der wachen Welt sind es weniger. Viele haben sich behauptet und sich der Dunkelheit gestellt, als diese sie holen kam. Wenige gehen der Dunkelheit entgegen und zwingen sie, sich ihnen zu stellen. Es ist ein hartes Leben, manchmal einsam, oft kurz. Ich habe niemandem gesagt, er solle sich dieser Berufung verweigern, aber ich würde auch nicht wünschen, ihre Zahl zu erhöhen.“

% Hermione hesitated; there was something in the lined face that stopped her, like a hint to all the emotion that wasn’t being displayed, years and years of it…
Hermine zögerte; da war etwas in dem gezeichneten Gesicht, das sie aufhielt, wie ein Hinweis auf all die Emotionen, die \emph{nicht} gezeigt wurden, über Jahrzehnte angesammelt…

% \emph{Maybe if there were more heroes, their lives wouldn’t be so lonely, or so short.}
\emph{Wenn es mehr Helden gäbe, wäre ihr Leben vielleicht nicht so einsam, oder so kurz.}

% She couldn’t bring herself to say that, though, not to him.
Sie brachte es nicht über sich, das zu sagen, nicht zu ihm.

% “But the point is moot,” said the old wizard. He smiled, a bit ruefully she thought. “Miss~Granger, you cannot teach heroism like you would teach Charms. You cannot assign twelve inches on how to carry on when all hope seems lost. You cannot rehearse students on when to stand up and tell the Headmaster he has done wrong. Heroes are born, not taught. And for whatever reason, more of them are born boys than girls.” The Headmaster shrugged, as if to say that \emph{he} was helpless to do anything about that.
„Aber dieser Punkt ist dennoch unwichtig“, sagte der alte Zauberer. Er lächelte, ein bisschen reumütig, wie sie fand. „Miss~Granger, man kann Heldentum nicht lehren, wie man Zauberei lehren würde. Sie können nicht einen zwölf Zoll Aufsatz als Hausaufgabe aufgeben, wie man weitermacht, wenn alle Hoffnung verloren scheint. Man kann Schülern nicht beibringen, wann man aufsteht und dem Schulleiter sagt, dass er Unrecht getan hat. Helden werden geboren, nicht gelehrt. Und aus welchem Grund auch immer, werden mehr von ihnen als Jungen geboren als als Mädchen.“ Der Schulleiter zuckte mit den Schultern, als wollte er sagen, dass er nichts dagegen tun könne.

% “Um,” Hermione said. She couldn’t help it, she glanced behind her.
„Ähm“, sagte Hermine. Sie konnte nicht anders, sie blickte hinter sich.

% Professor Sinistra was looking a bit indignant. And it \emph{wasn’t} true that everyone was staring at her like she’d just been silly, the way she’d started to imagine while she was listening to Dumbledore.
Professor Sinistra sah ein wenig entrüstet aus. Und es \emph{stimmte nicht}, dass alle sie anstarrten, als wäre sie nur ein naives, kleines Mädchen, so wie sie es sich vorzustellen begann, während sie Dumbledore zuhörte.

% Hermione turned back to face Dumbledore again, took a deep breath, and said, “Well, maybe people who are going to be heroes, will be heroes no matter what. But I don’t see how anyone could really \emph{know} that, aside from just saying it afterwards. And when \emph{I} told you that I wanted to be a hero, you weren’t very encouraging.”
Hermine wandte sich wieder Dumbledore zu, holte tief Luft und sagte: „Nun, vielleicht werden Leute, die Helden werden sollen, Helden sein, egal was passiert. Aber ich wüsste nicht, wie man das wirklich \emph{wissen} könnte, abgesehen davon, dass man es hinterher einfach sagt. Und als \emph{ich} Ihnen gesagt habe, dass ich ein Held werden will, waren Sie nicht sehr ermutigend.“

% “Mr~Potter,” the Headmaster said mildly. His eyes didn’t leave hers. “Please tell Miss~Granger your impression of our own first meeting. Would you say that I was encouraging? Speak the truth.”
„Mr~Potter“, sagte der Schulleiter milde. Seine Augen verließen ihre nicht. „Bitte schildern Sie Miss~Granger Ihren Eindruck von unserer eigenen ersten Begegnung. Würden Sie sagen, dass ich ermutigend war? Sagen Sie die Wahrheit.“

% There was a pause.
Es gab eine Pause.

% “Mr~Potter?” said Professor Vector’s voice from behind her, sounding puzzled.
„Mr~Potter?“, erklang Professor Vectors Stimme hinter ihr und klang verwirrt.

% “Um,” Harry’s voice said from further back, sounding extremely reluctant. “Um…well, actually in my case the Headmaster set fire to a chicken.”
„Ähm“, sagte Harrys Stimme von weiter hinten und klang äußerst zögernd. „Ähm…nun, in meinem Fall hat der Schulleiter ein Huhn in Brand gesetzt.“

% “He \emph{what?}” Hermione blurted, only there were several other people exclaiming things at around the same time so she wasn’t sure anyone heard her.
„Er hat \emph{was}?“, platzte Hermine heraus, nur dass es mehrere andere Leute gab, die ungefähr zur gleichen Zeit etwas riefen, sodass sie nicht sicher war, dass jemand sie hörte.

% Dumbledore went on gazing at her, looking perfectly serious.
Dumbledore starrte sie weiter an und sah vollkommen ernst aus.

% “I didn’t know about Fawkes,” Harry’s voice said rapidly, “so he told me that Fawkes was a phœnix, while he was pointing to a chicken on Fawkes’s stand so I’d think \emph{that} was Fawkes, and then he set the chicken on fire—and also he gave me this big rock and told me it had belonged to my father and I ought to carry it everywhere—”
„Ich wusste nichts von Fawkes“, sagte Harrys Stimme schnell, „also sagte er mir, dass Fawkes ein Phönix sei, während er auf ein Huhn auf Fawkes‘ Ständer zeigte, damit ich dachte, \emph{das} sei Fawkes, und dann zündete er das Huhn an—und außerdem gab er mir diesen Felsbrocken und sagte mir, er habe meinem Vater gehört und ich solle ihn überallhin mitnehmen—“

% “But that’s \emph{crazy!}” Susan blurted out.
„Aber das ist doch \emph{verrückt}!“, platzte es Susan heraus.

% There was a sudden hush.
Plötzlich herrschte Stille.

% The Headmaster slowly turned his head to stare at Susan.
Der Schulleiter drehte langsam seinen Kopf und starrte Susan an.

% “I—” said Susan. “I mean—I—”
„Ich—“, sagte Susan. „Ich meine—ich—“

% The Headmaster leaned down until he was face to face with the young girl.
Der Schulleiter beugte sich hinunter, bis er dem jungen Mädchen direkt gegenüberstand.

% “I didn’t—” said Susan.
„Ich habe nicht—“, sagte Susan.

% Dumbledore put a finger to his lips and twiddled them, making a \emph{wibble-wibble-wibble} sound.
Dumbledore legte einen Finger auf seine Lippen und machte bl-bl-bl.

% The Headmaster straightened up again and said, “Well, my good heroines, it has been pleasant speaking to you, but alas, much else remains to do this day. Still, rest assured that I am inscrutable to everyone, not just witches.”
Der Schulleiter richtete sich wieder auf und sagte: „Nun, meine lieben Heldinnen, es war angenehm, mit euch zu sprechen, aber leider bleibt heute noch viel zu tun. Seid jedoch versichert, dass ich für jeden unergründlich bin, nicht nur für Hexen.“

% The gargoyles stepped aside, the Flowing Stone rumbling like rock as it moved like flesh.
Die Wasserspeier traten zur Seite und der Fließende Stein rumpelte wie Fels übereinander, als er sich bewegte.

% The huge ugly figures waited briefly with dead grey eyes staring out in silent vigil, as Albus Percival Wulfric Brian Dumbledore, smiling as benevolently as when he’d first emerged from his office, stepped back into the Enchantment of the Endless Stair.
Die riesigen hässlichen Gestalten warteten kurz mit toten grauen Augen, die in stummer Wachsamkeit hinausstarrten, als Albus Percival Wulfric Brian Dumbledore, so wohlwollend lächelnd wie als sein Büro verlassen hatte, zurück auf die erste Stufe der Endlosen Wendeltreppe trat.

% Then the great gargoyles folded their wings back into place and stepped back into their former positions, only one last brief “Bwa ha ha!” echoing out before the gap closed.
Dann klappten die großen Wasserspeier ihre Flügel wieder ein und traten in ihre früheren Positionen zurück, wobei sie noch ein letztes kurzes „Bwa-ha-ha-ha!“ hörten, bevor sich die Lücke schloss.

% There was a long silence.
Es entstand eine lange Pause.

% “He \emph{really} set a chicken on fire?” said Hannah.
„Er hat \emph{wirklich} ein Huhn angezündet?“, sagte Hannah.

\later

% The eight of them had continued protesting even after that, but to be honest their heart had gone out of it.
Die acht hatten auch danach noch weiter protestiert, aber um ehrlich zu sein, waren sie nicht mehr so bei der Sache.

% It \emph{had} been established, after some careful questions from Professor Flitwick, that Harry Potter hadn’t smelled the chicken burning. Which meant that it had probably been a pebble or something, Transfigured into a chicken and then enclosed in a Boundary Charm to make sure that no smoke escaped into the air—both Professor Flitwick and Professor McGonagall had been very emphatic about nobody trying that without their supervision.
Nach einigen vorsichtigen Fragen von Professor Flitwick war festgestellt worden, dass Harry Potter das brennende Huhn nicht gerochen hatte. Was bedeutete, dass es sich wahrscheinlich um einen Kieselstein oder so etwas gehandelt hatte, der in ein Huhn verwandelt und dann mit einem Begrenzungszauber eingeschlossen wurde, um sicherzustellen, dass kein Rauch in die Luft entwich—sowohl Professor Flitwick als auch Professor McGonagall hatten sehr nachdrücklich darauf hingewiesen, dass niemand so etwas ohne ihre Aufsicht versuchen durfte.

% But still…
Aber trotzdem…

% But still…what?
Aber trotzdem…was bei Merlin?

% Hermione didn’t even \emph{know} but still what.
Hermine wusste nicht einmal, was das bedeuten sollte.

% But \emph{still}.
Aber \emph{trotzdem}.

% After a lot of glances exchanged between girls none of whom had wanted to be first to say it, Hermione had declared the protest over, and the adults and boys had drifted off.
Nach vielen Blicken, die zwischen den Mädchen ausgetauscht worden waren, von denen keine die Erste sein wollte, die es sagte, hatte Hermine den Protest für beendet erklärt, und die Lehrer und Schüler waren gegangen.

% “You don’t think we were being unfair to Dumbledore, do you?” said Susan as the heroines walked away to the sound of eight pairs of feet treading on the stone paving of Hogwarts’s corridors. “I mean, if he \emph{is} crazy at everyone and not just at witches then it’s not discrimination, right?”
„Du glaubst doch nicht, dass wir Dumbledore gegenüber unfair waren, oder?“, sagte Susan, als die Heldinnen begleitet vom Geräusch von acht Paar Füßen auf dem Steinpflaster, durch die Korridore von Hogwarts gingen. „Ich meine, wenn er allen gegenüber verrückt ist und nicht nur Hexen gegenüber, dann ist das doch keine Diskriminierung, oder?“

% “I don’t want to protest against the Headmaster any more,” Hannah said weakly. The Hufflepuff girl seemed a bit unsteady on her feet. “I don’t care what Professor McGonagall says about him not holding it against us, it’s just too much for my nerves.”
„Ich habe keine Lust mehr, gegen den Schulleiter zu protestieren“, sagte Hannah schwach. Das Hufflepuff-Mädchen schien ein wenig unsicher auf den Beinen zu sein. „Es ist mir egal, ob Professor McGonagall sagt, dass er es uns nicht übelnimmt, es ist einfach zu viel für meine Nerven.“

% Lavender snorted. “I guess \emph{you} won’t be slaying armies of Inferi anytime soon—”
Lavender schnaubte. „Ich schätze, \emph{du} wirst in nächster Zeit keine Armeen von Inferi erschlagen—“

% “Stop that!” Hermione said sharply. “Look, all of us have got to \emph{learn} to be heroines, right? It’s okay if someone doesn’t know how right away.”
„Hör auf damit!“ sagte Hermine scharf. „Wir müssen erst alle \emph{lernen}, Heldinnen zu sein, oder? Es ist in Ordnung, wenn es jemand nicht sofort weiß.“

% “The Headmaster doesn’t think it \emph{can} be learned,” Padma said. The Ravenclaw girl’s face was thoughtful, her steps measured as she strode through the corridor. “The Headmaster doesn’t even think that’s a good idea.”
„Der Schulleiter glaubt nicht, dass man es lernen \emph{kann}“, sagte Padma. Das Gesicht des Ravenclaw-Mädchens war nachdenklich, ihre Schritte gemessen, als sie durch den Korridor schritt. „Der Schulleiter hält das nicht einmal für eine gute Idee.“

% Daphne was striding with her back straight and her head held bolt upright, looking more like a Proper Young Lady in her Hogwarts robes than Hermione could have done with her best formal dress. “The Headmaster,” Daphne said in a precise voice, her shoes making hard, sharp tacking sounds on the stone, “thinks the lot of us are a bunch of silly girls playing games, and that some day Hermione might make a good sidekick but the rest of us are hopeless.”
Daphne schritt mit geradem Rücken und kerzengeradem Kopf und sah damit in ihren Hogwarts-Umhängen mehr wie eine noble, junge Dame aus, als Hermine es in ihrem besten Festtagskleid hätte tun können. „Der Schulleiter“, sagte Daphne mit präziser Stimme, wobei ihre Schuhe harte, kurze Klack-Geräusche auf dem Stein machten, „denkt, dass wir alle ein Haufen dummer Mädchen sind, die Spielchen spielen, und dass Hermine vielleicht eines Tages eine gute Gehilfin sein wird, aber der Rest von uns hoffnungslos ist.“

% “Is he \emph{right?}” said Parvati. The Gryffindor girl’s face was very serious, making her look much more like her twin than she usually did. “I mean it has to be asked—”
„Hat er \emph{recht}?“, sagte Parvati. Das Gesicht des Gryffindor-Mädchens war sehr ernst und ließ sie viel mehr wie ihren Zwilling aussehen, als sie es normalerweise tat. „Ich meine, man muss die Frage doch einmal in Raum werfen—“

% “\emph{No!}” spat Tracey. The Slytherin girl was stalking through the hallway looking ready to \emph{kill} someone, like a miniature female Snape. Of all the girls, Tracey was the one who Hermione knew least. Hermione had talked to Lavender once before, but she’d never really \emph{seen} Tracey except at wand-point during a battle, until the Slytherin had jumped up from her sofa to volunteer. “We’ll show him! We’ll show them \emph{all!}”
„\emph{Nein!}“, stieß Tracey hervor. Das Slytherin-Mädchen stakste durch den Flur und sah aus, als wäre sie bereit, jemanden zu töten, wie ein weiblicher Miniatur-Snape. Von allen Mädchen war Tracey diejenige, die Hermine am wenigsten kannte. Hermine hatte schon einmal mit Lavender gesprochen, aber mit Tracey hatte sie noch nie etwas zu tun gehabt, außer auf der Gegenseite bei einem Kampf, bis die Slytherin vom Sofa aufgesprungen war und sich freiwillig für \SPHEW gemeldet hatte. „Wir werden es ihm zeigen! Wir werden es ihnen \emph{allen} zeigen!“

% “Okay,” said Susan, “that was \emph{definitely} evil—”
„Okay“, sagte Susan, „das war \emph{definitiv} böse—“

% “No,” said Lavender, “that’s a Chaos Legion motto, actually. Only she didn’t do the insane laughter.”
„Nein“, sagte Lavender, „das ist nur ein Motto der Chaos-Legion. Nur hat sie das irre Lachen vergessen.“

% “That’s right,” Tracey said, her voice low and grim. “This time I’m not laughing.” The girl went on stalking through the corridor, like she had dramatic music accompanying her that only she could hear.
„Das stimmt“, sagte Tracey, ihre Stimme tief und grimmig. „Denn diesmal lache ich nicht.“ Das Mädchen pirschte weiter durch den Korridor, als würde sie von dramatischer Musik begleitet, die nur sie hören konnte.

% (Hermione was starting to worry about what \emph{exactly} the impressionable youths of the Chaos Legion were learning from Harry Potter.)
(Hermine begann sich Sorgen zu machen, was \emph{genau} die beeinflussbaren Jugendlichen der Chaos-Legion von Harry Potter lernten.)

% “But—I mean—” Parvati said. She still had a contemplative look on her face. “I mean, you can see \emph{why} the Headmaster would think we were just silly girls, right? What does protesting outside the Headmaster’s office have to do with becoming heroines?”
„Aber—ich meine—“ sagte Parvati. Sie hatte immer noch diesen nachdenklichen Gesichtsausdruck. „Ich meine, man kann doch verstehen, warum der Schulleiter uns für dumme Mädchen hält, oder? Was hat der Protest vor dem Büro des Schulleiters damit zu tun, Heldinnen zu werden?“

% “Huh,” Lavender said, now looking thoughtful herself. “That’s true. We should do something heroic. I mean heroinic.”
„Hm“, sagte Lavender, die nun selbst nachdenklich aussah. „Das ist wahr. Wir sollten etwas Heldenhaftes tun. Ich meine Heldinnenhaftes.“

% “Um—” said Hannah, which very much expressed Hermione’s own feelings on the subject.
„Ähm—“, sagte Hannah, was sehr gut Hermines eigene Gefühle zu diesem Thema ausdrückte.

% “Well,” said Parvati, “has everyone already been through Dumbledore’s third-floor forbidden corridor? I mean everyone in Gryffindor’s been through it by now—”
„Nun“, sagte Parvati, „hat denn schon jeder Dumbledores verbotenen Korridor im dritten Stock probiert? Ich meine, jeder aus Gryffindor war schonmal da—“

% “Hold \emph{on!}” Hermione said desperately. “I don’t want you doing anything \emph{dangerous!}”
„\emph{Moment} mal!“, sagte Hermine verzweifelt. „Ich will nicht, dass wir etwas \emph{Gefährliches} machen!“

% There was a pause while everyone looked at Hermione, who was realizing, much too late, why Dumbledore hadn’t wanted anyone \emph{else} to be a hero.
Es gab eine Pause, während alle Hermine ansahen, die viel zu spät begriff, warum Dumbledore nicht wollte, dass jemand \emph{anderes} ein Held wurde.

% “I don’t think you can become a heroine if you never do anything dangerous,” Lavender observed reasonably.
„Ich glaube nicht, dass man eine Heldin werden kann, wenn man nie etwas Gefährliches tut“, bemerkte Lavender vernünftig.

% “Besides,” said Padma, a considering look on her face. “Everyone knows that nothing \emph{really} bad ever happens in Hogwarts, right? To students, I mean, not to the Defence Professors. We’ve got all these ancient wards and so on.”
„Außerdem“, sagte Padma mit einem nachdenklichen Gesichtsausdruck. „Jeder weiß doch, dass in Hogwarts nie etwas \emph{wirklich} Schlimmes passiert, oder? Den Schülern, meine ich, nicht den Verteidigungsprofessoren. Wir haben all diese uralten Schutzzauber und so weiter.“

% “Um—” Hannah said again.
„Ähm—“ Sagte Hannah wieder.

% “Yeah,” said Parvati, “the worst that can happen is that we’ll lose a few dozen House points or something, and there’s two of us from each House so \emph{that’ll} all come out even.”
„Ja“, sagte Parvati, „das Schlimmste, was passieren kann, ist, dass wir ein paar Dutzend Hauspunkte verlieren oder so, und wir sind zwei aus jedem Haus, also wird \emph{das} alles ausgeglichen.“

% “Why, that’s \emph{brilliant}, Hermione!” said Daphne in a tone of great amazement. “The way you set it up means we can get away with \emph{anything!} And I didn’t even notice your cunning plan until now!”
„Das ist ja \emph{genial}, Hermine!“, sagte Daphne in einem Ton großer Bewunderung. „So wie du es eingerichtet hast, können wir \emph{mit allem} durchkommen! Und ich habe deinen schlauen Plan bis jetzt nicht einmal bemerkt!“

% “\emph{Um}—” said Hermione, Hannah, and Susan.
„\emph{Ähm}—“, sagten Hermine, Hannah und Susan.

% “Right!” said Parvati. “So now it’s time for us to become real heroines. We’ll come for the darkness—”
„Richtig!“, sagte Parvati. „Jetzt ist es also an der Zeit, dass wir zu echten Heldinnen werden. Wir werden gegen die Dunkelheit antreten—“

% “And make \emph{it} face \emph{us}—” said Lavender.
„Und bringen sie dazu, sich \emph{uns} zu stellen—“ sagte Lavender.

% “And teach it to be afraid,” Tracey Davis said grimly.
„Und lehren sie, uns zu fürchten“, sagte Tracey Davis grimmig.

%  LocalWords:  ven Preece Cazaril Cimorene Linderwall Bwa heroinic
