% Quelle der Übersetzung: Schneefl0cke https://www.fanfiktion.de/s/60044849000ccc541aef297e/81/
% \partchapter{Taboo Trade-offs}{III}
\partchapter{Tabubrüche}{III}

% \lettrinepara{I}{n} rising half-circles of dark stone, a great sea of upraised hands.

\lettrinepara{I}{n} aufsteigenden Halbkreisen aus dunklem Stein, ein großes Meer von erhobenen Händen.

\hplettrineextrapara
% The Lords and Ladies of the Wizengamot, in plum-coloured robes marked with a silver ‘W’, stared down in stern rebuke at a young girl trembling in chains. If they had, in any particular ethical system, damned themselves, they clearly thought quite highly of themselves for having done so.
Die Lords und Ladies des Zaubergamots, in pflaumenfarbenen Roben, die mit einem silbernen ‚Z‘ gekennzeichnet waren, starrten in strengem Tadel auf ein junges Mädchen herab, das in Ketten zitterte. Wenn sie sich in einem bestimmten ethischen System selbst verdammt hatten, dann hielten sie offensichtlich ziemlich viel von sich selbst, weil sie das getan hatten.

% Harry’s breath was trembling in his chest. His dark side had come up with a plan—and then rotated itself back out again because speaking too icily would not be to Hermione’s advantage; a fact which the only-half-cold Harry had somehow not realized…
Harrys Atem zitterte in seiner Brust. Seine dunkle Seite hatte sich einen Plan ausgedacht—und sich dann wieder herausgedreht, weil ein zu eisiges Sprechen nicht zu Hermines Vorteil sein würde; eine Tatsache, die der nur halbwegs kalte Harry irgendwie nicht erkannt hatte…

% “The vote carries, in favour,” intoned the secretary, when all the tallying was done, and the upraised hands fell back down. “The Wizengamot recognizes the blood debt owed by Hermione Granger to House Malfoy for the attempted murder of its scion and ending of its line.”
„Die Abstimmung ist angenommen“, stimmte der Sekretär an, als alles ausgezählt war und die erhobenen Hände wieder nach unten fielen. „Das Zaubergamot erkennt die Blutschuld an, die Hermine Granger dem Haus Malfoy für den versuchten Mord an seinem Spross und die Beendigung seiner Linie schuldet.“

% Lucius Malfoy was smiling in grim satisfaction. “And now,” said the white-maned wizard, “I say that her debt shall be paid—”
Lucius Malfoy lächelte in grimmiger Zufriedenheit.
„Und nun“, sagte der weißmähnige Zauberer, „sage ich, dass ihre Schuld beglichen werden soll—“

% Harry clenched his fists beneath the bench and shouted, “By the debt owed from House Malfoy to House Potter!”
Harry ballte die Fäuste unter der Bank und rief: „Mit der Schuld, die das Haus Malfoy dem Haus Potter schuldet!“

% “Silence!” snapped the woman in too much pink make-up sitting next to Minister Fudge. “You’ve disrupted these proceedings quite enough already! Aurors, escort him out!”
„Ruhe!“, schnauzte die Frau mit zu viel rosa Make-up, die neben Minister Fudge saß. „Du hast die Sitzung schon genug gestört! Auroren, geleiten Sie ihn hinaus!“

% “Wait,” said Augusta Longbottom from the top tier of seats. “What debt is this?”
„Warten Sie“, sagte Augusta Longbottom von der obersten Sitzreihe aus. „Was ist das für eine Schuld?“

% Lucius’s hands whitened on his cane. “House Malfoy owes no debt to you!”
Lucius' Hände wurden auf seinem Stock weiß. „Das Haus Malfoy hat keine Schulden bei dir!“

% It wasn’t the world’s most solid hope, it was based on one newspaper article from a woman who’d been False-Memory-Charmed, but Rita Skeeter had seemed to find it plausible, that Mr~Weasley had allegedly owed James Potter a debt because…
Es war nicht die solideste Hoffnung der Welt, sie basierte auf einem Zeitungsartikel einer Frau, die mit einem falschen Gedächtniszauber belegt worden war, aber Rita Skeeter schien es plausibel zu finden, dass Mr~Weasley angeblich James Potter etwas schuldete, weil…

% “I’m surprised you’ve forgotten,” Harry said evenly. “Surely it was a cruel and painful period of your life, labouring under the Imperius curse of He-Who-Must-Not-Be-Named, until you were freed of it by the efforts of House Potter. By my mother, Lily Potter, who died for it, and by my father, James Potter, who died for it, and by me, of course.”
„Es wundert mich, dass du das vergessen hast“, sagte Harry gleichmäßig. „Sicherlich war es eine grausame und schmerzhafte Zeit deines Lebens, als du unter dem Imperius-Fluch von Ihm-dessen-Name-nicht-genannt-werden-darf gelitten hast, bis du durch die Bemühungen des Hauses Potter davon befreit wurdest. Durch meine Mutter, Lily Potter, die dafür starb, und durch meinen Vater, James Potter, der dafür starb, und natürlich durch mich.“

% There was a brief silence within the Most Ancient Hall.
Es herrschte eine kurze Stille in der Ältestenhalle.

% “Why, what an excellent point, Mr~Potter,” said the old witch who’d been identified as Madam Bones. “I, too, am quite surprised that Lord Malfoy would forget such a significant event. It must have been such a happy day for him.”
„Was für ein ausgezeichnetes Argument, Mr~Potter“, sagte die alte Hexe, die als Madam Bones identifiziert worden war. „Auch ich bin ziemlich überrascht, dass Lord Malfoy ein so bedeutendes Ereignis vergessen würde. Es muss ein so glücklicher Tag für ihn gewesen sein.“

% “Yes,” said Augusta Longbottom. “He must have been so grateful.”
„Ja“, sagte Augusta Longbottom. „Er muss so dankbar gewesen sein.“

% Madam Bones nodded. “House Malfoy could not possibly deny that debt—unless, perhaps, Lord Malfoy is to tell us that he has misremembered something? I should take quite a professional interest in that. We are always trying to improve our picture of those dark days.”
Madam Bones nickte. „Das Haus Malfoy könnte diese Schuld unmöglich leugnen—es sei denn, Lord Malfoy will uns sagen, dass er sich an etwas falsch erinnert hat? Daran hätte ich ein recht professionelles Interesse. Wir sind immer bemüht, unser Bild von diesen dunklen Tagen zu verbessern.“

% Lucius Malfoy’s hands gripped the silver snake-handle of his cane like he was about to strike with it, unleash whatever power it kept—
Lucius Malfoys Hände umklammerten den silbernen Schlangengriff seines Stocks, als wolle er damit zuschlagen, die Macht entfesseln, die er in sich trug—

% Then the Lord Malfoy seemed to relax, and a chill smile came over his face. “Of course,” he said easily. “I do confess I had not understood, but the child is quite correct. But I do not quite think the two debts cancel—House Potter was only trying to save itself, after all—”
Dann schien sich Lord Malfoy zu entspannen, und ein kühles Lächeln kam über sein Gesicht. „Natürlich“, sagte er leichthin. „Ich gebe zu, ich hatte es nicht verstanden, aber das Kind hat recht. Aber ich glaube nicht, dass sich die beiden Schulden aufheben—Haus Potter hat schließlich nur versucht, sich selbst zu retten—“

% “Not so,” Dumbledore said from above.
„Nicht ganz“, sagte Dumbledore von oben.

% “—and therefore,” intoned Lucius Malfoy, “I demand monetary compensation as well, for the redemption of the blood debt owed my son. That, too, is the law.”
„- und deshalb“, stimmte Lucius Malfoy ein, „verlange ich auch eine finanzielle Entschädigung, um die Blutschuld an meinem Sohn zu tilgen. Auch das ist das Gesetz.“

% Harry felt a strange inward flinch. That had also been in the newspaper article, Mr~Weasley had demanded an additional ten thousand Galleons—
Harry spürte ein seltsames inneres Zusammenzucken. Das hatte auch in dem Zeitungsartikel gestanden, Mr~Weasley hatte zusätzlich zehntausend Galleonen gefordert—

% “How much?” said the Boy-Who-Lived.
„Wie viel?“, fragte der Junge-der-überlebte.

% Lucius was still wearing the cold smile. “One hundred thousand Galleons. If you have not that much in your vault, I suppose I must accept a promissory note for the remainder.”
Lucius trug immer noch das kalte Lächeln. „Einhunderttausend Galleonen. Wenn du nicht so viel in deinem Tresor hast, muss ich wohl einen Schuldschein für den Rest akzeptieren.“

% A roar of protest went up from Dumbledore’s side of the room, even some of the plum-coloured robes in the middle looked shocked.
Ein Aufschrei des Protestes ging von Dumbledores Seite des Raumes aus, sogar einige der pflaumenfarbenen Roben in der Mitte schauten schockiert.

% “Shall we put it to vote of the Wizengamot?” said Lucius Malfoy. “I think few of us would like to see the little murderess go free. By a show of hands, that additional compensation of one hundred thousand Galleons would be required to cancel the debt!”
„Sollen wir das Zaubergamot darüber abstimmen lassen?“, sagte Lucius Malfoy. „Ich glaube, nur wenige von uns würden es gerne sehen, wenn die kleine Mörderin frei kommt. Durch Handzeichen wäre die zusätzliche Entschädigung von hunderttausend Galleonen erforderlich, um die Schuld zu streichen!“

% The clerk began tallying, but that vote was also clear.
Der Schreiber begann zu zählen, aber auch dieses Votum war eindeutig.

% Harry stood there, breathing deeply.
Harry stand da und atmete tief durch.

% \emph{You’d better not even have to think about this,} Harry’s inner Gryffindor said threateningly.
\emph{Darüber solltest du besser gar nicht erst nachdenken,} sagte Harrys innerer Gryffindor drohend.

% \emph{It’s a major purchase,} observed Ravenclaw. \emph{We ought to spend a lot of time thinking about it.}
\emph{Es ist eine hohe Summe,} bemerkte der Ravenclaw. \emph{Wir sollten viel Zeit damit verbringen, darüber nachzudenken.}

% It shouldn’t have been hard. It \emph{shouldn’t} have. Two million pounds was only money, and money was only worth what it could buy…
\emph{Es sollte nicht schwer sein. Das hätte es nicht sollen. Zwei Millionen Pfund waren nur Geld, und Geld war nur das wert, was es kaufen konnte}…

% It was strange how much psychological attachment you could have to ‘only money’, or how painful it could be to imagine losing a bank vault full of gold that you hadn’t even imagined existed just one year earlier.
Es war seltsam, wie viel psychologische Anhaftung man an ‚nur Geld‘ haben konnte, oder wie schmerzhaft es sein konnte, sich vorzustellen, einen Banktresor voller Gold zu verlieren, von dem man sich noch ein Jahr zuvor nicht einmal vorstellen konnte, dass er existierte.

% \emph{Kimball Kinnison wouldn’t hesitate,} said Gryffindor. \emph{Seriously. Like, snap decision. What sort of hero are you? I already hate you just for having to think about it for longer than 50 milliseconds.}
\emph{Kimball Kinnison würde nicht zögern}, sagte der Gryffindor. \emph{Ernsthaft, es wäre eine Blitzentscheidung. Was für ein Held bist du? Ich hasse dich schon allein dafür, dass du länger als 50 Millisekunden darüber nachdenken musst.}

% \emph{This is real life,} said Ravenclaw. \emph{Losing all your money is a lot more painful for real people in real life than in heroic books.}
\emph{Das ist das wahre Leben,} sagte Ravenclaw. \emph{Sein ganzes Geld zu verlieren, ist für echte Menschen im wirklichen Leben viel schmerzhafter als in Heldenbüchern.}

% \emph{What?} demanded Gryffindor. \emph{Whose side are you on?}
\emph{Was?} fragte Gryffindor. \emph{Auf wessen Seite stehst du?}

% \emph{I wasn’t advocating for a particular answer,} said Ravenclaw, \emph{I was just saying it because it was true.}
\emph{Ich habe nicht für eine bestimmte Antwort plädiert,} sagte Ravenclaw, \emph{ich habe es nur gesagt, weil es wahr ist.}

% \emph{Could a hundred thousand Galleons be used to save more than one life if spent some other way?} said Slytherin. \emph{We have research to do, battles to fight, the difference between being 40,000 Galleons rich and being 60,000 Galleons in debt is not trivial—}
\emph{Könnte man mit hunderttausend Galleonen mehr als ein Leben retten, wenn man sie auf andere Weise ausgeben würde?} sagte Slytherin. \emph{Wir haben zu forschen, Schlachten zu schlagen, der Unterschied zwischen 40.000 Galleonen reich und 60.000 Galleonen verschuldet zu sein ist nicht trivial—}

% \emph{So we’ll just use one of our ways to make money fast and earn it all back,} said Hufflepuff.
\emph{also werden wir einfach eine unserer Möglichkeiten nutzen, um schnell Geld zu verdienen und alles zurückzubekommen,} sagte Hufflepuff.

% \emph{It’s not certain those will work,} said Slytherin, \emph{and a lot of them require starting cash—}
\emph{Es ist nicht sicher, dass diese funktionieren}, sagte Slytherin, \emph{und viele von ihnen erfordern Startkapital—}

% \emph{Personally,} said Gryffindor, \emph{I vote that we save Hermione and then gang up and kill our inner Slytherin.}
\emph{Ich persönlich,} sagte Gryffindor, \emph{bin dafür, dass wir Hermine retten und uns dann zusammentun und unseren inneren Slytherin töten}.

% The clerk’s voice said that the tally had been recorded and the vote had passed…
Die Stimme des Schreibers sagte, dass die Stimmenauszählung aufgezeichnet worden war und die Abstimmung angenommen wurde…

% Harry’s lips opened.
Harrys Lippen öffneten sich.

% “I accept your offer,” said Harry’s lips, without any hesitation, without any decision having been made; just as if the internal debate had been pretence and illusion, the true controller of the voice having been no part of it.
„Ich nehme das Angebot an“, sagten Harrys Lippen, ohne jegliches Zögern, ohne dass eine Entscheidung getroffen worden wäre; gerade so, als wäre die innere Debatte nur Schein und Illusion gewesen, ohne dass der wahre Kontrolleur der Stimme daran beteiligt gewesen wäre.

% Lucius Malfoy’s mask of calm shattered, his eyes widened, he stared at Harry in sheer blank astonishment. His mouth had opened slightly, though he wasn’t speaking, and if he was making any peculiar noises it couldn’t be heard over the roar of simultaneous gasps from the Wizengamot—
Lucius Malfoys Maske der Ruhe zerbrach, seine Augen weiteten sich, er starrte Harry in blankem Erstaunen an. Sein Mund hatte sich leicht geöffnet, obwohl er nicht sprach, und wenn er irgendwelche merkwürdigen Geräusche machte, war das nicht zu hören über dem Gebrüll des gleichzeitigen Keuchens des Zaubergamot—

% A tap of stone silenced the crowd.
Ein Klopfen auf Stein brachte die Menge zum Schweigen.

% “No,” said the voice of Dumbledore.
„Nein“, sagte die Stimme von Dumbledore.

% Harry’s head jerked around to stare at the ancient wizard.
Harrys Kopf ruckte herum und starrte den alten Zauberer an.

% Dumbledore’s lined face was pale, the silver beard was visibly trembling, he looked like he was in the final throes of a terminal illness. “I’m—sorry, Harry—but this choice is not yours—for I am still the guardian of your vault.”
Dumbledores liniertes Gesicht war blass, der silberne Bart zitterte sichtlich, er sah aus, als befände er sich in den letzten Zügen einer unheilbaren Krankheit.
„Es—tut mir leid, Harry—aber diese Entscheidung liegt nicht bei dir—denn ich bin immer noch der Bevollmächtigte deines Vermögens.“

% “\emph{What?}” said Harry, too shocked to compose his reply.
\emph{„Was?}“, sagte Harry, zu schockiert, um seine Antwort zu formulieren.

% “I cannot let you go into debt to Lucius Malfoy, Harry! I cannot! You do not know—you do not realize—”
„Ich kann nicht zulassen, dass du dich bei Lucius Malfoy verschuldest, Harry! Das kann ich nicht! Du weißt nicht—du begreifst nicht—“

\emph{Stirb.}

% Harry didn’t even know which part of himself had spoken, it might have been a unanimous vote, the pure rage and fury pouring through him. For an instant he thought that the sheer force of the anger might take magical wing and fly out to strike the Headmaster, send him tumbling back dead from the podium—
Harry wusste nicht einmal, welcher Teil von ihm gesprochen hatte, es hätte eine einstimmige Abstimmung sein können, die pure Wut und der Zorn strömten durch ihn. Einen Augenblick lang dachte er, dass die schiere Kraft der Wut magische Flügel annehmen und hinausfliegen könnte, um den Schulleiter zu treffen, ihn tot vom Podium zurückstürzen zu lassen—

% But when that mental voice had spoken, the old wizard was still standing there, gazing at Harry, long dark wand in his right hand, short black rod in his left.
Aber als diese mentale Stimme gesprochen hatte, stand der alte Zauberer immer noch da und starrte Harry an, den langen dunklen Zauberstab in der rechten Hand, den kurzen schwarzen Stab in der linken.

% And Harry’s eyes also went to the red-golden bird with its claws resting on the shoulder of Dumbledore’s black robes, silent when no phœnix should have been silent. “Fawkes,” Harry said, his voice sounding strange in his own ears, “can you scream at him for me?”
Und Harrys Augen gingen auch zu dem rotgoldenen Vogel, der mit seinen Krallen auf der Schulter von Dumbledores schwarzer Robe ruhte und schwieg, als kein Phönix hätte schweigen dürfen.
„Fawkes“, sagte Harry, wobei seine Stimme in seinen eigenen Ohren seltsam klang, „kannst du ihn für mich anschreien?“

% The fiery bird on the old wizard’s shoulder didn’t scream. Maybe the Wizengamot had demanded that a spell of silence be put on the creature, otherwise it probably would have been screaming the whole time. But Fawkes hit his master, one golden wing buffeting the old wizard’s head.
Der feurige Vogel auf der Schulter des alten Zauberers schrie nicht. Vielleicht hatte das Zaubergamot verlangt, dass ein Schweigezauber auf die Kreatur gelegt wurde, sonst hätte sie wahrscheinlich die ganze Zeit geschrien. Aber Fawkes schlug auf seinen Herrn ein, wobei ein goldener Flügel den Kopf des alten Zauberers umwarf.

% “I cannot, Harry!” the old wizard said, the agony clear in his voice. “I am doing as I must do!”
„Ich kann nicht, Harry!“, sagte der alte Zauberer, die Qual deutlich in seiner Stimme. „Ich tue nur, was ich tun muss!“

% And Harry knew, then, as he looked at the red-golden bird, what he had to do as well. It should have been obvious from the beginning, that solution.
Und Harry wusste, als er den rotgoldenen Vogel ansah, was auch er tun musste. Es hätte von Anfang an klar sein müssen, diese Lösung.

% “Then I too will do what I must,” Harry said up to Dumbledore, as though the two of them stood alone in the room. “You do realize that, don’t you?”
„Dann werde auch ich tun, was ich tun muss“, sagte Harry zu Dumbledore hinauf, als stünden sie beide allein im Raum. „Das ist Ihnen doch klar, oder?“

% The old wizard shook his trembling head. “You will change your mind when you are older—”
Der alte Zauberer schüttelte den zitternden Kopf. „Du wirst deine Meinung ändern, wenn du älter bist—“

% “I’m not talking about that,” Harry said, his voice still strange in his own ears. “I mean that I will not allow Hermione Granger to be eaten by Dementors under any circumstances. Period. Regardless of what any law says, and no matter what I have to do to stop it. Do I still need to spell it out?”
„Davon spreche ich nicht“, sagte Harry, seine Stimme noch immer fremd in seinen eigenen Ohren. „Ich meine, dass ich unter keinen Umständen zulassen werde, dass Hermine Granger von Dementoren gefressen wird. Punkt. Ungeachtet dessen, was irgendein Gesetz sagt, und ungeachtet dessen, was ich tun muss, um es zu verhindern. Muss ich es noch buchstabieren?“

% A strange male voice spoke from somewhere far away, “Be sure that the girl is taken directly to Azkaban, and put under extra guard.”
Eine fremde männliche Stimme sprach von irgendwo in der Ferne: „Sorgen Sie dafür, dass das Mädchen direkt nach Askaban gebracht und unter besondere Bewachung gestellt wird.“

% Harry waited, staring at the old wizard, and then spoke again. “I will go to Azkaban,” Harry said to the old wizard, as though they stood alone in the world, “before Hermione can be taken there, and start snapping my fingers. It may cost me my life, but by the time she gets there, there won’t be an Azkaban any more.”
Harry wartete, starrte den alten Zauberer an und sprach dann wieder.
„Ich werde nach Askaban gehen“, sagte Harry zu dem alten Zauberer, als stünden sie allein auf der Welt, „bevor Hermine dorthin gebracht werden kann, und ich werde mit den Fingern schnippen. Es mag mich mein Leben kosten, aber wenn sie dort ankommt, wird es kein Askaban mehr geben.“

% Some members of the Wizengamot gasped in surprise.
Einige Mitglieder des Zaubergamots schnappten überrascht nach Luft.

% Then a greater number started laughing.
Dann begann eine größere Anzahl zu lachen.

% “How would you even get there, little boy?” someone said, from among those who were laughing.
„Wie willst du überhaupt dorthin kommen, Kleiner?“, sagte jemand aus den Reihen der Lachenden.

% “I have my ways of getting to places,” said the boy’s distant voice. Harry kept his eyes on Dumbledore, on the old wizard staring at him in shock. Harry didn’t look directly at Fawkes, didn’t give his plan away; but in his mind he prepared to summon the phœnix to transport him, prepared to fill his mind with light and fury, to call for the fire-bird with all his might, he might have to do it upon the instant if Dumbledore pointed his wand—
„Ich habe meine Wege, um dorthin zu gelangen“, sagte die ferne Stimme des Jungen. Harry hielt seine Augen auf Dumbledore gerichtet, auf den alten Zauberer, der ihn schockiert anstarrte. Harry sah Fawkes nicht direkt an, verriet seinen Plan nicht; aber in seinem Geist bereitete er sich darauf vor, den Phönix zu beschwören, um ihn zu transportieren, bereit, seinen Geist mit Licht und Wut zu füllen, den Feuervogel mit all seiner Kraft zu rufen, er würde es vielleicht auf der Stelle tun müssen, wenn Dumbledore auf seinen Zauberstab zeigte—

% “Would you truly?” the old wizard said to Harry, also as if the two of them stood alone in the room.
„Würdest du wirklich?“, sagte der alte Zauberer zu Harry, auch so, als stünden die beiden allein im Raum.

% The room went silent again as everyone stared in shock at the Chief Warlock of the Wizengamot, who seemed to be taking the mad threat completely seriously.
Der Raum verstummte wieder, während alle schockiert auf den Großmeister des Zaubergamots starrten, der die irrsinnige Drohung völlig ernst zu nehmen schien.

% The old wizard’s eyes were locked only on Harry. “Would you risk everything—everything—only for her?”
Die Augen des alten Zauberers waren nur auf Harry fixiert.
„Würdest du alles—alles—nur für sie riskieren?“

% “Yes,” Harry said back in reply.
„Ja“, erwiderte Harry.

% \emph{That’s the wrong answer, you know,} said Slytherin. \emph{Seriously}.
\emph{Das ist die falsche Antwort, weißt du}, sagte Slytherin. \emph{Ganz im Ernst}.

% \emph{But it’s the true answer.}
\emph{Aber es ist die wahre Antwort.}

% “You will not see reason?” said the old wizard.
„Du willst nicht zur Vernunft kommen?“, fragte der alte Zauberer.

% “Apparently not,” Harry said back.
„Offenbar nicht“, sagte Harry zurück.

% The gazes stayed locked.
Sie blickten sich weiter an.

% “This is terrible folly,” said the old wizard.
„Das ist eine schreckliche Torheit“, sagte der alte Zauberer.

% “I am aware of this,” answered the hero. “Now get out of my way.”
„Dessen bin ich mir bewusst“, antwortete der Held. „Und jetzt geh mir aus dem Weg.“

% Strange light glinted in the ancient blue eyes. “As you will, Harry Potter, but know that this is not over.”
Ein seltsames Licht funkelte in den alten blauen Augen.
„Wie du willst, Harry Potter, aber wisse, dass dies noch nicht vorbei ist.“

% The rest of the world faded back into existence.
Der Rest der Welt verschwand wieder in der Existenz.

% “I withdraw my objection,” said the old wizard, “Harry Potter may do as he wishes,” and the Wizengamot exploded in a roar of shock, only to be silenced by a final tap of the stone rod.
„Ich ziehe meinen Einspruch zurück“, sagte der alte Zauberer, „Harry Potter mag tun, was er will“, und das Zaubergamot explodierte in einem Brüllen des Entsetzens, nur um durch ein letztes Klopfen des Steinstabs zum Schweigen gebracht zu werden.

% Harry turned his head back to look at Lord Malfoy, who looked like he’d seen a cat turn into a person and start eating other cats. To call the look confused did not begin to describe it.
Harry drehte seinen Kopf zurück und sah Lord Malfoy an, der aussah, als hätte er gesehen, wie sich eine Katze in einen Menschen verwandelte und anfing, andere Katzen zu fressen. Den Blick verwirrt zu nennen, beschrieb es nicht ansatzweise.

% “You would truly…” Lucius Malfoy said slowly. “You would truly pay a hundred thousand Galleons, to save one mudblood girl.”
„Du würdest wirklich…“ Lucius Malfoy sagte langsam. „Du würdest wirklich hunderttausend Galleonen bezahlen, um ein Schlammblutmädchen zu retten.“

% “I think there’s about forty thousand in my Gringotts vault,” Harry said. It was strange how that was \emph{still} causing more internal pain than the thought of taking an over-fifty-percent risk to his life to destroy Azkaban. “As for the other sixty thousand—what are the rules, exactly?”
„Ich glaube, in meinem Gringotts-Tresor befinden sich etwa vierzigtausend“, sagte Harry. Es war seltsam, dass das \emph{immer noch} mehr innere Schmerzen verursachte als der Gedanke, ein über fünfzigprozentiges Risiko für sein Leben einzugehen, um Askaban zu zerstören. „Was die anderen sechzigtausend angeht—wie lauten die Regeln genau?“

% “It comes due when you graduate Hogwarts,” the old wizard said from high above. “But Lord Malfoy has certain rights over you before then, I fear.”
„Die werden fällig, wenn du deinen Abschluss in Hogwarts machst“, sagte der alte Zauberer von oben herab. „Aber ich fürchte, Lord Malfoy hat schon vorher gewisse Rechte über dich.“

% Lucius Malfoy stood motionless, frowning down at Harry. “Who is she to you, then? \emph{What} is she to you, that you would pay so much to keep her from harm?”
Lucius Malfoy stand regungslos da und blickte stirnrunzelnd auf Harry herab.
„Wer ist sie für dich? Was ist sie für dich, dass du so viel bezahlen würdest, um sie vor Schaden zu bewahren?“

% “My friend,” the boy said quietly.
„Meine Freundin“, sagte der Junge leise.

% Lucius Malfoy’s eyes narrowed. “By the report I received, you cannot cast the Patronus Charm, and Dumbledore knows this. The power of a single Dementor nearly killed you. You would not dare venture near Azkaban in your own person—”
Lucius Malfoys Augen verengten sich.
„Nach dem Bericht, den ich erhalten habe, kannst du den Patronus-Zauber nicht wirken, und Dumbledore weiß das. Die Kraft eines einzigen Dementors hätte dich fast getötet. Du würdest dich nicht einmal in die Nähe von Askaban wagen—“

% “That was in January,” said Harry. “This is April.”
„Das war im Januar“, sagte Harry. „Jetzt haben wir April.“

% Lucius Malfoy’s eyes remained cool and calculating. “You pretend you can destroy Azkaban, and Dumbledore pretends to believe it.”
Die Augen von Lucius Malfoy blieben kühl und berechnend.
„Du tust so, als könntest du Askaban zerstören, und Dumbledore tut so, als würde er es glauben.“

% Harry did not reply.
Harry antwortete nicht.

% The white-haired man turned slightly, toward the centre of the half-circle, as though to address the greater Wizengamot. “I withdraw my offer!” shouted the Lord of Malfoy. “I will not accept the debt to House Potter in payment, not even for a hundred thousand Galleons! The girl’s blood debt to House Malfoy stands!”
Der weißhaarige Mann drehte sich leicht in Richtung der Mitte des Halbkreises, als wolle er sich an das gesamte Zaubergamot wenden.
„Ich ziehe mein Angebot zurück!“, rief der Lord von Malfoy. „Ich werde die Schuld gegenüber dem Haus Potter nicht in Zahlung nehmen, nicht einmal für hunderttausend Galleonen! Die Blutschuld des Mädchens gegenüber dem Haus Malfoy bleibt bestehen!“

% Again the roar of many voices. “Dishonourable!” someone cried. “You acknowledge the debt to House Potter, and yet you would—” and then that voice cut off.
Wieder das Gebrüll vieler Stimmen.
„Unehrenhaft!“, rief jemand.
„Du erkennst die Schuld gegenüber dem Haus Potter an und dennoch würdest du—“ und dann brach die Stimme ab.

% “I acknowledge the debt, but the law does not strictly oblige me to accept it in cancellation,” said Lord Malfoy with a grim smile. “The girl is no part of House Potter; the debt I owe House Potter is no debt to her. As for the \emph{dishonour}—” Lucius Malfoy paused. “As for the grave shame I feel at my ingratitude toward the Potters, who have done so much for me—” Lucius Malfoy bowed his head. “May my ancestors forgive me.”
„Ich erkenne die Schuld an, aber das Gesetz verpflichtet mich nicht strikt dazu, sie zu erlassen“, sagte Lord Malfoy mit einem grimmigen Lächeln. „Das Mädchen ist kein Teil des Hauses Potter; die Schuld, die ich dem Haus Potter schulde, ist keine Schuld ihr gegenüber. Was die Entehrung angeht—“ Lucius Malfoy hielt inne. „Was die große Scham betrifft, die ich wegen meiner Undankbarkeit gegenüber den Potters empfinde, die so viel für mich getan haben—“
Lucius Malfoy senkte den Kopf.
„Mögen meine Vorfahren mir vergeben.“

% “Well, boy?” called the scarred man sitting at Lord Malfoy’s right hand. “Go and destroy Azkaban, then!”
„Nun, Junge?“, rief der vernarbte Mann, der zur rechten Hand von Lord Malfoy saß. „Dann geh und zerstöre Askaban!“

% “I’d like to see that,” said another voice. “Will you be selling tickets?”
„Das würde ich gerne sehen“, sagte eine andere Stimme. „Verkaufst du Eintrittskarten?“

% It went without saying that Harry didn’t pick this particular moment to give up.
Es verstand sich von selbst, dass Harry nicht gerade diesen Moment wählte, um aufzugeben.

% \emph{The girl is no part of House Potter—}
\emph{Das Mädchen gehört nicht zum Haus Potter—}

% He had, in fact, seen the obvious way out of the dilemma almost instantly.
Eigentlich hatte er den offensichtlichen Ausweg aus dem Dilemma fast sofort gesehen.

% It might have taken him longer if he hadn’t recently overheard a number of conversations between older Ravenclaw girls, and read a certain number of Quibbler stories.
Er hätte vielleicht länger gebraucht, wenn er nicht in letzter Zeit eine Reihe von Gesprächen zwischen älteren Ravenclaw-Mädchen belauscht und eine gewisse Anzahl von \emph{Klitterer}-Geschichten gelesen hätte.

% He was, nonetheless, having trouble accepting it.
Nichtsdestotrotz hatte er Schwierigkeiten, es zu akzeptieren.

% \emph{This is ridiculous,} said a part of Harry which had just dubbed itself the Internal Consistency Checker. \emph{Our actions here are completely incoherent. First you feel less emotional reluctance to risk your bloody \emph{life} and probably \emph{die} for Hermione, than to part with a stupid heap of gold. And now you’re baulking just at getting married?}
\emph{Das ist lächerlich,} sagte ein Teil von Harry, der sich gerade als interner Konsistenzprüfer betitelt hatte. \emph{Unsere Handlungen hier sind völlig inkohärent. Erst empfindest du weniger emotionale Abneigung, dein verdammtes \emph{Leben} zu riskieren und wahrscheinlich für Hermine zu \emph{sterben}, als dich von einem dummen Haufen Gold zu trennen. Und jetzt sträubst du dich, nur wegen einer Heirat?}

% \emph{SYSTEM ERROR.}
\emph{SYSTEMFEHLER}.

% \emph{You know what?} said Internal Consistency Checker. \emph{You’re stupid.}
\emph{Weißt du was?} Sagte der interne Konsistenzprüfer. \emph{Du bist dumm.}

% \emph{I didn’t say no,} thought Harry. \emph{I was just saying SYSTEM ERROR.}
\emph{Ich habe nicht nein gesagt, dachte Harry. Ich habe nur \emph{SYSTEMFEHLER} gesagt}.

% \emph{I vote for destroying Azkaban,} said Gryffindor. \emph{It needs to be done anyway.}
\emph{Ich bin dafür, Askaban zu zerstören,} sagte Gryffindor. \emph{Es muss sowieso gemacht werden.}

% \emph{Really, really stupid,} said Internal Consistency Checker. \emph{Oh, screw this, I’m assuming control of our body.}
\emph{Wirklich, wirklich dumm}, sagte der interne Konsistenzprüfer. \emph{Oh, scheiß drauf, ich übernehme die Kontrolle über unseren Körper.}

% The boy took a deep breath, and opened his mouth—
Der Junge holte tief Luft und öffnete den Mund—

% By this point Harry Potter had entirely forgotten the existence of Professor McGonagall, who had been sitting there this whole time undergoing a number of interesting changes of facial expression which Harry had not been looking at because he was distracted. It would have been overly harsh to say that Harry had forgotten her because he did not consider her a PC. It could be more kindly said that Professor McGonagall was not visibly a solution to any of his current problems, and therefore she was not part of the universe.
Zu diesem Zeitpunkt hatte Harry Potter die Existenz von Professor McGonagall schon völlig vergessen, die die ganze Zeit dort gesessen und eine Reihe interessanter Veränderungen des Gesichtsausdrucks durchgemacht hatte, die Harry nicht beachtet hatte, weil er abgelenkt war. Es wäre zu hart gewesen, zu sagen, dass Harry sie vergessen hatte, weil er sie nicht als Wichtig betrachtete. Man könnte freundlicher sagen, dass Professor McGonagall keine sichtbare Lösung für eines seiner aktuellen Probleme war, und deshalb war sie nicht Teil des Universums.

% So Harry, who at this point had a fair amount of adrenaline in his bloodstream, started and jumped quite visibly when Professor McGonagall, her eyes now blazing with impossible hope and the tears on her cheek half-dried, leapt to her feet and cried, “\emph{With me, Mr~Potter!}” and, without waiting for a reply, tore down the stairs that led to the bottom platform where waited a chair of dark metal.
Harry, der zu diesem Zeitpunkt eine ordentliche Portion Adrenalin im Blut hatte, schreckte auf und zuckte sichtlich zusammen, als Professor McGonagall, deren Augen nun vor unmöglicher Hoffnung glühten und deren Tränen auf den Wangen schon halb getrocknet waren, aufsprang und rief: „Mit mir, Mr~Potter!“ und, ohne eine Antwort abzuwarten, die Treppe hinunterrannte, die zur unteren Plattform führte, wo ein Stuhl aus dunklem Metall wartete.

% It took a moment, but Harry ran after; though it took him longer to reach the bottom, after Professor McGonagall vaulted half the stairs with a strange catlike motion and landed with the astonished-looking Auror trio already pointing their wands at her.
Es dauerte einen Moment, aber Harry rannte hinterher; allerdings dauerte es länger, bis er unten ankam, nachdem Professor McGonagall mit einer seltsamen katzenartigen Bewegung die halbe Treppe übersprungen hatte und bei dem erstaunt dreinblickenden Aurorentrio landete, das bereits seine Zauberstäbe auf sie richtete.

% “Miss~Granger!” cried Professor McGonagall. “Can you speak yet?”
„Miss~Granger!“, rief Professor McGonagall. „Können Sie schon sprechen?“

% Much as with Professor McGonagall, there was a certain sense in which it could be said that Harry had forgotten about the existence of Hermione Granger, because Harry had been tilting his neck back to look upward rather than downward, and because he hadn’t considered her a solution to any of his current problems. Though it was hardly certain, in fact it wasn’t at all probable, that Harry remembering to look at Hermione or think about what she must be feeling, would have helped anything in the slightest.
Ähnlich wie bei Professor McGonagall konnte man in gewissem Sinne sagen, dass Harry die Existenz von Hermine Granger vergessen hatte, weil er seinen Nacken nach hinten geneigt hatte, um nach oben statt nach unten zu schauen, und weil er sie nicht als Lösung für irgendeines seiner aktuellen Probleme betrachtet hatte. Obwohl es kaum sicher war, ja, es war sogar unwahrscheinlich, dass es Harry auch nur im Geringsten geholfen hätte, wenn er daran gedacht hätte, Hermine anzuschauen oder darüber nachzudenken, was sie fühlen musste.

% Harry reached the bottom of the stairs and saw Hermione Granger full on—
Harry erreichte den Fuß der Treppe und sah Hermine Granger in voller Pracht—

% Without thinking, without being able to help himself, Harry shut his eyes, but he’d seen.
ohne nachzudenken, ohne sich helfen zu können, schloss Harry die Augen, aber er hatte alles gesehen.

% Her school robes around her neck, soaked all the way through with tears.

% The way she’d been looking away from \emph{him}.

% And the eye of memory and sympathy, which could not be shut, which could not look away, knew that Hermione had recounted the worst shame of her life in front of the nobility of magical Britain and Professor McGonagall and Dumbledore and Harry; and then been sentenced to Azkaban where she would be exposed to darkness and cold and all her worst memories until she went mad and died; and then she’d heard that Harry was going to give away all his money and go into debt to save her, and maybe even sacrifice his life; and with the Dementor standing only a few paces behind her, she hadn’t said anything…
Ihren Schulmantel um den Hals, ganz durchnässt von Tränen. Die Art, wie sie von \emph{ihm} weggesehen hatte. Und das Auge der Erinnerung und des Mitgefühls, das sich nicht schließen ließ, das nicht wegschauen konnte, wusste, dass Hermine vor dem Adel des magischen Britanniens und Professor McGonagall und Dumbledore und Harry die schlimmste Schande ihres Lebens erzählt hatte; und dann nach Askaban verurteilt worden war, wo sie der Dunkelheit und der Kälte und all ihren schlimmsten Erinnerungen ausgesetzt sein würde, bis sie verrückt wurde und starb; und dann hatte sie gehört, dass Harry sein ganzes Geld verschenken und sich verschulden würde, um sie zu retten, und vielleicht sogar sein Leben opfern würde, und da der Dementor nur ein paar Schritte hinter ihr stand, hatte sie nichts gesagt…

% “Y-yes,” whispered the voice of Hermione Granger. “I c-can talk.”
„J-ja“, flüsterte die Stimme von Hermine Granger. „Ich k-kann reden.“

% Harry opened his eyes again and saw her face, now looking at him. It didn’t say anything like what he thought Hermione was feeling, faces couldn’t say anything that complicated, all facial muscles could do was contort themselves into knots.
Harry öffnete die Augen wieder und sah ihr Gesicht, das ihn nun anschaute. Es sagte nichts von dem, was er dachte, was Hermine fühlte, Gesichter konnten nichts so Kompliziertes sagen, alles, was die Gesichtsmuskeln tun konnten, war, sich zu Knoten zu verziehen.

% “H-H-Harry, I-I’m so, I’m so—”
„H-H-Harry, mir geht’s gut, lass mich—“

% “Shut up,” Harry suggested.
„Halt die Klappe“, schlug Harry vor.

% “s-s-sorry—”
„tut m-m-mir L-leid—“

% “If you’d never met me on the train you wouldn’t be in any trouble right now. So shut up,” said Harry Potter.
„Wenn du mich nie im Zug getroffen hättest, wärst du jetzt nicht in Schwierigkeiten. Also halt die Klappe“, sagte Harry Potter.

% “Both of you stop being silly,” Professor McGonagall said in her firm Scottish accent (it was strange how much that helped). “Mr~Potter, hold out your wand so that Miss~Granger’s fingers can touch it. Miss~Granger, repeat after me. Upon my life and magic—”
„Hört beide auf, so albern zu sein“, sagte Professor McGonagall in ihrem festen schottischen Akzent (es war seltsam, wie sehr das half). „Mr~Potter, halten Sie Ihren Zauberstab so, dass die Finger von Miss~Granger ihn berühren können. Miss~Granger, sprechen Sie mir nach. Bei meinem Leben und meiner Magie—“

% Harry did as he was bid, thrusting his wand forward to touch Hermione’s fingers; and then Hermione’s faltering voice said, “Upon my life and magic—”
Harry tat, wie ihm geheißen, und stieß seinen Zauberstab vor, um Hermines Finger zu berühren; und dann sagte Hermines stockende Stimme:
„Bei meinem Leben und meiner Magie—“

% “I swear service to the House of Potter—” said Professor McGonagall.
„Ich schwöre, dem Haus Potter zu dienen—“, sagte Professor McGonagall.

% And Hermione, without waiting for any further instructions, said, the words spilling out of her in a rush, “I swear service to the House of Potter, to obey its Master or Mistress, and stand at their right hand, and fight at their command, and follow where they go, until the day I die.”
Und Hermine sagte, ohne auf weitere Anweisungen zu warten, und die Worte sprudelten nur so aus ihr heraus:
„Ich schwöre, dem Haus Potter zu dienen, seinem Meister oder seiner Meisterin zu gehorchen, zu ihrer Rechten zu stehen, auf ihren Befehl hin zu kämpfen und ihnen zu folgen, wohin sie gehen, bis zum Tag meines Todes.“

% All those words had been blurted out in a desperate gasp before Harry could have thought or said anything, if he’d been mad enough to interrupt.
All diese Worte waren in einem verzweifelten Keuchen herausgeplatzt, bevor Harry etwas hätte denken oder sagen können, wenn er verrückt genug gewesen wäre, sie zu unterbrechen.

% “Mr~Potter, repeat these words,” said Professor McGonagall. “I, Harry, heir and last scion of the Potters, accept your service, until the end of the world and its magic.”
„Mr~Potter, wiederholen Sie diese Worte“, sagte Professor McGonagall. „Ich, Harry, Erbe und letzter Spross der Potters, nehme deinen Dienst an, bis zum Ende der Welt und ihrer Magie.“

% Harry took a breath and said, “I, Harry, heir and last scion of the Potters, accept your service, until the end of the world and its magic.”
Harry holte tief Luft und sagte: „Ich, Harry, Erbe und letzter Spross der Potters, nehme Ihre Dienste an, bis zum Ende der Welt und ihrer Magie.“

% “That’s it,” said Professor McGonagall. “Well done.”
„Das war’s“, sagte Professor McGonagall. „Gut gemacht.“

% Harry looked up, and saw that the entire Wizengamot, whose existence he’d forgotten, was staring at them.
Harry blickte auf und sah, dass das gesamte Zaubergamot, dessen Existenz er vergessen hatte, auf sie starrte.

% And then Minerva McGonagall, who \emph{was} Head of House Gryffindor even if she didn’t always act like it, looked up high above at where Lucius Malfoy stood; and she said to him before the entire Wizengamot, “I regret every point I ever gave you in Transfiguration, you vile little worm.”
Und dann schaute Minerva McGonagall, die Leiterin des Hauses Gryffindor, auch wenn sie sich nicht immer so verhielt, hoch oben auf die Stelle, an der Lucius Malfoy stand; und sie sagte vor dem gesamten Zaubergamot zu ihm: „Ich bereue jeden Punkt, den ich dir jemals in Verwandlung gegeben habe, du widerlicher kleiner Wurm.“

% Whatever Lucius was about to say in reply was silenced by a tap of the short rod in Dumbledore’s hand. “Ahem!” said the old wizard from his podium of dark stone. “This session has carried on quite considerably, and if it is not dismissed soon, some of us may miss their entire luncheon. The law of this matter is clear. You have already voted on the terms of the bargain, and Lord Malfoy cannot legally decline it. As we have far exceeded our allotted time, I now, in accordance with the last decision of the survivors of the eighty-eighth Wizengamot, adjourn this session.”
Was auch immer Lucius darauf erwidern wollte, wurde durch einen Schlag mit dem kurzen Stab in Dumbledores Hand zum Schweigen gebracht. „Ähem!“, sagte der alte Zauberer von seinem Podium aus dunklem Stein. „Diese Sitzung hat sich ziemlich in die Länge gezogen, und wenn sie nicht bald beendet wird, könnten einige von uns ihr gesamtes Mittagessen verpassen. Das Gesetz in dieser Angelegenheit ist klar. Es wurde bereits über die Bedingungen des Abkommens abgestimmt, und Lord Malfoy kann es rechtlich nicht ablehnen. Da wir die uns zugewiesene Zeit weit überschritten haben, vertage ich nun, in Übereinstimmung mit dem letzten Beschluss der Überlebenden des achtundachtzigsten Zaubergamots, diese Sitzung.“

% The old wizard tapped the rod of dark stone three times.
Der alte Zauberer klopfte dreimal auf den Stab aus dunklem Stein.

% “You fools!” shouted Lucius Malfoy. The white hair was shaking as though in a wind, the face beneath was pale with fury. “Do you think you’ll get away with what you’ve done today? Do you think that girl can try to murder my son and escape unscathed?”
„Ihr Narren!“, rief Lucius Malfoy.
Das weiße Haar schüttelte sich wie im Wind, das Gesicht darunter war blass vor Wut. „Glaubt ihr, dass ihr mit dem, was ihr heute getan habt, davonkommt? Glaubst du, dieses Mädchen kann versuchen, meinen Sohn zu ermorden und ungeschoren davonkommen?“

% The toad-like pink–make-up woman, whose name Harry could no longer remember, was standing up from her seat. “Why, of course not,” she said with a sickening smile. “After all, the girl \emph{is} still a murderess, and I think the Ministry shall be watching her affairs quite closely—it hardly seems wise that she should be allowed to wander the streets, after all—”
Die krötenartige, rosa geschminkte Frau, an deren Namen sich Harry nicht mehr erinnern konnte, erhob sich von ihrem Platz.
„Natürlich nicht“, sagte sie mit einem hämischen Lächeln. „Immerhin ist das Mädchen immer noch eine Mörderin, und ich denke, das Ministerium wird ihre Angelegenheiten sehr genau beobachten—es erscheint kaum klug, sie auf den Straßen herumlaufen zu lassen…“

% Harry was fed up at this point.
Harry war an diesem Punkt genervt.

% Without waiting to listen, Harry turned on his heel and strode forward in long steps toward—
Ohne zu warten, um zuzuhören, drehte sich Harry auf dem Absatz um und schritt in langen Schritten vorwärts in Richtung—

% The horror only he could truly see, the absence of colour and space, the wound in the world, above which floated a tattered cloak; most imperfectly guarded by a running moonlit squirrel and fluttering silver sparrow.
Das Grauen, das nur er wirklich sehen konnte, die Abwesenheit von Farbe und Raum, die Wunde in der Welt, über der ein zerfledderter Umhang schwebte; höchst unvollkommen bewacht von einem rennenden, mondbeschienenen Eichhörnchen und einem flatternden Silberspatz.

% His dark side had also noticed, when it was looking through the entire room for anything that could possibly be used as a weapon, that the enemy had been foolish enough to bring a Dementor into Harry’s presence. That was a powerful weapon indeed, and one that Harry might wield better than its supposed masters. There had been a time in Azkaban when Harry had told twelve Dementors to turn and go, and they had gone.
Seine dunkle Seite hatte auch bemerkt, als sie den ganzen Raum nach allem durchsuchte, was möglicherweise als Waffe verwendet werden konnte, dass der Feind dumm genug gewesen war, einen Dementor in Harrys Gegenwart zu bringen. Das war in der Tat eine mächtige Waffe, und eine, die Harry vielleicht besser beherrschte als seine angeblichen Meister. Es gab eine Zeit in Askaban, da hatte Harry zwölf Dementoren befohlen, sich umzudrehen und zu gehen, und sie waren gegangen.

% \emph{The Dementors are Death, and the Patronus Charm works by thinking about happy thoughts instead of Death.}
\emph{Die Dementoren sind der Tod, und der Patronus-Zauber funktioniert, indem man an glückliche Gedanken denkt, statt an den Tod.}

% If Harry’s theory was correct, that one sentence would be all it took to pop the Aurors’ Patronus Charms like a soap bubble, and ensure that nobody within reach of his voice could cast another one.
Wenn Harrys Theorie richtig war, würde dieser eine Satz genügen, um die Patronus-Zauber der Auroren wie eine Seifenblase zerplatzen zu lassen und dafür zu sorgen, dass niemand in Reichweite seiner Stimme einen weiteren wirken konnte.

% \emph{I am going to cancel the Patronus Charms and prevent any more Patronuses from being cast. And then my Dementor, flying faster than any broomstick, is going to Kiss everyone here who voted to send a twelve-year-old girl to Azkaban.}
\emph{Ich werde die Patronus-Zauber aufheben und verhindern, dass noch mehr Patronusse gewirkt werden. Und dann wird mein Dementor, schneller fliegend als jeder Besen, jeden hier küssen, der dafür gestimmt hat, ein zwölfjähriges Mädchen nach Askaban zu schicken.}

% Say that, to set up the if-then expectation, and wait for people to understand and laugh. Then speak the fatal truth; and when the Aurors’ Patronuses winked out to prove the point, either people’s \emph{anticipations} of the mindless void, or Harry’s threat of its destruction, would make the Dementor obey. Those who had sought to compromise with the darkness would be consumed by it.
Sag das vorher, um die Wenn-dann-Erwartung aufzustellen, und warte, dass die Leute es verstehen und lachen. Dann spreche die tödliche Wahrheit; und wenn die Patronusse der Auroren zum Beweis ausblinzeln würden, würde entweder die Vorahnung der Menschen auf die geistlose Leere oder Harrys Drohung mit ihrer Zerstörung den Dementor gehorchen lassen.
Diejenigen, die einen Kompromiss mit der Dunkelheit gesucht hatten, würden von ihr verschlungen werden.

% It was the other solution his dark side had devised.
Das war die andere Lösung, die sich seine dunkle Seite ausgedacht hatte.

% Ignoring the gasps rising from behind him, Harry crossed the radius of the Patronuses, strode to a single pace from Death. Its unhindered fear burst around him like a whirlpool, like stepping next to the sucking drain of some huge bathtub emptying out its water; but with the false Patronuses no longer obscuring the level on which they interacted, Harry could reach the Dementor even as it could reach him. Harry looked straight into the pulling vacuum and—
Das hinter ihm aufsteigende Keuchen ignorierend, durchquerte Harry den Radius des Patronus, schritt bis auf einen Schritt an den Tod heran. Seine ungehinderte Angst umgab ihn wie ein Strudel, als ob er neben den saugenden Abfluss einer riesigen Badewanne treten würde, die ihr Wasser entleert; aber da die falschen Patronusse die Ebene, auf der sie interagierten, nicht mehr verdeckten, konnte Harry den Dementor erreichen, genauso wie dieser ihn erreichen konnte. Harry blickte geradewegs in das ziehende Vakuum und—

% \emph{the Earth among the stars}
\emph{die Erde zwischen den Sternen}

% all his triumph at saving Hermione
all sein Triumph, Hermine gerettet zu haben

% \emph{some day the reality of which you are a shadow will cease to exist}
\emph{eines Tages wird die Realität, von der du ein Schatten bist, aufhören zu existieren!}

% Harry took all the silver emotion that fuelled his Patronus Charm and \emph{shoved} it at the Dementor; and expected Death’s shadow to flee from him—
Harry nahm all die silberne Emotion, die seinen Patronus-Zauber angetrieben hatte, und \emph{schob} sie gedanklich auf den Dementor; und erwartete, dass der Schatten des Todes vor ihm fliehen würde—

% —and as Harry did that, he flung his hands up and shouted “\shout{Boo!}”
—und als Harry das tat, warf er seine Hände hoch und schrie „\shout{Buh!}“

% The void retreated sharply away from Harry until it came up against the dark stone behind.
Die Leere wich scharf von Harry zurück, bis sie auf den dunklen Stein dahinter stieß.

% In the hall there was a deathly silence.
In der Halle herrschte eine tödliche Stille.

% Harry turned his back on the empty void, and looked up at where the toad-woman stood. She was pale beneath the pink make-up, her mouth opening and closing like a fish.
Harry drehte der leeren Leere den Rücken zu und schaute hinauf zu der Stelle, wo die Krötenfrau stand. Sie war blass unter der rosa Schminke, ihr Mund öffnete und schloss sich wie der eines Fisches.

% “I make you this one offer,” said the Boy-Who-Lived. “I never learn that you’ve been interfering with me or any of mine. And you never find out why the unkillable soul-eating monster is scared of me. Now sit down and shut up.”
„Ich mache dir dieses Angebot nur ein einziges Mal!“, sagte der Junge-der-überlebte. „Ich erfahre nie, dass du dich bei mir oder einem meiner Freunde eingemischt hast. Und du erfährst nie, warum das unbesiegbare, seelenfressende Monster Angst vor mir hat. Jetzt setz dich hin und halt den Mund.“

% The toad-woman fell back down to her bench without a word.
Die Krötenfrau ließ sich wortlos auf ihre Bank zurückfallen.

% Harry looked further up.
Harry blickte weiter nach oben.

% “A riddle, Lord Malfoy!” the Boy-Who-Lived shouted across the Most Ancient Hall. “I know you weren’t in Ravenclaw, but try to answer this one anyway! What destroys Dark Lords, frightens Dementors, and owes you sixty thousand Galleons?”
„Ein Rätsel, Lord Malfoy!“, rief der Junge-der-überlebte quer durch die Ältestenhalle. „Ich weiß, dass Sie nicht in Ravenclaw waren, aber versuchen Sie trotzdem, dieses zu beantworten! Was vernichtet die Dunklen Lords, erschreckt die Dementoren und schuldet dir sechzigtausend Galleonen?“

% For an instant Lord Malfoy stood there with eyes slightly widened; then his face fell back into calm scorn, and his voice spoke coolly in reply. “Are you openly threatening me, Mr~Potter?”
Einen Augenblick lang stand Lord Malfoy mit leicht geweiteten Augen da, dann verwandelte sich sein Gesicht wieder in ruhigen Hohn, und seine Stimme antwortete kühl.
„Wollen Sie mir offen drohen, Mr~Potter?“

% “I’m not threatening you,” said the Boy-Who-Lived. “I’m \emph{scaring} you. There’s a difference.”
„Ich bedrohe dich nicht“, sagte der Junge-der-überlebte. „Ich jage dir Angst ein. Das ist ein Unterschied.“

% “Enough, Mr~Potter,” said Professor McGonagall. “We shall be late for afternoon Transfiguration as it is. And do come back here, you’re still terrifying that poor Dementor.” She turned to the Aurors. “Mr~Kleiner, if you would!”
„Genug, Mr~Potter“, sagte Professor McGonagall. „Wir werden ohnehin zu spät zur Nachmittagsverwandlungsstunde kommen. Und kommen Sie bitte zurück, Sie machen dem armen Dementor immer noch Angst.“
Sie wandte sich an die Auroren.
„Mr~Kleiner, wenn Sie so freundlich wären!“

% Harry strode back to them, as the Auror addressed moved forward and pressed a short rod of dark metal to the dark metal chair, muttering an inaudible word of dismissal.
Harry schritt zu ihnen zurück, während der angesprochene Auror sich nach vorne bewegte und einen kurzen Stab aus dunklem Metall an den dunklen Metallstuhl drückte und ein unhörbares Wort der Entlassung murmelte.

% The chains slithered back as smoothly as they had come forth; and Hermione pushed herself out of the chair as fast as she could, and half-ran and half-staggered forward a few steps.
Die Ketten glitten so geschmeidig zurück, wie sie herausgekommen waren; und Hermine schob sich so schnell sie konnte aus dem Stuhl und rannte halb rennend und halb torkelnd ein paar Schritte vorwärts.

% Harry held out his arms—
Harry streckte seine Arme aus—

% —and Hermione half-jumped half-fell into Professor McGonagall’s arms, beginning to sob hysterically.
—und Hermine sprang halb und fiel halb in Professor McGonagalls Arme und begann hysterisch zu schluchzen.

% \emph{Hmpfh,} said a voice inside Harry. \emph{I kind of thought we’d earned that one ourselves.}
\emph{Hmpfh,} sagte eine Stimme in Harry. \emph{Ich dachte irgendwie, wir hätten uns das selbst verdient.}

% \emph{Oh, shut up.}
\emph{Ach, halt die Klappe.}

% Professor McGonagall was holding Hermione so firmly that you might have thought it was a mother holding her daughter, or maybe granddaughter. After a few moments Hermione’s sobs slowed, and then stopped. Professor McGonagall suddenly shifted her stance and grabbed onto her more tightly; the girl’s hands were dangling limply, now, and her eyes were closed—
Professor McGonagall hielt Hermine so fest, dass man hätte meinen können, es sei eine Mutter, die ihre Tochter oder vielleicht Enkelin festhält. Nach ein paar Augenblicken wurde Hermines Schluchzen langsamer und hörte dann auf. Professor McGonagall änderte plötzlich ihre Haltung und packte sie fester; die Hände des Mädchens baumelten jetzt schlaff herunter und ihre Augen waren geschlossen—

% “She’ll be fine, Mr~Potter,” Professor McGonagall said softly in Harry’s direction, without looking at him. “She just needs a few hours in one of Madam Pomfrey’s beds.”
„Sie wird wieder gesund, Mr~Potter“, sagte Professor McGonagall leise in Harrys Richtung, ohne ihn anzusehen. „Sie braucht nur ein paar Stunden in einem der Betten von Madam Pomfrey.“

% “All right, then,” Harry said. “Let’s get her to Madam Pomfrey’s.”
„Also gut“, sagte Harry. „Bringen wir sie zu Madam Pomfrey.“

% “Yes,” said Dumbledore, as he descended to the bottom of the dark stone stairs. “Let us all go home, indeed.” His blue eyes were locked on Harry, as hard as sapphires.
„Ja“, sagte Dumbledore, als er die dunkle Steintreppe hinunterstieg. „Lasst uns alle nach Hause gehen, in der Tat.“
Seine blauen Augen waren auf Harry gerichtet, so hart wie Saphire.

\later

% The Lords and Ladies of the Wizengamot are departing their wooden benches, leaving as they came, looking rather nervous.
Die Lords und Ladies des Zaubergamots verlassen ihre hölzernen Bänke, gehen so, wie sie gekommen sind, und sehen ziemlich nervös aus.

% The vast majority are thinking ‘The Dementor was frightened of the Boy-Who-Lived!’
Die allermeisten denken: „Der Dementor hatte Angst vor dem Jungen!“

% Some of the shrewder ones are already wondering how this will affect the delicate power balance of the Wizengamot—if a new piece has appeared upon the game board.
Einige der Klügeren fragen sich bereits, wie sich dies auf das empfindliche Machtgleichgewicht des Zaubergamots auswirken wird—wenn eine neue Figur auf dem Spielbrett erschienen ist.

% Almost none are thinking anything along the lines of ‘I wonder how he did that.’
Fast keiner denkt etwas in der Art von „Ich frage mich, wie er das gemacht hat.“

% This is the truth of the Wizengamot: many are nobles, many are wealthy magnates of business, a few came by their status in other ways. Some of them are stupid. Most are shrewd in the realms of business and politics, but their shrewdness is circumscribed. Almost none have walked the path of a powerful wizard. They have not read through ancient books, scrutinized old scrolls, searching for truths too powerful to be told openly and disguised in conundrums, hunting for true magic among a hundred fantastic fairy tales. When they are not looking at a contract of debt, they abandon what shrewdness they possess and relax with some comfortable nonsense. They believe in the Deathly Hallows, but they also believe that Merlin fought the dread Totoro and imprisoned the Ree. They know (because that too is part of the standard legend) that a powerful wizard must learn to distinguish the truth among a hundred plausible lies. But it has not occurred to them that they might do the same.
Das ist die Wahrheit über das Zaubergamot: Viele sind Adelige, viele sind reiche Wirtschaftsmagnaten, einige wenige sind auf andere Weise zu ihrem Status gekommen. Einige von ihnen sind dumm. Die meisten sind gewitzt in den Bereichen Wirtschaft und Politik, aber ihre Gewitztheit ist begrenzt. Fast keiner hat den Weg eines mächtigen Zauberers beschritten. Sie haben sich nicht durch uralte Bücher gelesen, alte Schriftrollen unter die Lupe genommen, auf der Suche nach Wahrheiten, die zu mächtig sind, um offen und getarnt in Rätseln zu wandeln, auf der Jagd nach wahrer Magie unter hundert fantastischen Märchen. Wenn sie nicht gerade einen Schuldvertrag vor sich haben, geben sie auf, was an Scharfsinn in ihnen steckt, und entspannen sich mit irgendeinem bequemen Blödsinn. Sie glauben an die Heiligtümer des Todes, aber sie glauben auch, dass Merlin den schrecklichen Totoro bekämpft und den Ree gefangen hat. Sie wissen (denn auch das ist Teil der Standardlegende), dass ein mächtiger Zauberer lernen muss, die Wahrheit unter hundert plausiblen Lügen zu unterscheiden. Aber es ist ihnen nicht in den Sinn gekommen, dass sie das auch tun könnten.

% (Why not? Why, indeed, would wizards with enough status and wealth to turn their hands to almost any endeavour, choose to spend their lives fighting over lucrative monopolies on ink importation? The Headmaster of Hogwarts would hardly see the question; of course most people should not be powerful wizards, just as most people should not be heroes. The Defence Professor could explain at great and cynical length why their ambitions are so trivial; to him, too, there is no puzzle. Only Harry Potter, for all the books he has read, is unable to understand; to the Boy-Who-Lived the life choices of the Lords and Ladies seem incomprehensible—not what a good person would do, nor yet an evil person either. Now which of the three is most wise?)
(Warum nicht? Nun, warum sollten Zauberer, die über genügend Status und Reichtum verfügen, um sich fast allen Unternehmungen zuzuwenden, ihr Leben damit verbringen, um lukrative Monopole für den Tintenimport zu kämpfen?
Der Schulleiter von Hogwarts würde die Frage kaum sehen; natürlich sollten die meisten Menschen keine mächtigen Zauberer sein, so wie die meisten Menschen keine Helden sein sollten.
Der Verteidigungsprofessor könnte in großer und zynischer Länge erklären, warum ihre Ambitionen so trivial sind; auch für ihn gibt es kein Rätsel.
Nur Harry Potter ist trotz aller Bücher, die er gelesen hat, nicht in der Lage, es zu verstehen; dem Jungen, der gelebt hat, erscheinen die Lebensentscheidungen der Lords und Ladies unverständlich—nicht das, was ein guter Mensch tun würde, aber auch nicht ein böser Mensch. Wer von den dreien ist nun am weisesten?)

% For whatever reason, then, most of the Wizengamot has never walked the path that leads to powerful wizardry; they do not seek out what is hidden. For them, there is no \emph{why}. There is no explanation. There is no causality. The Boy-Who-Lived, who was already halfway into the pantheon of legend, has now been promoted all the way there; and it is a brute fact, simple and unexplained, that the Boy-Who-Lived frightens Dementors. Ten years earlier they were told that a one-year-old boy defeated the most terrible Dark Lord of their generation, perhaps the most evil Dark Lord ever to live; and they just accepted that too.
Aus welchem Grund auch immer, die meisten der Mitglieder des Zaubergamots haben den Weg, der zu mächtigen Zauberern führt, nie beschritten; sie suchen nicht nach dem Verborgenen. Für sie gibt es kein \emph{Warum}. Es gibt keine Erklärung. Es gibt keine Kausalität. Der Junge-der-überlebte, der bereits auf halbem Weg in die Geschichten der Legende war, ist nun ganz dorthin befördert worden; und es ist eine brachiale Tatsache, einfach und unerklärlich, dass der Junge-der-überlebte die Dementoren erschreckt. Zehn Jahre zuvor wurde ihnen erzählt, dass ein einjähriger Junge den schrecklichsten Dunklen Lord ihrer Generation besiegt hat, vielleicht den bösesten Dunklen Lord, der je gelebt hat; und auch das haben sie einfach akzeptiert.

% You are not meant to question that sort of thing (they know in some unspoken way). If the most terrible Dark Lord in history, confronts an innocent baby—why, how could he \emph{not} be vanquished? The rhythm of the play demands it. You are supposed to applaud, not stand up from your seat in the audience and say ‘Why?’ It is just the story’s conceit, that in the end the Dark Lord is brought down by a little child; and if you are going to question that, you might as well not attend the play in the first place.
\emph{Man soll so etwas nicht in Frage stellen} (das wissen sie auf eine unausgesprochene Weise). Wenn der schrecklichste Dunkle Lord der Geschichte einem unschuldigen Baby gegenübersteht—wie sollte er nicht besiegt werden? Der Rhythmus des Stücks verlangt es. Man soll applaudieren, nicht von seinem Platz im Publikum aufstehen und sagen: „\emph{Warum}?“ Es ist nur das Schicksal der Geschichte, dass der Dunkle Lord am Ende von einem kleinen Kind besiegt wird; und wenn man das in Frage stellt, kann man das Stück genauso gut gar nicht erst besuchen.

% It does not occur to them to second-guess the application of such reasoning to the events they have seen with their own eyes in the Most Ancient Hall. Indeed, they are not consciously aware that they are using story-reasoning on real life. As for scrutinizing the Boy-Who-Lived with the same careful logic they would use on a political alliance or a business arrangement—what brain would associate to \emph{that}, when a part of the legendary magisterium is at hand?
Es kommt ihnen nicht in den Sinn, die Anwendung einer solchen Argumentation auf die Ereignisse, die sie mit eigenen Augen in der Ältestenhalle gesehen haben, zu hinterfragen. In der Tat sind sie sich nicht bewusst, dass sie die Argumentation von Geschichten auf das reale Leben anwenden. Welches Gehirn würde den Jungen-der-überlebte mit der gleichen sorgfältigen Logik untersuchen, die sie bei einem politischen Bündnis oder einer Geschäftsvereinbarung anwenden würden, wenn es so bequem durch Schicksal und Legende erklärt wird?

% But there are a very few, seated on those wooden benches, who do \emph{not} think like this.
Aber es gibt einige wenige, die auf diesen Holzbänken sitzen, die \emph{nicht} so denken.

% There are a certain few of the Wizengamot who have read through half-disintegrated scrolls and listened to tales of things that happened to someone’s sibling’s cousin, not for entertainment, but as part of a quest for power and truth. They have already marked the Night of Godric’s Hollow, as reported by Albus Dumbledore, as an anomalous and potentially important event. They have wondered why it happened, if it did happen; or if not, why Dumbledore is lying.
Es gibt ein paar wenige aus dem Zaubergamot, die sich durch halb zerfallene Schriftrollen gelesen und Geschichten über Dinge angehört haben, die dem Cousin des Bruders von jemandem passiert sind, nicht zur Unterhaltung, sondern als Teil einer Suche nach Macht und Wahrheit.
Sie haben die Nacht von Godric’s Hollow, wie sie von Albus Dumbledore berichtet wurde, bereits als anormales und potenziell wichtiges Ereignis markiert.
Sie haben sich gefragt, \emph{warum} es passiert ist, \emph{wenn} es wirklich passiert ist; oder \emph{wenn nicht}, \emph{warum} Dumbledore \emph{lügt}.

% And when an eleven-year-old boy rises up and says “Lucius Malfoy” in that cold adult voice, and goes on to speak words one simply would not expect to hear from a first-year in Hogwarts, they do not allow the fact to slip into the confused blurs of legends and the whimsical premises of plays.
Und wenn sich ein elfjähriger Junge erhebt und „\emph{Lucius Malfoy}“ mit dieser kalten Erwachsenenstimme sagt und dann noch Worte spricht, die man von einem Erstklässler in Hogwarts einfach nicht erwarten würde, dann lassen sie diese Tatsache nicht in die gesetzlosen Unschärfen von Legenden und die Prämissen von Theaterstücken gleiten.

% They mark it as a clue.
Sie markieren es als einen Hinweis.

% They add it to the list.
Sie fügen es der Liste hinzu.

% This list is beginning to look somewhat alarming.
Diese Liste sieht langsam ziemlich beunruhigend aus.

% It doesn’t particularly help when the boy yells “\shout{Boo!}” at a Dementor and the decaying corpse presses itself flat against the opposite wall and its horrible ear-hurting voice rasps, “\emph{Make him go away.}”
Es hilft nicht gerade, wenn der Junge einen Dementor mit „\shout{Buh!}“ anschreit und der verwesende Kadaver sich flach an die gegenüberliegende Wand presst und seine schreckliche, ohrenbetäubende Stimme rasselt: „\emph{Macht dass er weggeht!}“

%  LocalWords:  Kleiner Hmpfh Totoro Ree
