% Quelle der Übersetzung: DieFuechsin https://www.fanfiktion.de/s/5c793dfe000a402030774dc7/19/
% \partchapter{The Stanford Prison Experiment}{I}
\partchapter{Das Stanford-Prison-Experiment}{I}

% \lettrinepara{S}{aturday}.
\lettrinepara{S}{amstag}.

\hplettrineextrapara
% Harry had run into trouble falling asleep Friday night, which he had anticipated might happen, and so he had decided to take the obvious advance precaution of buying a sleeping potion; and to prevent it from constituting a visible sign that he was nervous, he had decided to buy it off Fred and George a couple of months earlier. \emph{(Be prepared, that’s the Boy Scout’s marching song…)}
Harry hatte am Freitagabend Schwierigkeiten beim Einschlafen, was er vorausgesehen hatte, und so hatte er beschlossen, die offensichtliche Vorsichtsmaßnahme zu ergreifen und einen Schlaftrank zu kaufen; und um zu verhindern, dass dieser ein sichtbares Zeichen seiner Nervosität darstellte, hatte er einige Monate zuvor beschlossen, ihn Fred und George abzukaufen. (\emph{Seid bereit, das ist das Marschlied der Pfadfinder…})

% Thus Harry was fully rested, and his pouch contained almost everything which he owned and might conceivably need. Harry had, in fact, run into the volume limitation on the pouch; and keeping in mind that he would need to store a large snake, and might need to store who-knew-what-else, he had removed some of the bulkier items, like the car battery. He was up to the point now where he could Transfigure something the size of a car battery in four minutes flat, so it wasn’t much of a loss.
Daher war Harry völlig ausgeruht, und sein Beutel enthielt fast alles, was er besaß und möglicherweise brauchen könnte. Harry war in der Tat auf die Größenbegrenzung des Beutels gestoßen; und da er bedenken musste, dass er eine große Schlange zu verstauen hatte und vielleicht auch wer-weiß-was-noch, hatte er einige der sperrigeren Gegenstände, wie die Autobatterie, entfernt. Er war jetzt an dem Punkt angelangt, an dem er etwas von der Größe einer Autobatterie in vier Minuten transfigurieren konnte, so dass es kein großer Verlust war.

% Harry \emph{had} kept the emergency flares and the oxyacetylene welding torch and fuel tank, since you couldn’t just Transfigure things that were to be burned.
Harry \emph{hatte} die Notfackeln und den Autogenschweißbrenner und den Kraftstofftank aufbewahrt, da man nicht einfach Dinge transfigurieren konnte, die verbrannt werden sollten.

% \emph{(Be prepared, as through life you march along…)}
(\emph{Sei vorbereitet, denn durchs Leben marschierst du mit…})

% Mary’s Place.
Marys Platz.

% After the waitress had taken their order and bowed to them and left the room, Professor Quirrell had performed only four Charms, and then they’d talked about nothing of any vast consequence, just Professor Quirrell’s complex thesis about how the Dark Lord’s curse on the Defence position had led to the decline of duelling and how this had changed social customs in magical Britain. Harry listened and nodded and said intelligent things, while he tried to control the pounding of his heart.
Nachdem die Kellnerin ihre Bestellung entgegengenommen, sich vor ihnen verbeugt und den Raum verlassen hatte, hatte Professor Quirrell nur vier Zauber ausgeführt, und dann hatten sie über nichts von großer Tragweite gesprochen, nur über Professor Quirrells komplexe These darüber, wie der Fluch des Dunklen Lords über die Position des Verteidigungsprofessors zum Niedergang des Duellwesens geführt hatte und wie dies die gesellschaftlichen Gepflogenheiten im magischen Großbritannien verändert hatte. Harry hörte zu, nickte und sagte intelligente Dinge, während er versuchte, das Klopfen seines Herzens zu kontrollieren.

% Then the waitress came in again bearing their food, and this time, a minute after the waitress had departed, Professor Quirrell gestured for the door to close and lock, and began to speak twenty-nine security Charms, one of the ones in Mr~Bester’s sequence being left out this time, which somewhat puzzled Harry.
Dann kam die Kellnerin wieder herein und brachte ihr Essen, und dieses Mal, eine Minute nachdem die Kellnerin gegangen war, führte Professor Quirrell Gesten aus, so dass die Tür geschlossen und verriegelt wurde, und begann, neunundzwanzig Sicherheitszauber zu sprechen, wobei diesmal einer von Mr~Besters Zaubern ausgelassen wurde, was Harry etwas verwirrte.

% Professor Quirrell finished his Charms—
Professor Quirrell beendete seine Zauber—

% —stood up from his chair—
—stand von seinem Stuhl auf—

% —blurred into a green snake, banded in blue and white—
—verschwamm zu einer grünen Schlange, die in blau und weiß gebändert war—

% —hissed, “\parsel{Hungry, boy? Eat your fill swiftly, we shall need both strength and time.}”
—zischte: „\parsel{Hungrig, Junge? Is dich schnell satt, wir brauchen sowohl Kraft als auch Zeit.}“

% Harry’s eyes were a bit wide, but he hissed, “\parsel{I ate well at breakfast,}” and then rapidly began forking noodles into his mouth.
Harrys Augen waren ein bisschen weit aufgerissen, aber er zischte: „\parsel{Ich habe beim Frühstück gut gegessen},“ und dann fing er schnell an, sich Nudeln in den Mund zu stopfen.

% The snake watched him for a moment, with those flat eyes, and then hissed, “\parsel{Do not wish to explain here. Prefer to be elsewhere first. Need to leave unobserved, without sign we have ever departed room.}”
Die Schlange beobachtete ihn einen Moment lang mit diesen flachen Augen und zischte dann: „\parsel{Wünsche nicht, hier zu erklären. Ziehe es vor, erst einmal woanders zu sein. Müssen unbeobachtet raus, ohne ein Zeichen, dass wir den Raum jemals verlassen haben.}“

% “\parsel{So no-one can track us,}” hissed Harry.
„\parsel{Damit unss niemand verfolgen kann},“ zischte Harry.

% “\parsel{Yes. Do you trust me that much, boy? Think before answer. I will have important request of you, which requires trust; if say no regardless, then say no now.}”
„\parsel{Ja. Vertraust du mir so sehr, Junge? Denk nach, bevor du antwortest. Ich werde eine wichtige Bitte an dich haben, die Vertrauen erfordert; wenn du ablehnst, dann sag jetzt nein.}“

% Harry dropped his gaze from the snake’s flat eyes, and looked back down at his sauce-coated noodles, and ate another bite, then another, while he thought.
Harry wandte seinen Blick von den flachen Augen der Schlange ab und schaute wieder auf seine mit Soße bestrichenen Nudeln hinunter, aß noch einen Bissen und dann noch einen, während er nachdachte.

% The Defence Professor…was an ambiguous figure, to put it mildly; Harry thought he had unravelled some of his goals, but others remained mysterious.
Der Verteidigungsprofessor… war eine zweideutige Figur, um es milde auszudrücken; Harry dachte, er hätte einige seiner Ziele enträtselt, aber andere blieben geheimnisvoll.

% But Professor Quirrell had knocked down two hundred girls to stop the ones summoning Harry. Professor Quirrell had deduced that the Dementor was draining Harry through his wand. The Defence Professor had saved Harry’s life, twice, in a two-week period.
Aber Professor Quirrell hatte zweihundert Mädchen niedergerissen, um diejenigen aufzuhalten, die Harry herbei riefen. Professor Quirrell war zu dem Schluss gekommen, dass der Dementor Harry durch seinen Zauberstab aussaugte. Der Verteidigungsprofessor hatte Harry zweimal innerhalb von zwei Wochen das Leben gerettet.

% Which could mean that the Defence Professor was just saving Harry \emph{for later,} that there were ulterior motives. Indeed, it was \emph{certain} that there were ulterior motives. Professor Quirrell wasn’t doing this on a whim. But then Professor Quirrell had also seen Harry taught Occlumency, he had taught Harry how to lose…if the Defence Professor wanted to make some use of Harry Potter, it was a use that required a strengthened Harry Potter, not a weakened one. That was what it meant to be used by a friend, that they would want the use to make you stronger instead of weaker.
Das könnte bedeuten, dass der Verteidigungsprofessor Harry nur \emph{für später} gerettet hatte, dass es Hintergedanken gab. Tatsächlich war es \emph{sicher}, dass es Hintergedanken gab. Professor Quirrell tat dies nicht aus einer Laune heraus. Aber dann hatte Professor Quirrell auch dafür gesorgt, dass Harry Okklumentik Unterricht bekam, er hatte Harry beigebracht, wie man verlor… wenn der Verteidigungsprofessor Harry Potter in irgendeiner Weise benutzen wollte, dann war dies eine Nutzung, die einen gestärkten Harry Potter erforderte, keinen geschwächten. Das war es, was es bedeutete, von einem Freund benutzt zu werden, dass er den Einsatz nutzen wollte, um dich stärker zu machen statt schwächer.

% And if there was sometimes a cold atmosphere about the Defence Professor, bitterness in his voice or emptiness in his gaze, then Harry was the only one who Professor Quirrell allowed to see it.
Und wenn den Verteidigungsprofessor manchmal eine kalte Atmosphäre umgab, Bitterkeit in seiner Stimme oder Leere in seinem Blick, dann war Harry der einzige, dem Professor Quirrell erlaubte, es zu sehen.

% Harry didn’t quite know how to describe in words the sense of kinship he felt with Professor Quirrell, except to say that the Defence Professor was the only \emph{clear-thinking} person Harry had met in the wizarding world. Sooner or later everyone else started playing Quidditch, or not putting protective shells on their time machines, or thinking that Death was their friend. It didn’t matter how good their intentions were. Sooner or later, and usually sooner, they demonstrated that something deep inside their brain was confused. Everyone except Professor Quirrell. It was a bond that went beyond anything of debts owed, or even anything of personal liking, that the two of them were alone in the wizarding world. And if the Defence Professor occasionally seemed a little scary or a little Dark, well, that was just the same thing some people said about Harry.
Harry wusste nicht recht, wie er das Gefühl der Verwandtschaft, das er mit Professor Quirrell empfand, in Worte fassen sollte, außer zu sagen, dass der Verteidigungsprofessor die einzige \emph{klar denkende} Person war, die Harry in der Welt der Zauberer getroffen hatte. Früher oder später fingen alle anderen an, Quidditch zu spielen oder ihre Zeitmaschinen nicht mit Schutzhüllen zu versehen oder zu glauben, der Tod sei ihr Freund. Es spielte keine Rolle, wie gut ihre Absichten waren. Früher oder später, und meistens früher, zeigten sie, dass etwas tief in ihrem Gehirn verwirrt war. Alle außer Professor Quirrell. Es war ein Bund, das über alles hinausging, was sie sich schuldig waren, oder sogar über alle persönlichen Vorlieben, dass die beiden allein in der Welt der Zauberer waren. Und wenn der Verteidigungsprofessor gelegentlich etwas beängstigend oder ein wenig düster wirkte, dann war das genau dasselbe, was einige Leute über Harry sagten.

% “\parsel{I trust you,}” hissed Harry.
„\parsel{Ich vertraue dir},“ zischte Harry.

% And the snake explained the first stage of the plan.
Und die Schlange erklärte die erste Stufe des Plans.

\later

% Harry took a final forkful of noodles, chewed. Beside him, Professor Quirrell, now in human form again, was eating his soup placidly, as though nothing of special interest were occurring.
Harry nahm eine letzte Portion Nudeln und kaute. Neben ihm aß Professor Quirrell, nun wieder in menschlicher Gestalt, seine Suppe in aller Ruhe, als ob nichts von besonderem Interesse vorgefallen wäre.

% Then Harry swallowed, and in the same moment stood up from his chair, already feeling his heart start to hammer hard in his chest. The security precautions they were taking were literally the most stringent possible…
Dann schluckte Harry und stand im selben Moment von seinem Stuhl auf, wobei er bereits spürte, wie sein Herz anfing, hart in seiner Brust zu schlagen. Die Sicherheitsvorkehrungen, die sie trafen, waren buchstäblich die strengsten, die möglich waren…

% “Are you ready to test it, Mr~Potter?” Professor Quirrell said calmly.
„Sind Sie bereit, es zu testen, Mr~Potter?“ sagte Professor Quirrell ruhig.

% It \emph{wasn’t} a test, but Professor Quirrell wouldn’t say that, not out loud in human speech, even in this room screened to the limit that Professor Quirrell had secured with further Charms.
Es \emph{war kein} Test, aber Professor Quirrell wollte das nicht sagen, nicht laut in menschlicher Sprache, nicht einmal in diesem Raum, der bis zum Limit abgeschirmt war, welches Professor Quirrell mit weiteren Zaubern gesichert hatte.

% “Yep,” Harry said as casually as he could.
„Ja,“ sagte Harry so beiläufig, wie er konnte.

% \emph{Step one.}
\emph{Schritt eins.}

% Harry said “Cloak” to his pouch, drew forth the Cloak of Invisibility, and then unstuck the pouch from his belt and threw it toward the other side of the table.
Harry sagte „Umhang“ zu seinem Beutel, zog den Unsichtbarkeitsumhang hervor, löste dann den Beutel von seinem Gürtel und warf ihn auf die andere Seite des Tisches.

% The Defence Professor stood up from his own seat, drew his wand, bent down, and touched his wand to the pouch, murmuring a quiet incantation. The new enchantments would ensure that Professor Quirrell could enter the pouch on his own in snake form, and leave it on his own, and hear what went on outside while he was in the pouch.
Der Verteidigungsprofessor erhob sich von seinem eigenen Platz, zog seinen Zauberstab, beugte sich vor und berührte den Beutel mit seinem Zauberstab und murmelte eine leise Beschwörungsformel. Die neuen Beschwörungen würden dafür sorgen, dass Professor Quirrell den Beutel allein in Schlangenform betreten und verlassen konnte und hörte, was sich draußen abspielte, während er sich in dem Beutel befand.

% \emph{Step two.}
\emph{Schritt zwei.}

% As Professor Quirrell stood up from where he’d bent over by the pouch, and put away his wand, his wand happened to point in Harry’s direction, and there was a brief crawling sensation on Harry’s chest near where the Time-Turner lay, like something creepy had passed very close by without touching him.
Als Professor Quirrell sich von der Stelle erhob, an der er sich über den Beutel gebeugt hatte, und seinen Zauberstab weglegte, zeigte sein Zauberstab zufällig in Harrys Richtung, und über Harrys Brust in der Nähe der Stelle, an der der Zeitumkehrer lag, kroch kurz ein Gefühl, als wäre etwas Unheimliches ganz in der Nähe vorbeigegangen, ohne ihn zu berühren.

% \emph{Step three.}
\emph{Schritt drei.}

% The Defence Professor turned into a snake again, and the sense of doom diminished; the snake crawled to the pouch and into it, the pouch’s mouth opening to admit the green shape, and as the mouth closed again behind the tail, the sense of doom diminished further.
Der Verteidigungsprofessor verwandelte sich wieder in eine Schlange, und das Gefühl des Untergangs nahm ab; die Schlange kroch zu dem Beutel und in ihn hinein, wobei sich der Mund des Beutels öffnete, um die grüne Form aufzunehmen, und als sich der Mund hinter dem Schwanz wieder schloss, nahm das Gefühl des Untergangs weiter ab.

% \emph{Step four.}
\emph{Schritt vier.}

% Harry drew his wand, being careful to stand still as he did it, so that the Time-Turner would not move from where Professor Quirrell had anchored the hourglass within the shell in its current orientation. “\emph{Wingardium Leviosa},” murmured Harry, and the pouch began to float toward him.
Harry zog seinen Zauberstab und achtete dabei darauf, still zu stehen, so dass sich der Zeitumkehrer nicht von der Stelle bewegte, an der Professor Quirrell die Sanduhr in ihrer jetzigen Ausrichtung in der Schale verankert hatte. „Wingardium Leviosa,“ murmelte Harry, und der Beutel begann auf ihn zuzuschweben.

% Slowly, slowly, as Professor Quirrell had instructed, the pouch began to float toward Harry, who waited alert for any sign the pouch was opening, in which case Harry was to use the Hover Charm to propel it away from him as fast as possible.
Langsam, langsam, wie Professor Quirrell angewiesen hatte, begann der Beutel auf Harry zuzuschweben, der aufmerksam auf jedes Anzeichen wartete, dass sich der Beutel öffnete. In diesem Fall sollte Harry den Schwebezauber verwenden, um ihn so schnell wie möglich von sich weg zu befördern.

% As the pouch came within a metre of Harry, the sense of doom returned.
Als sich der Beutel Harry bis auf einen Meter näherte, kehrte das Gefühl des Untergangs zurück.

% As Harry reattached the pouch to his belt, the sense of doom was stronger than it had ever been, but still not overwhelming; it was tolerable.
Als Harry den Beutel wieder an seinem Gürtel befestigte, war das Gefühl des Unheils stärker als je zuvor, aber immer noch nicht überwältigend; es war erträglich.

% Even with Professor Quirrell’s Animagus form lying within the extended space of the pouch resting on Harry’s very hip.
Sogar mit Professor Quirrells Animagus-Form, die im ausgedehnten Raum des auf Harrys Hüfte ruhenden Beutels lag, war es erträglich.

% \emph{Step five.}
\emph{Schritt fünf.}

% Harry sheathed his wand. His other hand still held the Cloak of Invisibility, and Harry drew that cloak over himself.
Harry steckte seinen Zauberstab in die Scheide. Seine andere Hand hielt immer noch den Unsichtbarkeitsumhang, und Harry zog diesen über sich selbst.

% \emph{Step six.}
\emph{Schritt sechs.}

% And so in that room shielded from every possible scrying, which Professor Quirrell had personally and further secured, it was not until \emph{after} Harry was wearing the true Cloak of Invisibility that he reached beneath his shirt and twisted the outer shell of the Time-Turner just once.
Und so griff Harry in diesem Raum, der von jeder möglichen Spionage abgeschirmt war, den Professor Quirrell persönlich und weiter gesichert hatte, erst, nachdem er den wahren Unsichtbarkeitsmantel trug, unter sein Hemd und verdrehte die äußere Hülle des Zeitumkehrers nur einmal.

% The Time-Turner’s inner hourglass stayed anchored and motionless, the setting twisted around it—
Die innere Sanduhr des Zeitumkehrers blieb verankert und bewegungslos, die Fassung verdrehte sich um sie herum—

% The food vanished from the table, the chairs leaped back into place, the door sprang open.
Das Essen verschwand vom Tisch, die Stühle sprangen zurück an ihren Platz, die Tür sprang auf.

% Mary’s Room was deserted, as it should have been, because Professor Quirrell had earlier contacted Mary’s Place under a false name to inquire whether the room would be available at this hour—not to reserve it, not to place a cancelled reservation that might be noted, but only to inquire.
Marys Zimmer war verlassen, so wie es sein sollte, denn Professor Quirrell hatte sich zuvor unter falschem Namen an Marys Platz gewandt, um sich zu erkundigen, ob das Zimmer zu dieser Stunde zur Verfügung stünde—nicht um es zu reservieren, nicht um eine stornierte Reservierung vorzunehmen, die vermerkt werden könnte, sondern nur, um sich zu erkundigen.

% \emph{Step seven.}
\emph{Schritt sieben.}

% Staying under the Cloak of Invisibility, Harry left through the open door. He navigated the tiled hallways of Mary’s Place to the well-stocked bar that greeted new entrants, tended by the owner, Jake. There were only a few people at the bar in the late morning, and Harry had to wait invisibly by the door for several minutes, listening to the murmur of conversation and the gurgle of alcohol, before the door opened to emit a huge genial Irishman, and Harry slipped out silently in his wake.
Harry blieb unter dem Deckmantel der Unsichtbarkeit und ging durch die offene Tür. Er ging durch die gekachelten Gänge von Marys Place zu der gut bestückten Bar, die Neuankömmlinge begrüßte und vom Besitzer Jake betreut wurde. Am Morgen vor der Mittagspause waren nur wenige Leute an der Bar, und Harry musste mehrere Minuten lang unsichtbar an der Tür warten, während er dem Gesprächsgemurmel und dem Glucksen des Alkohols lauschte, bevor sich die Tür öffnete, um einen riesigen, fröhlichen Iren hereinzulassen, und Harry schlich sich in seinem Kielwasser leise hinaus.

% \emph{Step eight.}
\emph{Schritt acht.}

% Harry walked for a while. He was well away from Mary’s Place when he turned off Diagon Alley into a smaller alley, at the end of which lay a shop that was dark, the windows enchanted to blackness.
Harry ging eine Weile zu Fuß. Er war weit von Marys Platz entfernt, als er von der Winkelgasse in eine kleinere Gasse abbog, an deren Ende ein Geschäft lag, das dunkel war, die Fenster verzaubert in Schwärze.

% \emph{Step nine.}
\emph{Schritt neun.}

% “Sword fish melon friend,” Harry spoke the passphrase to the lock, and it clicked open.
„Schwertfisch-Melonenfreund,“ sprach Harry die Passphrase für das Schloss, und es klickte auf.

% Within the shop was also darkness, the light from the open door briefly illuminating it to show a wide, empty room. The furniture shop which had once operated here had gone bankrupt a few months ago, according to the Defence Professor, and the shop had been repossessed, but not yet resold. The walls were painted a simple white, the wooden floor scratched and unpolished, a single closed door set in the back wall; this had been a showroom, once, but now it showed nothing.
Auch im Inneren des Ladens herrschte Dunkelheit, das Licht der geöffneten Tür erhellte ihn kurz, um einen weiten, leeren Raum zu zeigen. Laut dem Verteidigungsprofessor war das Möbelgeschäft, das hier einst tätig gewesen war, vor einigen Monaten in Konkurs gegangen, und das Geschäft war wieder in Besitz genommen, aber noch nicht wieder verkauft worden. Die Wände waren einfach weiß gestrichen, der Holzboden zerkratzt und unpoliert, eine einzige geschlossene Tür in der Rückwand; dies war einst ein Ausstellungsraum gewesen, aber jetzt zeigte er nichts mehr.

% The door clicked shut behind Harry, and then the darkness was pitch and complete.
Die Tür schlug hinter Harry zu, und dann war es stockfinster und komplett dunkel.

% \emph{Step ten.}
\emph{Schritt zehn.}

% Harry took out his wand and said “\emph{Lumos}”, lighting the room with white glow; he took his pouch from his belt (the sense of doom growing a little sharper as he grasped it with his fingers) and lightly tossed it to the opposite side of the room (the sense of doom fading almost completely). And then he began to take off the Cloak of Invisibility, even as his voice hissed, “\parsel{It is done.}”
Harry holte seinen Zauberstab heraus, sagte „\emph{Lumos}“ und erleuchtete den Raum mit weißem Schein; er nahm seinen Beutel von seinem Gürtel (das Gefühl des Untergangs wurde etwas stärker, als er ihn mit den Fingern ergriff) und warf ihn sanft auf die gegenüberliegende Seite des Raumes (das Gefühl des Untergangs verblasste fast vollständig). Und dann begann er, den Umhang der Unsichtbarkeit abzulegen, während seine Stimme zischte: „\parsel{Es ist vollbracht}“.

% \emph{Step eleven.}
\emph{Schritt elf.}

% From the pouch poked a green head, followed shortly by a metre-long green body as the snake slithered out. A moment later, the snake blurred into Professor Quirrell.
Aus dem Beutel stieß ein grüner Kopf, kurz darauf folgte ein meterlanger grüner Körper, als die Schlange herausschlüpfte. Einen Augenblick später verschwamm die Schlange zu Professor Quirrell.

% \emph{Step twelve.}
\emph{Schritt zwölf.}

% Harry waited in silence while the Defence Professor recited thirty Charms.
Harry wartete schweigend, während der Verteidigungsprofessor dreißig Zaubersprüche rezitierte.

% “All right,” Professor Quirrell said calmly, when he had finished. “If anyone is still watching us now, we are in any case doomed, so I will speak plainly and in human form. Parseltongue does not quite suit me, I fear, as I am neither a descendant of Salazar nor a true snake.”
„In Ordnung,“ sagte Professor Quirrell ruhig, als er fertig war. „Wenn uns jetzt noch jemand zuschaut, sind wir auf jeden Fall dem Untergang geweiht, also werde ich offen und in menschlicher Gestalt sprechen. Ich fürchte, Parsel steht mir nicht ganz, denn ich bin weder ein Nachfahre von Salazar noch eine echte Schlange.“

% Harry nodded.
Harry nickte.

% “So, Mr~Potter,” said Professor Quirrell. His gaze intent, his pale blue eyes dark and shadowed in the white light coming from Harry’s wand. “We are alone and unobserved, and I have an important question to ask you.”
„So, Mr~Potter,“ sagte Professor Quirrell. Sein Blick war entschlossen, seine blassblauen Augen dunkel und schattenhaft im weißen Licht von Harrys Zauberstab. „Wir sind allein und unbeobachtet, und ich muss Ihnen eine wichtige Frage stellen.“

% “Go ahead,” said Harry, his heart starting to beat faster.
„Nur zu,“ sagte Harry, sein Herz begann schneller zu schlagen.

% “What is your opinion of the government of magical Britain?”
„Was ist Ihre Meinung über die Regierung des magischen Britannien?“

% That wasn’t quite what Harry had been expecting, but it was close enough, so Harry said, “Based on my limited knowledge, I would say that both the Ministry and the Wizengamot appear to be stupid, corrupt, and evil.”
Das war nicht ganz das, was Harry erwartet hatte, aber es war nahe dran, also sagte Harry: „Aufgrund meines begrenzten Wissens würde ich sagen, dass sowohl das Ministerium als auch der Zaubergamot dumm, korrupt und böse zu sein scheinen.“

% “Correct,” Professor Quirrell said. “Do you understand why I ask?”
„Korrekt,“ sagte Professor Quirrell. „Verstehen Sie, warum ich frage?“

% Harry took a deep breath, and looked Professor Quirrell straight in the eyes, unflinching. Harry had finally worked out that the way to make amazing deductions from scanty evidence was to know the answer in advance, and he had guessed this answer fully a week ago. It needed only a slight adjustment…
Harry holte tief Luft und schaute Professor Quirrell unbeirrt in die Augen. Harry hatte schließlich herausgefunden, dass man aus dürftigen Beweisen erstaunliche Schlussfolgerungen ziehen konnte, wenn man die Antwort im Voraus wusste, und er hatte diese Antwort vor einer Woche vollständig erraten. Es bedurfte nur einer kleinen Anpassung…

% “You are about to invite me to join a secret organization full of interesting people like yourself,” said Harry, “one of whose goals is to reform or overthrow the government of magical Britain, and yes, I’m in.”
„Sie sind im Begriff, mich einzuladen, einer Geheimorganisation voller interessanter Leute wie Ihnen beizutreten,“ sagte Harry, „zu deren Zielen es gehört, die Regierung des magischen Britannien zu reformieren oder zu stürzen, und ja, ich bin dabei“.

% There was a slight pause.
Es gab eine kleine Pause.

% “I’m afraid that is not quite where I intended to direct this conversation,” said Professor Quirrell. The corners of his lips were twitching slightly. “I merely planned to ask for your help in doing something extremely treasonous and illegal.”
„Ich fürchte, das ist nicht ganz das wohin ich dieses Gespräch lenken wollte,“ sagte Professor Quirrell. Seine Lippenwinkel zuckten leicht. „Ich hatte lediglich vor, Sie um Hilfe zu bitten, etwas extrem Verräterisches und Illegales zu tun.“

% \emph{Darn,} thought Harry. Still, Professor Quirrell hadn’t \emph{denied} it… “Go on.”
\emph{Verflixt}, dachte Harry. Aber Professor Quirrell hatte es nicht \emph{geleugnet}… „Fahren Sie fort.“

% “Before I do,” said Professor Quirrell. There was no levity in his voice, now. “\emph{Are} you open to such requests, Mr~Potter? I say again that if you are likely to say no regardless, you must say no now. If your curiosity impels you otherwise, squash it.”
„Bevor ich das tue,“ sagte Professor Quirrell. Es lag kein Leichtsinn in seiner Stimme. „\emph{Sind} Sie offen für solche Wünsche, Mr~Potter? Ich wiederhole: Wenn Sie wahrscheinlich sowieso nein sagen werden, müssen Sie jetzt nein sagen. Wenn Ihre Neugierde Sie anderweitig antreibt, zerquetschen Sie sie.“

% “Treasonous and illegal doesn’t bother me,” said Harry. “Risks bother me and the stakes would need to be commensurate, but I can’t imagine \emph{you} taking risks frivolously.”
„Verräterisch und illegal stört mich nicht,“ sagte Harry. „Risiken stören mich, und der Einsatz müsste angemessen sein, aber ich kann mir nicht vorstellen, dass \emph{Sie} leichtfertig Risiken eingehen.“

% Professor Quirrell nodded. “I would not. It is a terrible abuse of my friendship with you, and of such trust as is placed in my teaching position at Hogwarts—”
Professor Quirrell nickte. „Das würde ich nicht tun. Es ist ein schrecklicher Missbrauch meiner Freundschaft zu Ihnen und des Vertrauens, das in meine Lehrtätigkeit in Hogwarts gesetzt wird—“

% “You can skip this part,” Harry said.
„Sie können diesen Teil überspringen,“ sagte Harry.

% The lips twitched again, and then went flat. “Then I shall skip it. Mr~Potter, you sometimes make a game of lying with truths, playing with words to conceal your meanings in plain sight. I, too, have been known to find that amusing. But if I so much as \emph{tell} you what I hope we shall do this day, Mr~Potter, you will \emph{lie} about it. You will lie straight out, without hesitation, without wordplay or hints, to anyone who asks about it, be they foe or closest friend. You will lie to Malfoy, to Granger, and to McGonagall. You will speak, always and without hesitation, in \emph{exactly} the fashion you would speak if you knew nothing, with no concern for your honour. That also is how it must be.”
Die Lippen zuckten wieder, und dann wurden sie flach. „Dann werde ich es überspringen. Mr~Potter, Sie machen manchmal ein Spiel daraus mit Wahrheiten zu lügen, spielen mit Worten, um ihre Bedeutungen vor aller Augen zu verbergen. Auch ich bin bekannt dafür, dass ich das amüsant finde. Aber wenn ich Ihnen nun \emph{sage}, was ich mir für diesen Tag erhoffe, Mr~Potter, werden Sie \emph{lügen}. Sie werden ohne zu zögern, ohne Wortspiele oder Andeutungen, jeden, der danach fragt, ob Feind oder engster Freund, ohne Umschweife belügen. Sie werden Malfoy, Granger und McGonagall anlügen. Sie werden reden, immer und ohne zu zögern, \emph{genau so}, wie Sie reden würden, wenn Sie nichts wüssten, ohne Rücksicht auf Ihre Ehre. Das ist auch eine Bedingung.“

% There was silence, then, for a time.
Es herrschte eine Zeitlang Stille.

% That was a price measured in a fraction of Harry’s soul.
Das war ein Preis, gemessen an einem Bruchteil von Harrys Seele.

% “Without telling me yet…” said Harry. “Can you say if the need is desperate?”
„Ohne es mir zu sagen…“ sagte Harry. „Können Sie mir sagen, ob das Bedürfnis verzweifelt ist?“

% “There is someone in the most terrible want of your help,” Professor Quirrell said simply, “and there is no-one who can help them but you.”
„Es gibt jemanden, der Ihre Hilfe am dringendsten benötigt,“ sagte Professor Quirrell ganz einfach, „und es gibt niemanden, der ihm helfen kann, außer Ihnen.“

% There was another silence, but not a long one.
Es gab eine weitere Stille, aber keine lange.

% “All right,” Harry said quietly. “Tell me of the mission.”
„In Ordnung,“ sagte Harry leise. „Erzählen Sie mir von der Mission.“

% The dark robes of the Defence Professor seemed to blur against the shadow on the wall, cast by his silhouette blocking the white light of Harry’s wand. “The ordinary Patronus Charm, Mr~Potter, wards off a Dementor’s fear. But the Dementors still see you through it, they know that you are there. Only not your Patronus Charm. It blinds them, or more than blinds them. What I saw beneath the cloak wasn’t even looking in our direction as you killed it; as though it had forgotten our existence, even as it died.”
Die dunkle Robe des Verteidigungsprofessors schien gegen den Schatten an der Wand zu verschwimmen, der von seiner Silhouette geworfen wurde und das weiße Licht von Harrys Zauberstab blockierte. „Der gewöhnliche Patronuszauber, Mr~Potter, wehrt die Angst eines Dementors ab. Aber die Dementoren durchschauen Sie immer noch, sie wissen, dass Sie da sind. Nur nicht Ihren Patronuszauber. Er blendet sie, oder mehr als nur blenden. Was ich unter dem Umhang sah, schaute nicht einmal in unsere Richtung, als Sie es getötet haben; als hätte es unsere Existenz vergessen, selbst als es starb.“

% Harry nodded. That wasn’t surprising, not when you confronted a Dementor on the level of its true existence, beyond anthropomorphism. Death might be the last enemy, but it wasn’t a sentient enemy. When humanity had wiped out smallpox, smallpox hadn’t fought back.
Harry nickte. Das war nicht überraschend, nicht, wenn ein Dementor auf der Ebene seiner wahren Existenz konfrontiert wurde, jenseits des Anthropomorphismus. Der Tod mag der letzte Feind sein, aber er war kein fühlender Feind. Als die Menschheit die Pocken ausgerottet hatte, hatten sich die Pocken nicht gewehrt.

% “Mr~Potter, the central branch of Gringotts is guarded by every spell high and low that the goblins know. Even so those vaults have been successfully robbed; for what wizardry can do, wizardry can undo. And yet no-one has ever escaped from Azkaban. No-one. For every Charm there is a counter-Charm, for every ward there is a bypass. How can it be that no-one has ever been rescued from Azkaban?”
„Herr Potter, die Hauptfiliale von Gringotts wird von jedem Zauberspruch bewacht, den die Kobolde kennen, ob hoch oder niedrig. Dennoch sind diese Gewölbe erfolgreich ausgeraubt worden; denn was Zauberei bewirken kann, kann Zauberei rückgängig machen. Und doch ist noch nie jemand aus Askaban entkommen. Niemand. Für jeden Zauber gibt es einen Gegenzauber, jeder Bann kann umgangen werden. Wie kann es sein, dass noch nie jemand aus Askaban gerettet wurde?“

% “Because Azkaban has something invincible,” Harry said. “Something so terrible that no-one can defeat it.”
„Weil Askaban etwas Unbesiegbares hat,“ sagte Harry. „Etwas so Schreckliches, dass niemand es besiegen kann.“

% That was the keystone of their perfect security, it had to be, nothing human. It was Death that guarded Azkaban.
Das war der Schlüssel ihrer vollkommenen Sicherheit, das musste es sein, nichts Menschliches. Es war der Tod, der Askaban bewachte.

% “The Dementors don’t like their meals being taken away from them,” Professor Quirrell said. Coldness had entered that voice, now. “They know if anyone tries. There are more than a hundred Dementors there, and they speak to the guards as well. It’s that simple, Mr~Potter. If you’re a powerful wizard then Azkaban isn’t hard to enter, and it isn’t hard to leave. So long as you don’t try to take anything out of it that belongs to the Dementors.”
„Die Dementoren mögen es nicht, wenn ihnen ihre Mahlzeiten weggenommen werden,“ sagte Professor Quirrell. Die Kälte war jetzt in diese Stimme eingedrungen. „Sie wissen, wenn es jemand versucht. Es sind mehr als hundert Dementoren dort, und sie sprechen auch mit den Wachen. So einfach ist das, Mr~Potter. Wenn Sie ein mächtiger Zauberer sind, dann ist es nicht schwer, Askaban zu betreten und zu verlassen. Solange man nicht versucht, etwas herauszuholen, was den Dementoren gehört.“

% “But the Dementors are \emph{not} invincible,” said Harry. He could have cast the Patronus Charm with that thought, in that very moment. “Never believe that they are.”
„Aber die Dementoren sind \emph{nicht} unbesiegbar,“ sagte Harry. Mit diesem Gedanken hätte er in diesem Moment den Patronuszauber wirken können. „Glauben Sie niemals, dass sie es sind.“

% Professor Quirrell’s voice was very quiet. “Do you remember what it was like when you went before the Dementor, the first time, when you failed?”
Professor Quirrells Stimme war sehr leise. „Erinnern Sie sich, wie es war, als Sie vor dem Dementor standen, das erste Mal, als Sie versagt haben?“

% “I remember.”
„Ich erinnere mich.“

% And then with a sudden sickening lurch in his stomach, Harry knew where this was going; he should have seen it before.
Und dann, mit einem plötzlichen, miesen Gefühl im Bauch, wusste Harry, wohin das Gespräch führte; er hätte es vorher sehen müssen.

% “There is an innocent person in Azkaban,” Professor Quirrell said.
„Es gibt eine unschuldige Person in Askaban,“ sagte Professor Quirrell.

% Harry nodded, there was a burning sensation in his throat, but he didn’t cry.
Harry nickte, er hatte ein brennendes Gefühl im Hals, aber er weinte nicht.

% “The one of whom I speak was not under the Imperius Curse,” said the Defence Professor, dark robes silhouetted against a greater shadow. “There are surer ways to break wills than the Imperius, if you have the time for torture, and Legilimency, and rituals of which I will not speak. I cannot tell you how I know this, how I know any of this, cannot hint at it even to you, you will have to trust me. But there is a person in Azkaban who never once chose to serve the Dark Lord, who has spent years suffering alone in the most terrible cold and darkness imaginable, and never deserved a single minute of it.”
„Derjenige, von dem ich spreche, stand nicht unter dem Imperius-Fluch,“ sagte der Verteidigungsprofessor, dunkle Gewänder, die sich gegen einen größeren Schatten abhoben. „Es gibt sicherere Wege, den Willen zu brechen als der Imperius, wenn man die Zeit für Folter, Legilimentik und Rituale hat, von denen ich nicht sprechen werde. Ich kann Ihnen nicht sagen, woher ich das weiß, wie ich irgendetwas davon weiß, ich kann es Ihnen nicht einmal andeuten, Sie werden mir vertrauen müssen. Aber es gibt einen Menschen in Askaban, der sich nicht ein einziges Mal dafür entschieden hat, dem Dunklen Lord zu dienen, der jahrelang allein in der schrecklichsten Kälte und Finsternis, die man sich vorstellen kann, gelitten hat und keine einzige Minute davon verdient hat“.

% Harry saw it in a single leap of intuition, his mouth racing almost ahead of his thoughts.
Harry sah es mit einer plötzlichen Intuition, sein Mund raste fast seinen Gedanken voraus.

% \emph{There was no hint, no warning, we all thought—}
\emph{Es gab keine Andeutung, keine Warnung, wir alle dachten—}

% “A person by the name of Black,” Harry said.
„Eine Person mit dem Namen Black,“ sagte Harry.

% There was silence. Silence, while the pale blue eyes stared at him.
Es herrschte Schweigen. Stille, während die blassblauen Augen ihn anstarrten.

% “Well,” said Professor Quirrell after a while. “So much for not telling you the name until after you had accepted the mission. I would ask whether you’re reading \emph{my} mind, but that’s flatly impossible.”
„Nun,“ sagte Professor Quirrell nach einer Weile. „So viel dazu, Ihnen den Namen erst zu verraten, nachdem Sie die Mission angenommen hatten. Ich würde Sie fragen, ob Sie meine Gedanken lesen, aber das ist schlichtweg unmöglich.“

% Harry said nothing, but it was simple enough if you \emph{believed} in the processes of modern democracy. The most obvious person in Azkaban to be innocent was the one who hadn’t had a trial—
Harry sagte nichts, aber es war einfach genug, wenn man an die Prozesse der modernen Demokratie \emph{glaubte}. Die offensichtlichste Person in Askaban, die unschuldig war, war diejenige, die keinen Prozess bekommen hatte—

% “I am \emph{certainly} impressed, Mr~Potter,” said Professor Quirrell. His face was grave. “But this is a serious matter, and if there is some way others could make the same deduction, I \emph{must} know. So tell me, Mr~Potter. How in the name of Merlin, of Atlantis, and the void between the stars, did you guess that I was talking about Bellatrix?”
„Ich bin \emph{natürlich} beeindruckt, Mr~Potter,“ sagte Professor Quirrell. Sein Gesicht war ernst. „Aber dies ist eine ernste Angelegenheit, und wenn es eine Möglichkeit gibt, wie andere die gleiche Schlussfolgerung ziehen könnten, \emph{muss} ich es wissen. Also sagen Sie mir, Mr~Potter. Wie im Namen Merlins, von Atlantis und der Leere zwischen den Sternen haben Sie erraten, dass ich von Bellatrix gesprochen habe?“

%  LocalWords:  aturday
